### 2014-04-11 AAAI_AuthorKit/paper.tex
AAAI author kit (also used by SoCS)

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Bootstrapping Abstract Planning with E-Graphs)
/Author (Aram Ebtekar, Maxim Likhachev)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Bootstrapping Abstract Planning with E-Graphs}
\author{Aram Ebtekar, Maxim Likhachev\\
Carnegie Mellon University\\
5000 Forbes Ave,\\
Pittsburgh, PA 15213\\
}
\maketitle
\begin{abstract}
\begin{quote}
AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors. To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions. 
\end{quote}
\end{abstract}

\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report! This document details the requirements necessary to get your accepted paper published using \LaTeX{}. If you are using Microsoft Word, instructions are provided in a different document. If you want to use some other formatting software, you must obtain permission from AAAI Press first.

The instructions herein are provided as a general guide for experienced \LaTeX{} users who would like to use that software to format their paper for an AAAI Press publication or report. If you are not an experienced \LaTeX{} user, do not use it to format your paper. AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work. If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.

These instructions are generic. Consequently, they do not include specific dates, page charges, and so forth. Please consult your specific written conference instructions for details regarding your submission. Please review the entire document for specific instructions that might apply to your particular situation. All authors must comply with the following:

\begin{itemize}
\item You must use the latest AAAI Press \LaTeX{} macro.
\item Download the author kit.
\item Complete, sign, and return by the deadline the AAAI copyright form (proceedings authors) or distribution license (technical report authors).
\item Read and format your paper source and PDF according to the formatting instructions for authors.
\item Submit your electronic files and abstract using our electronic submission form \textbf{on time.}
\item Submit your copyright form, and any required page or formatting charges to AAAI Press so that they are received by the deadline.
\item Check every page of your paper before submitting it.
\end{itemize}

\section{Copyright}
All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form or, in the case of technical reports, by a valid signed permission to distribute form. There are no exceptions to this requirement. You must send us the original version of this form. However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms14@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office. \textbf{If you fail to send in a signed copyright or permission form, your paper will not be published.} You will find PDF versions of the AAAI copyright and permission to distribute forms in the author kit.

\section{Formatting Requirements in Brief}
We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices. AAAI imposes some requirements on your source and PDF files that must be followed. Most of these requirements are based on our efforts to standardize conference manuscript properties and layout. These requirements are as follows, and all papers submitted to AAAI for publication must comply:

\begin{itemize}
\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
\item No type 3 fonts may be used (even in illustrations).
\item Your title must follow US capitalization rules.
\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
\item No \LaTeX{} 209 documents may be used or submitted.
\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
\item Two-column format in AAAI style is required for all papers.
\item The paper size for final submission must be US letter. No exceptions.
\item The source file must exactly match the PDF.
\item The document margins must be as specified in the formatting instructions.
\item The number of pages and the file size must be as specified for your event.
\item No document may be password protected.
\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
\item Your source and PDF must not have any page numbers, footers, or headers.
\item Your PDF must be compatible with Acrobat 5 or higher.
\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
\end{itemize}

If you do not follow the above requirements, it is likely that we will be unable to publish your paper.

\section{What Files to Submit}
You must submit the following items to ensure that your paper is published:
\begin{itemize}
\item A fully-compliant PDF file.
\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file). The only exception is the bibliography, which you may include separately. Your source must compile on our system, which includes the standard \LaTeX{} support files.
\item All your graphics files.
\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
\end{itemize}

Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).   \textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros. Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.

Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution. Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive. Name your source file with your last (family) name.

\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.  A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.

\section{Using \LaTeX{} to Format Your Paper}

The latest version of the AAAI style file is available on AAAI's website. Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path. Placing it in the same directory as the paper should also work. You must download the latest version of the complete author kit so that you will have the latest instruction set.

\subsection{Document Preamble}

In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection. This command set-up is for three authors. Add or subtract author and address lines as necessary, and uncomment the portions that apply to you. In most instances, this is all you need to do to format your paper in the Times font. The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font. These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).

Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper. If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers). The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.

\begin{quote}
\begin{small}
\textbackslash documentclass[letterpaper]{article}\\
\% \textit{Required Packages}\\
\textbackslash usepackage\{aaai\}\\
\textbackslash usepackage\{times\}\\
\textbackslash usepackage\{helvet\}\\
\textbackslash usepackage\{courier\}\\
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{PDFINFO for PDF\LaTeX{}}\\
\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
\textbackslash pdfinfo\{\\
/Title (Input Your Paper Title Here)\\
/Author (John Doe, Jane Doe)\\
/Keywords (Input your paper's keywords in this optional area)\\
\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Section Numbers}\\
\% Uncomment if you want to use section numbers\\
\% and change the 0 to a 1 or 2\\
\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Title, Author, and Address Information}\\
\textbackslash title\{Title\}\\
\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Body of Paper Begins}\\
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{References and End of Paper}\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}
\end{small}
\end{quote}

\subsection{Inserting Document Metadata with \LaTeX{}}
PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately. \textbf{Document Metadata  for Author and Title are REQUIRED.}

If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them. The epstopdf package will usually work for eps files. You will need to convert your ps files to PDF however.

\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata. The data in the metadata must be completely plain ascii. It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands. Type the title exactly as it appears on the paper (minus all formatting). Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma. You may also include keywords in the Keywords field.

\subsection{Preparing Your Paper}

After the preamble above, you should prepare your paper as follows:

\begin{quote}
\begin{small}
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}\\
\end{small}
\end{quote}
\subsection{Incompatible Packages}
The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
\begin{itemize}
\item hyperref
\item natbib
\item geometry
\item titlesec
\item layout
\item caption
\item titlesec
\item T1 fontenc package (install the CM super fonts package instead)
\end{itemize}

\subsection{Illegal Commands}
The following commands may not be used in your paper:
\begin{itemize}
\item \textbackslash input
\item \textbackslash vspace (when used before or after a section or subsection)
\item \textbackslash addtolength 
\item \textbackslash columnsep
\item \textbackslash top margin (or text height or addsidemargin or even side margin)
\end{itemize}

\subsection{Paper Size, Margins, and Column Width}
Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
\begin{itemize}
\item Top margin: .75 inches
\item Left margin: .75 inches
\item Right margin: .75 inches
\item Bottom margin: 1.25 inches
\end{itemize}

The default paper size in most installations of \LaTeX{} is A4. However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size. Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file: 
\textbackslash documentclass[letterpaper]{article}.

This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
in your preamble.

\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.

\subsubsection{Column Width and Margins.}
To ensure maximum readability, your paper must include two columns. Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns. The aaai.sty file will automatically create these columns for you.

\subsection{Overlength Papers}
If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods. Next,  shrink the size of your graphics. Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment. If these two methods don't work, you may minimally use the following. For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip. For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep. You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
right before the bibliography.

Commands that alter page layout are forbidden. These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive). If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee. Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip. Commands that alter the space between sections are also questionable. The title sec package is not allowed. Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted. Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge. It will be cheaper in the long run.

\subsection{Figures}
Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.

When you include your figures, you must crop them \textbf{outside} of \LaTeX{}. The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.

\subsection{Type Font and Size}
Your paper must be formatted in Times Roman or Nimbus. We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface. Sans serif, when used, should be Courier. Use Symbol or Lucida or Computer Modern for \textit{mathematics only. }

Do not use type 3 fonts for any portion of your paper, including graphics. Type 3 bitmapped fonts are designed for fixed resolution printers. Most print at 300 dpi even if the printer resolution is 1200 dpi or higher. They also often cause high resolution imagesetter devices and our PDF indexing software to crash. Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts. Files containing those fonts (even in graphics) will be rejected.

Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts. The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e. (Note that papers formatted in this way will still use Computer Modern for the mathematics. To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")

If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader. The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document. If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.

The default size for your type should be ten-point with twelve-point leading (line spacing). Start all pages (except the first) directly under the top margin. (See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.

\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}

If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts. They are available without charge from the American Mathematical Society:
http://www.ams.org/tex/type1-fonts.html.

\subsection{Title and Authors}
Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading). This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading). (If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.

\subsubsection{Formatting Author Information}
Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display. For several authors from the same institution, use \textbackslash and:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
\end{small}
\end{quote}

\noindent If the names do not fit well on one line use:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
\end{small}
\end{quote}

\noindent For authors from different institutions, use \textbackslash And:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
\textbackslash And  ...  
\textbackslash And
Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
... \textbackslash \textbackslash ~
Address line\}
\end{small}
\end{quote}

\noindent To start a separate ``row" of authors, use \textbackslash AND:
\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash AND\\
Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
\end{small}
\end{quote}

\noindent If the title and author information does not fit in the area allocated, place
\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.

\subsection{\LaTeX{} Copyright Notice}
The copyright notice automatically appears if you use aaai.sty. If you are creating a technical report, it is not necessary to include this notice. You may disable the copyright line using the \verb+\+nocopyrightcommand. To change the entire text of the copyright slug, use:
\textbackslash copyrighttext \{\emph{text}\}.
Either of these must appear before \textbackslash maketitle. Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}

\subsection{Credits}
Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
For example:
\begin{quote}
\begin{small}
\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
 supported by everybody.\}\}
\end{small}
\end{quote}
Multiple \textbackslash thanks commands can be given. Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document. Note that the \textbackslash thanks command is fragile. You will need to use \textbackslash protect.

Please do not include \textbackslash pubnote commands in your document.

\subsection{Abstract}
The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins. The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract. The abstract should be set in nine-point type with ten-point leading. This concise, one-paragraph summary should describe the general thesis and conclusion of your paper. A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract. The abstract should be no more than two hundred words in length. (Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}

\subsection{Page Numbers}

Do not \textbf{ever} print any page numbers on your paper.

\subsection{Text }
The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).

\subsection{Citations}
Citations within the text should include the author's last name and year, for example (Newell 1980). Append lower-case letters to the year in cases of ambiguity. Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992). In the case of four or more authors, list only the first author, followed by et al. (Ford et al. 1997).

\subsection{Extracts}
Long quotations and extracts should be indented ten points from the left and right margins.

\begin{quote}
This is an example of an extract or quotation. Note the indent on both sides. Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.

\end{quote}

\subsection{Footnotes}
Avoid footnotes as much as possible; they interrupt the reading of the text. When essential, they should be consecutively numbered throughout with superscript Arabic numbers. Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.

\subsection{Headings and Sections}
When necessary, headings should be used to separate major sections of your paper. Remember, you are writing a short paper, not a lengthy book! An overabundance of headings will tend to make your paper look more like an outline than a paper.

First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them. Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them. Do not skip a line between paragraphs. Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.

\subsubsection{Section Numbers}
The use of section numbers in AAAI Press papers is optional. To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2. Section numbers should not be used in short poster papers.

\subsubsection{Section Headings.}
Sections should be arranged and headed as follows:

\subsubsection{Acknowledgments.}
The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish. Please acknowledge other contributors, grant support, and so forth, in this section. Do not put acknowledgments in a footnote on the first page. If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back. Please try to limit acknowledgments to no more than three sentences.

\subsubsection{Appendices.}
Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.

\subsubsection{References}
The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page). A sample list of references is given later on in these instructions. Please use a consistent format for references. Poorly prepared or sloppy references reflect badly on the quality of your paper and your research. Please prepare complete and accurate citations.

\subsection{Illustrations and Figures}
Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed. Do not group them together at the end of the paper. If placed at the top or bottom of the paper, illustrations may run across both columns. Figures must not invade the top, bottom, or side margin areas. Figures must be inserted using the \textbackslash usepackage\{graphicx\}. Number figures sequentially, for example, figure 1, and so on.

The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.

\subsubsection{Low-Resolution Bitmaps.}
You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed. If they are color, they will become an indecipherable mess when converted to black and white. This is always the case with gif files, which should never be used. The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels. You can also enlarge files by manipulating them in software such as PhotoShop. Your figures should be a minimum of 266 dpi when incorporated into your document.

\subsubsection{\LaTeX{} Overflow.}
\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin. If this happens, you need to scale the figure or table down, or reformat the equation. Check your log file! You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}). If you don't, the overflow text will simply be eliminated. \textbf{Nothing is permitted to intrude into the margins.}

\subsubsection{Using Color.}
Your paper will be printed in black and white and grayscale. Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document. Of course, any reference to color will be indecipherable to your reader.

\subsubsection{Drawings.}
We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations. Do not use Microsoft Publisher. These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas. Shading should be 133 lines per inch if possible. Use Times Roman or Helvetica for all figure call-outs. \textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt. Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.

\subsubsection{Photographs and Images.}
Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi. Do not prescreen images.

\subsubsection{Resizing Graphics.}
Resize your graphics \textbf{before} you include them with LaTeX. You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command. Resize the media box of your PDF using a graphics program instead.

\subsubsection{Fonts in Your Illustrations}
You must embed all fonts in your graphics before including them in your LaTeX document.

\subsection{References} 
The aaai.sty file includes a set of definitions for use in formatting references with BibTeX. These definitions make the bibliography style fairly close to the one specified below. To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site. Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:

\begin{quote}
\begin{small}
\textbackslash bibliographystyle\{aaai\}
\textbackslash bibliography\{bibfile1,bibfile2,...\}
\end{small}
\end{quote}

The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).

The following commands are available for your use in citing references:
\begin{quote}
\begin{small}
\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
\end{small}
\end{quote}

\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.

Formatted bibliographies should look like the following examples.

\smallskip \noindent \textit{Book with Multiple Authors}\\
Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.

\smallskip \noindent \textit{Journal Article}\\
Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.

\smallskip \noindent \textit{Magazine Article}\\
Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.

\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
Clancey, W. J. 1983b. Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education. In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560. Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.

\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.

\smallskip \noindent \textit{University Technical Report}\\
Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.

\smallskip \noindent \textit{Dissertation or Thesis}\\
Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.

\smallskip \noindent \textit{Forthcoming Publication}\\
Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.

\section{Producing Reliable PDF\\Documents with \LaTeX{}}
Generally speaking, PDF files are platform independent and accessible to everyone. When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern. Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
\begin{itemize}
\item Use type 1 fonts (not type 3 fonts)
\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
\item Embed all fonts when producing the PDF
\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
\end{itemize}

\subsection{Creating Output Using PDF\LaTeX{} Is Required}
By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont). PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source. The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).

PDF\LaTeX{}'s default is to create documents with type 1 fonts. If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.

\subsubsection{dvipdf Script}
Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.

\subsubsection{dvipdfm}
Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).

\subsection{Ghostscript}
\LaTeX{} users should not use GhostScript to create their PDFs.

\subsection{Graphics}
If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.

\section{Proofreading Your PDF}
Please check all the pages of your PDF file. Is the page size A4? Are there any type 3, Identity-H, or CID fonts? Are all the fonts embedded? Are there any areas where equations or figures run into the margins? Did you include all your figures? Did you follow mixed case capitalization rules for your title? Did you include a copyright notice? Do any of the pages scroll slowly (because the graphics draw slowly on the page)? Are URLs underlined and in color? You will need to fix these common errors before submitting your file.

\section{Improperly Formatted Files }
In the past, AAAI has corrected improperly formatted files submitted by the authors. Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb. Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication. If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee. If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet. Files that are not corrected after a second attempt will be withdrawn.

\subsection{\LaTeX{} 209 Warning}
If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.

\section{Naming Your Electronic File}
We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions. If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.

\section{Submitting Your Electronic Files to AAAI}
Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.

\section{Inquiries} 
If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below. If you have technical questions about implementation of the aaai style file, please contact an expert at your site. We do not provide technical support for \LaTeX{} or any other software package. To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.

\begin{quote}
\noindent AAAI Press\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\ 
\textit{Telephone:} (650) 328-3123\\ 
\textit{E-mail:} See the submission instructions for your particular conference or event.
\end{quote}

\section{Additional Resources}
\LaTeX{} is a difficult program to master. If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems. (It was written for another purpose, but it has general application as well). It is available at www.ctan.org in the tex-archive.

\section{ Acknowledgments}
AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton. We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.

The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press. Bibliography style changes were added by Sunil Issar. \verb+\+pubnote was added by J. Scott Penberthy. George Ferguson added support for printing the AAAI copyright slug. Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.

\bigskip
\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!

\end{document}

### 2014-04-11 AAAI_AuthorKit/paper.tex
bug: logistics98/prob24 takes a long time to run despite 2s limit

@@
 \pdfinfo{
-/Title (Bootstrapping Abstract Planning with E-Graphs)
+/Title (Bootstrapping Abstract Planning with Experience Graphs)
 /Author (Aram Ebtekar, Maxim Likhachev)}
@@
 %
-\title{Bootstrapping Abstract Planning with E-Graphs}
+\title{Bootstrapping Abstract Planning with Experience Graphs}
 \author{Aram Ebtekar, Maxim Likhachev\\
@@
 \begin{quote}
-AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors.
-To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions.
+A* and variants are regularly applied to plan paths in a graph.
+Rather than planning each query from scratch, we follow the recent trend across AI and robotics of collecting and reusing information, i.e.
+learning.
+Experience-graphs (E-graphs) store past plans in order to speed up related planning episodes in the future.
+New challenges arise when we try to apply E-graphs in high-level planning, where the state graph is implicitly exponentially sized in its description length.
+We describe an algorithm that combines E-graphs with a standard STRIPS relaxation to form $\epsilon$-admissible heuristics in a domain-independent manner.
 \end{quote}
@@
 
-\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report!
-This document details the requirements necessary to get your accepted paper published using \LaTeX{}.
-If you are using Microsoft Word, instructions are provided in a different document.
-If you want to use some other formatting software, you must obtain permission from AAAI Press first.
+\section{Introduction}
+asdf
 
-The instructions herein are provided as a general guide for experienced \LaTeX{} users who would like to use that software to format their paper for an AAAI Press publication or report.
-If you are not an experienced \LaTeX{} user, do not use it to format your paper.
-AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work.
-If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.
-
-These instructions are generic.
-Consequently, they do not include specific dates, page charges, and so forth.
-Please consult your specific written conference instructions for details regarding your submission.
-Please review the entire document for specific instructions that might apply to your particular situation.
-All authors must comply with the following:
-
-\begin{itemize}
-\item You must use the latest AAAI Press \LaTeX{} macro.
-\item Download the author kit.
-\item Complete, sign, and return by the deadline the AAAI copyright form (proceedings authors) or distribution license (technical report authors).
-\item Read and format your paper source and PDF according to the formatting instructions for authors.
-\item Submit your electronic files and abstract using our electronic submission form \textbf{on time.}
-\item Submit your copyright form, and any required page or formatting charges to AAAI Press so that they are received by the deadline.
-\item Check every page of your paper before submitting it.
-\end{itemize}
-
-\section{Copyright}
-All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form or, in the case of technical reports, by a valid signed permission to distribute form.
-There are no exceptions to this requirement.
-You must send us the original version of this form.
-However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms14@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office.
-\textbf{If you fail to send in a signed copyright or permission form, your paper will not be published.} You will find PDF versions of the AAAI copyright and permission to distribute forms in the author kit.
-
-\section{Formatting Requirements in Brief}
-We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices.
-AAAI imposes some requirements on your source and PDF files that must be followed.
-Most of these requirements are based on our efforts to standardize conference manuscript properties and layout.
-These requirements are as follows, and all papers submitted to AAAI for publication must comply:
-
-\begin{itemize}
-\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
-\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
-\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
-\item No type 3 fonts may be used (even in illustrations).
-\item Your title must follow US capitalization rules.
-\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
-\item No \LaTeX{} 209 documents may be used or submitted.
-\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
-\item Two-column format in AAAI style is required for all papers.
-\item The paper size for final submission must be US letter. No exceptions.
-\item The source file must exactly match the PDF.
-\item The document margins must be as specified in the formatting instructions.
-\item The number of pages and the file size must be as specified for your event.
-\item No document may be password protected.
-\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
-\item Your source and PDF must not have any page numbers, footers, or headers.
-\item Your PDF must be compatible with Acrobat 5 or higher.
-\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
-\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
-\end{itemize}
-
-If you do not follow the above requirements, it is likely that we will be unable to publish your paper.
-
-\section{What Files to Submit}
-You must submit the following items to ensure that your paper is published:
-\begin{itemize}
-\item A fully-compliant PDF file.
-\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file).
-The only exception is the bibliography, which you may include separately.
-Your source must compile on our system, which includes the standard \LaTeX{} support files.
-\item All your graphics files.
-\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
-\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
-\end{itemize}
-
-Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).
-\textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros.
-Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.
-
-Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution.
-Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive.
-Name your source file with your last (family) name.
-
-\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.
-A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.
-
-\section{Using \LaTeX{} to Format Your Paper}
-
-The latest version of the AAAI style file is available on AAAI's website.
-Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path.
-Placing it in the same directory as the paper should also work.
-You must download the latest version of the complete author kit so that you will have the latest instruction set.
-
-\subsection{Document Preamble}
-
-In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection.
-This command set-up is for three authors.
-Add or subtract author and address lines as necessary, and uncomment the portions that apply to you.
-In most instances, this is all you need to do to format your paper in the Times font.
-The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font.
-These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).
-
-Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper.
-If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers).
-The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.
-
-\begin{quote}
-\begin{small}
-\textbackslash documentclass[letterpaper]{article}\\
-\% \textit{Required Packages}\\
-\textbackslash usepackage\{aaai\}\\
-\textbackslash usepackage\{times\}\\
-\textbackslash usepackage\{helvet\}\\
-\textbackslash usepackage\{courier\}\\
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{PDFINFO for PDF\LaTeX{}}\\
-\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
-\textbackslash pdfinfo\{\\
-/Title (Input Your Paper Title Here)\\
-/Author (John Doe, Jane Doe)\\
-/Keywords (Input your paper's keywords in this optional area)\\
-\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Section Numbers}\\
-\% Uncomment if you want to use section numbers\\
-\% and change the 0 to a 1 or 2\\
-\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Title, Author, and Address Information}\\
-\textbackslash title\{Title\}\\
-\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
-Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Body of Paper Begins}\\
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{References and End of Paper}\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}
-\end{small}
-\end{quote}
-
-\subsection{Inserting Document Metadata with \LaTeX{}}
-PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately.
-\textbf{Document Metadata  for Author and Title are REQUIRED.}
-
-If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them.
-The epstopdf package will usually work for eps files.
-You will need to convert your ps files to PDF however.
-
-\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata.
-The data in the metadata must be completely plain ascii.
-It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands.
-Type the title exactly as it appears on the paper (minus all formatting).
-Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma.
-You may also include keywords in the Keywords field.
-
-\subsection{Preparing Your Paper}
-
-After the preamble above, you should prepare your paper as follows:
-
-\begin{quote}
-\begin{small}
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}\\
-\end{small}
-\end{quote}
-\subsection{Incompatible Packages}
-The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
-\begin{itemize}
-\item hyperref
-\item natbib
-\item geometry
-\item titlesec
-\item layout
-\item caption
-\item titlesec
-\item T1 fontenc package (install the CM super fonts package instead)
-\end{itemize}
-
-\subsection{Illegal Commands}
-The following commands may not be used in your paper:
-\begin{itemize}
-\item \textbackslash input
-\item \textbackslash vspace (when used before or after a section or subsection)
-\item \textbackslash addtolength 
-\item \textbackslash columnsep
-\item \textbackslash top margin (or text height or addsidemargin or even side margin)
-\end{itemize}
-
-\subsection{Paper Size, Margins, and Column Width}
-Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
-\begin{itemize}
-\item Top margin: .75 inches
-\item Left margin: .75 inches
-\item Right margin: .75 inches
-\item Bottom margin: 1.25 inches
-\end{itemize}
-
-The default paper size in most installations of \LaTeX{} is A4.
-However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size.
-Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file:
-\textbackslash documentclass[letterpaper]{article}.
-
-This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
-in your preamble.
-
-\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.
-
-\subsubsection{Column Width and Margins.}
-To ensure maximum readability, your paper must include two columns.
-Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns.
-The aaai.sty file will automatically create these columns for you.
-
-\subsection{Overlength Papers}
-If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods.
-Next,  shrink the size of your graphics.
-Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment.
-If these two methods don't work, you may minimally use the following.
-For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip.
-For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep.
-You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
-right before the bibliography.
-
-Commands that alter page layout are forbidden.
-These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive).
-If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee.
-Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip.
-Commands that alter the space between sections are also questionable.
-The title sec package is not allowed.
-Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted.
-Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge.
-It will be cheaper in the long run.
-
-\subsection{Figures}
-Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.
-
-When you include your figures, you must crop them \textbf{outside} of \LaTeX{}.
-The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.
-
-\subsection{Type Font and Size}
-Your paper must be formatted in Times Roman or Nimbus.
-We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface.
-Sans serif, when used, should be Courier.
-Use Symbol or Lucida or Computer Modern for \textit{mathematics only.
-}
-
-Do not use type 3 fonts for any portion of your paper, including graphics.
-Type 3 bitmapped fonts are designed for fixed resolution printers.
-Most print at 300 dpi even if the printer resolution is 1200 dpi or higher.
-They also often cause high resolution imagesetter devices and our PDF indexing software to crash.
-Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts.
-Files containing those fonts (even in graphics) will be rejected.
-
-Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts.
-The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e.
-(Note that papers formatted in this way will still use Computer Modern for the mathematics.
-To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")
-
-If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader.
-The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document.
-If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.
-
-The default size for your type should be ten-point with twelve-point leading (line spacing).
-Start all pages (except the first) directly under the top margin.
-(See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.
-
-\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}
-
-If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts.
-They are available without charge from the American Mathematical Society:
-http://www.ams.org/tex/type1-fonts.html.
-
-\subsection{Title and Authors}
-Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading).
-This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading).
-(If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.
-
-\subsubsection{Formatting Author Information}
-Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display.
-For several authors from the same institution, use \textbackslash and:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
-Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
-\end{small}
-\end{quote}
-
-\noindent If the names do not fit well on one line use:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
-... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
-Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
-\end{small}
-\end{quote}
-
-\noindent For authors from different institutions, use \textbackslash And:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
-\textbackslash And  ...  
-\textbackslash And
-Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
-... \textbackslash \textbackslash ~
-Address line\}
-\end{small}
-\end{quote}
-
-\noindent To start a separate ``row" of authors, use \textbackslash AND:
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash AND\\
-Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
-\end{small}
-\end{quote}
-
-\noindent If the title and author information does not fit in the area allocated, place
-\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
-after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.
-
-\subsection{\LaTeX{} Copyright Notice}
-The copyright notice automatically appears if you use aaai.sty.
-If you are creating a technical report, it is not necessary to include this notice.
-You may disable the copyright line using the \verb+\+nocopyrightcommand.
-To change the entire text of the copyright slug, use:
-\textbackslash copyrighttext \{\emph{text}\}.
-Either of these must appear before \textbackslash maketitle.
-Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}
-
-\subsection{Credits}
-Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
-\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
-For example:
-\begin{quote}
-\begin{small}
-\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
- supported by everybody.\}\}
-\end{small}
-\end{quote}
-Multiple \textbackslash thanks commands can be given.
-Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document.
-Note that the \textbackslash thanks command is fragile.
-You will need to use \textbackslash protect.
-
-Please do not include \textbackslash pubnote commands in your document.
-
-\subsection{Abstract}
-The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins.
-The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract.
-The abstract should be set in nine-point type with ten-point leading.
-This concise, one-paragraph summary should describe the general thesis and conclusion of your paper.
-A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract.
-The abstract should be no more than two hundred words in length.
-(Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}
-
-\subsection{Page Numbers}
-
-Do not \textbf{ever} print any page numbers on your paper.
-
-\subsection{Text }
-The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).
-
-\subsection{Citations}
-Citations within the text should include the author's last name and year, for example (Newell 1980).
-Append lower-case letters to the year in cases of ambiguity.
-Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992).
-In the case of four or more authors, list only the first author, followed by et al.
-(Ford et al.
-1997).
-
-\subsection{Extracts}
-Long quotations and extracts should be indented ten points from the left and right margins.
-
-\begin{quote}
-This is an example of an extract or quotation.
-Note the indent on both sides.
-Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.
-
-\end{quote}
-
-\subsection{Footnotes}
-Avoid footnotes as much as possible; they interrupt the reading of the text.
-When essential, they should be consecutively numbered throughout with superscript Arabic numbers.
-Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.
-
-\subsection{Headings and Sections}
-When necessary, headings should be used to separate major sections of your paper.
-Remember, you are writing a short paper, not a lengthy book!
-An overabundance of headings will tend to make your paper look more like an outline than a paper.
-
-First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them.
-Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them.
-Do not skip a line between paragraphs.
-Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.
-
-\subsubsection{Section Numbers}
-The use of section numbers in AAAI Press papers is optional.
-To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2.
-Section numbers should not be used in short poster papers.
-
-\subsubsection{Section Headings.}
-Sections should be arranged and headed as follows:
-
-\subsubsection{Acknowledgments.}
-The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish.
-Please acknowledge other contributors, grant support, and so forth, in this section.
-Do not put acknowledgments in a footnote on the first page.
-If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back.
-Please try to limit acknowledgments to no more than three sentences.
-
-\subsubsection{Appendices.}
-Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.
-
-\subsubsection{References}
-The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page).
-A sample list of references is given later on in these instructions.
-Please use a consistent format for references.
-Poorly prepared or sloppy references reflect badly on the quality of your paper and your research.
-Please prepare complete and accurate citations.
-
-\subsection{Illustrations and Figures}
-Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed.
-Do not group them together at the end of the paper.
-If placed at the top or bottom of the paper, illustrations may run across both columns.
-Figures must not invade the top, bottom, or side margin areas.
-Figures must be inserted using the \textbackslash usepackage\{graphicx\}.
-Number figures sequentially, for example, figure 1, and so on.
-
-The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.
-
-\subsubsection{Low-Resolution Bitmaps.}
-You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed.
-If they are color, they will become an indecipherable mess when converted to black and white.
-This is always the case with gif files, which should never be used.
-The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels.
-You can also enlarge files by manipulating them in software such as PhotoShop.
-Your figures should be a minimum of 266 dpi when incorporated into your document.
-
-\subsubsection{\LaTeX{} Overflow.}
-\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin.
-If this happens, you need to scale the figure or table down, or reformat the equation.
-Check your log file!
-You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}).
-If you don't, the overflow text will simply be eliminated.
-\textbf{Nothing is permitted to intrude into the margins.}
-
-\subsubsection{Using Color.}
-Your paper will be printed in black and white and grayscale.
-Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document.
-Of course, any reference to color will be indecipherable to your reader.
-
-\subsubsection{Drawings.}
-We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations.
-Do not use Microsoft Publisher.
-These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas.
-Shading should be 133 lines per inch if possible.
-Use Times Roman or Helvetica for all figure call-outs.
-\textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt.
-Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.
-
-\subsubsection{Photographs and Images.}
-Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi.
-Do not prescreen images.
-
-\subsubsection{Resizing Graphics.}
-Resize your graphics \textbf{before} you include them with LaTeX.
-You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command.
-Resize the media box of your PDF using a graphics program instead.
-
-\subsubsection{Fonts in Your Illustrations}
-You must embed all fonts in your graphics before including them in your LaTeX document.
-
-\subsection{References} 
-The aaai.sty file includes a set of definitions for use in formatting references with BibTeX.
-These definitions make the bibliography style fairly close to the one specified below.
-To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site.
-Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:
-
-\begin{quote}
-\begin{small}
-\textbackslash bibliographystyle\{aaai\}
-\textbackslash bibliography\{bibfile1,bibfile2,...\}
-\end{small}
-\end{quote}
-
-The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).
-
-The following commands are available for your use in citing references:
-\begin{quote}
-\begin{small}
-\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
-\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
-\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
-\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
-\end{small}
-\end{quote}
-
-\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.
-
-Formatted bibliographies should look like the following examples.
-
-\smallskip \noindent \textit{Book with Multiple Authors}\\
-Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.
-
-\smallskip \noindent \textit{Journal Article}\\
-Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.
-
-\smallskip \noindent \textit{Magazine Article}\\
-Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
-Clancey, W.
-J.
-1983b.
-Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education.
-In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560.
-Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
-Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.
-
-\smallskip \noindent \textit{University Technical Report}\\
-Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.
-
-\smallskip \noindent \textit{Dissertation or Thesis}\\
-Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.
-
-\smallskip \noindent \textit{Forthcoming Publication}\\
-Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.
-
-\section{Producing Reliable PDF\\Documents with \LaTeX{}}
-Generally speaking, PDF files are platform independent and accessible to everyone.
-When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern.
-Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
-\begin{itemize}
-\item Use type 1 fonts (not type 3 fonts)
-\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
-\item Embed all fonts when producing the PDF
-\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
-\end{itemize}
-
-\subsection{Creating Output Using PDF\LaTeX{} Is Required}
-By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont).
-PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source.
-The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).
-
-PDF\LaTeX{}'s default is to create documents with type 1 fonts.
-If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.
-
-\subsubsection{dvipdf Script}
-Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.
-
-\subsubsection{dvipdfm}
-Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).
-
-\subsection{Ghostscript}
-\LaTeX{} users should not use GhostScript to create their PDFs.
-
-\subsection{Graphics}
-If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.
-
-\section{Proofreading Your PDF}
-Please check all the pages of your PDF file.
-Is the page size A4?
-Are there any type 3, Identity-H, or CID fonts?
-Are all the fonts embedded?
-Are there any areas where equations or figures run into the margins?
-Did you include all your figures?
-Did you follow mixed case capitalization rules for your title?
-Did you include a copyright notice?
-Do any of the pages scroll slowly (because the graphics draw slowly on the page)?
-Are URLs underlined and in color?
-You will need to fix these common errors before submitting your file.
-
-\section{Improperly Formatted Files }
-In the past, AAAI has corrected improperly formatted files submitted by the authors.
-Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb.
-Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication.
-If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee.
-If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet.
-Files that are not corrected after a second attempt will be withdrawn.
-
-\subsection{\LaTeX{} 209 Warning}
-If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.
-
-\section{Naming Your Electronic File}
-We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions.
-If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.
-
-\section{Submitting Your Electronic Files to AAAI}
-Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.
-
-\section{Inquiries} 
-If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below.
-If you have technical questions about implementation of the aaai style file, please contact an expert at your site.
-We do not provide technical support for \LaTeX{} or any other software package.
-To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.
-
-\begin{quote}
-\noindent AAAI Press\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\ 
-\textit{Telephone:} (650) 328-3123\\ 
-\textit{E-mail:} See the submission instructions for your particular conference or event.
-\end{quote}
-
-\section{Additional Resources}
-\LaTeX{} is a difficult program to master.
-If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems.
-(It was written for another purpose, but it has general application as well).
-It is available at www.ctan.org in the tex-archive.
-
-\section{ Acknowledgments}
-AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton.
-We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.
-
-The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press.
-Bibliography style changes were added by Sunil Issar.
-\verb+\+pubnote was added by J.
-Scott Penberthy.
-George Ferguson added support for printing the AAAI copyright slug.
-Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.
-
-\bigskip
-\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!
+\section{Algorithm}
 

### 2014-04-11 TestSuite.sh

@@ -1,6 +1,5 @@
 #!/bin/sh
-rm -r Test
-mkdir Test
+rm -r Test/*
 
 #for prob in "6-0" "7-0" "8-0" "9-0" "10-0" "11-0" "12-0" "13-0" "14-0" "14-1" "15-0" "15-1" "16-1" "16-2" "17-0"
 #do
@@ -17,13 +16,14 @@ mkdir Test
 
 for dir in examples/*/
 do
+	mkdir -p Test/${dir}
 	for filename in ${dir}p*.pddl
 	do
 	if [ "${filename}" != "${dir}p*.pddl" ]
 	then
-		echo ${filename}
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/$(basename "$filename" .pddl).eg0 Test/$(basename "$filename" .pddl).eg1 -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/$(basename "$filename" .pddl).eg1 Test/$(basename "$filename" .pddl).eg2 -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
+		#without file extension: Test/$(basename "$filename" .pddl).eg
+		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/${filename}.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
+		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/${filename}.eg Test/trash.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
 	fi
 	done
 done

### 2014-04-11 planner/planner.cpp

@@ -4020,7 +4020,7 @@ printStatistics( void )
   FILE *file = fopen( std::string(StatisticsOut).c_str(), "a" );
   if (file != nullptr)
   {
-   if (EGraphIn[EGraphIn.size()-1] == '0')
+   if (EGraphIn == "Test/none.eg")
       fprintf( file, "%d ", generatedNodes );
     else
       fprintf( file, "%d\t%s\n", generatedNodes, problemFile );
@@ -4485,6 +4485,10 @@ scheduler( schedule_t *schedule )
     if( result == nullptr )
     {
       fprintf( stderr, "SOLUTION: no solution found\n" );
+      // TODO debug remove extra prints
+      FILE *file = fopen( std::string(StatisticsOut).c_str(), "a" );
+      if (file != nullptr )
+          fprintf( file, ">" );
     }
     else
     {
@@ -4494,10 +4498,6 @@ scheduler( schedule_t *schedule )
       memorizePath(result);
       printEGraph(EGraphOut);
     }
-    // TODO debug remove extra prints
-    FILE *file = fopen( std::string(StatisticsOut).c_str(), "a" );
-    if (file != nullptr && result == nullptr )
-        fprintf( file, "!" );
       
     printStatistics();
 

### 2014-04-11 AAAI_AuthorKit/paper.tex
Starting the paper

@@
 \section{Algorithm}
+When planning over possible states of the world, it's typically more efficient to describe the states in terms of a set of features.
+The set of states is exponential in the number of features, so even a small problem description may imply a large graph.
+In general, planning over such a large space is computationally infeasible.
+
+We may view planning as a process that generates distance-to-goal labels for each node of a graph.
+Given these distance labels, it's a simple matter to generate a plan by successively moving to the cheapest neighbour.
+Since there is no deterministic polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try an approximation algorithm.
+The resulting labels we call \textbf{heuristics}, and we use them in hopes of achieving optimal or near-optimal plans more efficiently.
+If the heuristic precisely reflects the true distances, we find a path immediately.
+Algorithms such as A* are designed to find solutions quickly whenever the heuristic is reasonably tight and \textbf{$\epsilon$-consistent}.
+Note that in practice any subexponential algorithm can only afford to look at a subset of the nodes, so it is only for these that we compute the heuristic.
+If the heuristic is good, we hope not to have to look at (i.e.
+generate) too many nodes.
+Thus, there is a tradeoff between spending more time to get a tight heuristic, vs evaluating a weaker heuristic more quickly but also more frequently.
 

### 2014-04-22 TestSuite.sh
Test

@@ -1,5 +1,5 @@
 #!/bin/sh
-rm -r Test/*
+#rm -r Test/*
 
 #for prob in "6-0" "7-0" "8-0" "9-0" "10-0" "11-0" "12-0" "13-0" "14-0" "14-1" "15-0" "15-1" "16-1" "16-2" "17-0"
 #do
@@ -14,7 +14,8 @@ rm -r Test/*
 #  echo "--------------------------------------------------------------------------------"
 #done
 
-for dir in examples/*/
+#for dir in examples/*/
+for dir in "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
 do
 	mkdir -p Test/${dir}
 	for filename in ${dir}p*.pddl

### 2014-04-22 planner/planner.cpp

@@ -150,6 +150,7 @@ string               EGraphOut;
 vector<experience_t> experience;
 vector<atom_t*>      eNode;
 vector<vector<cost_t> > eDist;
+FILE* statsFile;
 
 
 
@@ -3816,6 +3817,7 @@ readEGraph(string fileName)
         eDist[i][j].max = min(eDist[i][j].max, eDist[i][k].max + eDist[k][j].max);
       }
   // TODO remove debug code
+  fprintf(statsFile, "EgSize=%u ", experience.size());
   /*for (size_t i = 0; i < eNode.size(); ++i)
   {
       fprintf( stdout, "%d'th distance to goal is %d:\t", i, eDist[i][0].max );
@@ -3839,6 +3841,9 @@ printEGraph(string fileName)
     perror( "ERROR: could not write EGraph to file" );
     return false;
   }
+  
+  // TODO remove debug code
+  fprintf(statsFile, "ExpSize=%u ", experience.size());
   
   std::uniform_real_distribution<double> dist(0, 1);
   for (auto& exper: experience)
@@ -4017,14 +4022,12 @@ printStatistics( void )
   fprintf( stdout, "STATISTICS: average branching factor = %f\n", (float)generatedNodes / (float)expandedNodes );
   
   // TODO debug remove extra prints
-  FILE *file = fopen( std::string(StatisticsOut).c_str(), "a" );
-  if (file != nullptr)
+  if (statsFile != nullptr)
   {
    if (EGraphIn == "Test/none.eg")
-      fprintf( file, "%d ", generatedNodes );
+      fprintf( statsFile, "Gen=%d ", generatedNodes );
     else
-      fprintf( file, "%d\t%s\n", generatedNodes, problemFile );
-    fclose( file );
+      fprintf( statsFile, "Gen=%d\tProb=%s\n", generatedNodes, problemFile );
   }
 }
 
@@ -4486,9 +4489,8 @@ scheduler( schedule_t *schedule )
     {
       fprintf( stderr, "SOLUTION: no solution found\n" );
       // TODO debug remove extra prints
-      FILE *file = fopen( std::string(StatisticsOut).c_str(), "a" );
-      if (file != nullptr )
-          fprintf( file, ">" );
+      if (statsFile != nullptr )
+          fprintf( statsFile, "!" );
     }
     else
     {
@@ -4497,6 +4499,9 @@ scheduler( schedule_t *schedule )
[…]

### 2014-04-25 AAAI_AuthorKit/paper.tex
Added random walks with additional domain tests and data analysis spreadsheet

--- 2014-04-11 AAAI_AuthorKit/paper.tex
@@
 \documentclass[letterpaper]{article}
+% AAAI format packages
 \usepackage{aaai}
@@
 \usepackage{courier}
+% Additional packages
+\usepackage{amsmath}
 \frenchspacing
@@
 \title{Bootstrapping Abstract Planning with Experience Graphs}
-\author{Aram Ebtekar, Maxim Likhachev\\
+\author{Aram Ebtekar, Maxim Likhachev, Mike Phillips, Sven Koenig\\
 Carnegie Mellon University\\
@@
 \section{Introduction}
-asdf
+Planning entails finding action sequences that achieve a goal state.
+In order to apply the language of graph theory, states are often thought of as nodes connected by actions.
+A \textit{plan} is a path from start to goal.
+Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.
+The reason usually is that the graphs involved are very large, in fact so large that they are never stored explicitly.
+Pieces may be generated dynamically as the search progresses, using a short description of the graph's structure.
+In motion planning, the space is often a continuous geometric set which is discretized during the search.
+In high-level logical planning, a domain language such as STRIPS or SAS+, or the more elaborate PDDL, is used.
+These short descriptions put structural constraints on the graph, which may be used to aid the search.
 
-\section{Algorithm}
+In order to create a domain-independent solver for a language such as STRIPS, we need to extract information about the problem automatically.
+
+We may view planning as a process that generates distance-to-goal labels for each node of a graph.
+Given these distance labels, it's a simple matter to generate a plan by successively moving to the optimal predecessor.
+Since there is no worst-case polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try to roughly approximate the distance labels.
+The approximate labels we call \textbf{heuristics}, and we use them in hopes of finding plans more efficiently.
+If the heuristic precisely reflects the true distances, we of course find a path immediately.
+Algorithms such as A* are designed to find solutions quickly whenever the heuristic is of reasonable quality.
+Note that in practice any subexponential algorithm can only afford to look at a subset of the nodes, so it is only for these that we compute the heuristic.
+If the heuristic is good, we hope not to have to look at (i.e.
+generate) too many nodes.
+Thus, there is a tradeoff between spending more time to get a tighter heuristic, vs evaluating a weaker heuristic more quickly but at many more nodes.
+
+However, even with a domain-independent heuristic, many STRIPS problems can be hard.
+Even humans have difficulty when faced with an unfamiliar puzzle.
+However, one would hope that a planning agent would learn to generalize solutions from past planning instances to similar new instances.
+A recent approach builds \textit{Experience graphs} to represent the high-level connectivity of the free space in motion planning tasks.
+The high-level idea is to remember previously generated paths so that, when a new start and goal is queries, a new path can be more quickly generated by reusing pieces of the E-graph.
+
+In section [???], we present the HSP heuristic for STRIPS.
+Then, we independently discuss E-graphs.
+This paper's novel contributions follow thereafter, when we extend E-graphs to STRIPS planning by fitting it on top of the HSP heuristic.
+We prove a few theoretical properties of this algorithm, most importantly its $\epsilon$-optimality guarantee, and then present experiments showing a class of problems in which this method achieves significant speedups over plain HSP.
+
+\section{Related Work}
+
+\section{HSP}
+
+A STRIPS problem is a tuple $P = \langle A,O,I,G\rangle$ of atoms $A$, operators $O$, an initial state $I \subset A$ and goal state $G \subset A$.
+Each operator $op\in O$ has precondition, add and delete lists: $Prec(op),Add(op),Del(op) \subset A$.
+The STRIPS problem $P$ defines a state space $\mathcal S = \langle S,s_0,S_G,\rangle$.
+
+To find optimal paths, we need a heuristic which underestimates true distances.
+A simple way to do this is to solve a relaxed version of the original problem, e.g.
+by ignoring certain constraints.
+The STRIPS representation is monotone, so one possible relaxation is to simply ignore the delete lists of operators.
+However, this relaxation is still hard to solve, as it includes subset-sum as a special case.
+One way to ensure a fast calculation is to cast aside the exponential state space by estimating the costs for achieving individual atoms.
+These costs can then be combined by taking their sum if the atoms are independent or, to ensure consistency in the general case, we can take their maximum.
+Thus,
+$h(S) = g_S(G)$ where \[g_S(a) = \begin{cases} 0  &\mbox{if } a \in S \\ 1 + \min_{op,a\in Add(op)} g(Prec(op))  &\mbox{otherwise} \end{cases}\]
+
+for atoms $a\in A$, and $g_S(P) = \max_{p\in P} g_S(p)$ for sets of atoms $P$.
+
+\section{Experience Graphs}
+
+\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(s_i,s_{i+1},c^E(s_i,s_{i+1})\}\] over all paths $pi = \langle s_0,s_1,...,s_N \rangle$ with $s_0 = S$ and $s_N = G$.
+
+\section{Algorithm Discussion and Analysis}
+
+For $S\in N^E$, we compute $h^E(S)$ by fusing the E-graph edges and off-E-graph estimates with Dijkstra's algorithm.
+The complexity of this pre-processing step is quadratic in the number of E-graph nodes.
+
+For $S\notin N^E$, \[h^E(S) = \min_{C\in N^E} \left( \epsilon^E g_S(C) + h^E(C) \right)\]
+
+\section{Experiments}
+
+\section{Conclusion and Extensions}
 

### 2014-04-25 TestSuite.sh

@@ -15,7 +15,8 @@
 #done
 
 #for dir in examples/*/
-for dir in "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
+#for dir in "examples/mprime/" "examples/openstacks/" "examples/parcprinter-strips/" "examples/pegsolitaire/"
+#for dir in "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
 do
 	mkdir -p Test/${dir}
 	for filename in ${dir}p*.pddl
@@ -24,6 +25,7 @@ do
 	then
 		#without file extension: Test/$(basename "$filename" .pddl).eg
 		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/${filename}.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
+		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/trash.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
 		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/${filename}.eg Test/trash.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
 	fi
 	done

### 2014-04-25 planner/planner.cpp

@@ -281,7 +281,8 @@ static procRegister_t *procStackTop = nullptr;
 
 /* random number generator */
 std::random_device randomDevice;
-std::mt19937_64 rng(randomDevice());
+//std::mt19937_64 rng(randomDevice());
+std::mt19937_64 rng;
 
 
 
@@ -2176,6 +2177,48 @@ printLists( void )
 **
 **/
 
+void
+randomWalk( atom_t* state, int steps )
+{
+  
+  atom_t prevState[MAXATOMPACKS];
+  while (steps--)
+  {
+    vector<int> ops;
+    int* p;
+    for( int* alpha = validOperators; *alpha != -1; ++alpha )
+    {
+      /* preconditions */
+      for( p = operatorTable[*alpha].prec; (*p != 0) && asserted( state, *p ); ++p );
+      if( *p == 0 )
+        ops.push_back(*alpha);
+    }
+    if (ops.empty())
+      break;
+    std::uniform_int_distribution<int> dist(0, ops.size()-1);
+    int op = ops[dist(rng)];
+    memcpy( prevState, state, SIZE_PACKS * sizeof( atom_t ) );
+    
+    /* operators effects */
+    for( int* a = operatorTable[op].add; *a != 0; ++a )
+      set( state, *a );
+    for( int* d = operatorTable[op].del; *d != 0; ++d )
+      clear( state, *d );
+    /* suboperators effects */
+    for( suboperator_t* sub = operatorTable[op].suboperators; sub != nullptr; sub = sub->next )
+    {
+      for( p = sub->prec; (*p != 0) && asserted( prevState, *p ); ++p );
+      if( *p == 0 )
+      {
+        for( int* a = sub->add; *a != 0; ++a )
+          set( state, *a );
+        for( int* d = sub->del; *d != 0; ++d )
+          clear( state, *d );
+      }
+    }
+  }
+}
+
 int
 forwardNodeExpansion( node_t *node, node_t ***result )
 {
@@ -3470,12 +3513,12 @@ initialize( void )
   /* goal state */
   int* p = _low_copyGoalAtoms;
   for( int* a = _low_goalAtoms; *a != 0; ++a )
-    {
-      set( staticGoalState, *a );
-      *p++ = *a;
-    }
+  {
+    set( staticGoalState, *a );
+    *p++ = *a;
+  }
   *p = 0;
-
+  
   /* operator instantiation */
   operatorCompilation();
 
[…]

### 2014-05-02 TestSuite.sh
No coin flips

@@ -17,6 +17,7 @@
 #for dir in examples/*/
 #for dir in "examples/mprime/" "examples/openstacks/" "examples/parcprinter-strips/" "examples/pegsolitaire/"
 #for dir in "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
+for dir in "examples/blocks/" "examples/elevators/" "examples/rovers/" "examples/satellite/"
 do
 	mkdir -p Test/${dir}
 	for filename in ${dir}p*.pddl

### 2014-05-02 planner/planner.cpp

@@ -3540,8 +3540,8 @@ initialize( void )
   /* TODO make random walks configurable: randomly move start and goal */
   if (EGraphOut == "Test/trash.eg")
   {
-    randomWalk(staticInitialState, 10);
-    randomWalk(staticGoalState, 10);
+    randomWalk(staticInitialState, 0);
+    randomWalk(staticGoalState, 0);
     p = _low_initialAtoms;
     for (size_t at = 1; at < SIZE_ATOMS; ++at)
       if ( asserted( staticInitialState, at ) )
@@ -3911,7 +3911,7 @@ readEGraph(string fileName)
 
 
 bool
-printEGraph(string fileName)
+printEGraph(string fileName, double proportion = 1)
 {
   FILE *file = fopen( fileName.c_str(), "w" );
   if (file == nullptr)
@@ -3923,32 +3923,37 @@ printEGraph(string fileName)
   // TODO remove debug code
   fprintf(statsFile, "ExpSize= %u ", experience.size());
   
-  std::uniform_real_distribution<double> dist(0, 1);
+  int n = experience.size();
+  int k = std::round(n * proportion);
   for (auto& exper: experience)
-  if (dist(rng) < 0.5) // TODO debug: randomly remember edges
   {
-    fprintf( file, "%s\n", exper.opName );
-    /*for (size_t i = 0; i < SIZE_PACKS; ++i)
-      fprintf( file, " %u", exper.tailState[i].pack );
-    for (size_t i = 0; i < SIZE_PACKS; ++i)
-      fprintf( file, " %u", exper.headState[i].pack );
-    fprintf( file, "\n" );*/
-    int atomsToPrint = 0;
-    for (size_t p = 1; p < SIZE_ATOMS; ++p)
-      if (asserted(exper.tailState, p))
-        ++atomsToPrint;
-    fprintf( file, "%u\n", atomsToPrint );
-    for (size_t p = 1; p < SIZE_ATOMS; ++p)
-      if (asserted(exper.tailState, p))
-        fprintf( file, "%s\n", readAtomName(p) );
-    atomsToPrint = 0;
-    for (size_t p = 1; p < SIZE_ATOMS; ++p)
-      if (asserted(exper.headState, p))
-        ++atomsToPrint;
-    fprintf( file, "%u\n", atomsToPrint );
-    for (size_t p = 1; p < SIZE_ATOMS; ++p)
-      if (asserted(exper.headState, p))
[…]

### 2014-05-05 AAAI_AuthorKit/paper.tex
Main background and algorithm discussion added to the paper

--- 2014-04-11 AAAI_AuthorKit/paper.tex
@@
 \usepackage{courier}
+% Additional packages
+\usepackage{amsmath}
+\usepackage{amssymb}
 \frenchspacing
@@
 \section{Introduction}
-asdf
+Planning entails finding action sequences that achieve a goal state.
+In order to apply the language of graph theory, states are often thought of as nodes connected by actions.
+A \textit{plan} is a path from start to goal.
+Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.
+The reason usually is that the graphs involved are very large, in fact so large that they cannot be stored explicitly.
+By either observing new states or using a compressed representation of the graph's structure, states may be generated dynamically as the search progresses.
+In motion planning, the space may be a continuous geometric set which is dynamically discretized.
 
-\section{Algorithm}
+In high-level logical planning, a domain language such as STRIPS, SAS+ or PDDL encode a graph whose size is exponential in its description length. 
+These short descriptions often create structure that can be exploited.
+In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret information about the problem.
+
+We may view planning as a process that generates distance-to-goal labels for each node of a graph.
+Given these distance labels, it's a simple matter to generate a plan by tracing steps from the goal, successively taking the optimal predecessor.
+Since there is no worst-case polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try to roughly approximate the distance labels.
+The approximate labels we call \textbf{heuristics}, and we use them in hopes of finding plans more efficiently.
+If the heuristic precisely reflects the true distances, we saw how to immediately find a path.
+Algorithms such as A* are designed to find solutions quickly whenever the heuristic is of reasonable quality.
+Note that in practice, any subexponential algorithm can only afford to look at a subset of the nodes, so it is only for these that we compute the heuristic.
+If the heuristic is good, we hope not to have to look at (i.e. generate) too many nodes.
+Hence, there is a tradeoff between spending more time to get a tighter heuristic, vs evaluating a weaker heuristic more quickly but at many more nodes.
+
+In practice, even with a domain-independent means of generating heuristics, many STRIPS problems can be hard.
+Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
+Thus, one would hope that a planning agent would similarly learn to generalize solutions from past planning instances to related new instances.
+A recent approach builds \textit{Experience graphs} to represent the high-level connectivity of the free space in motion planning tasks.
+The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be more quickly generated by reusing subpaths from the E-graph.
+However, E-graphs have never before been applied to high-level representations such as STRIPS. This is our present contribution.
+
+In section [???], we present the HSP heuristic for STRIPS.
+Then, we discuss E-graphs in more technical detail.
+This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by fitting it on top of the HSP heuristic.
+We prove a few theoretical properties of this algorithm, most notably its $\epsilon$-optimality guarantee, and then present experiments showing domains in which this method achieves significant speedups over plain HSP.
+
+\section{Related Work}
+
+\section{HSP}
+
+A STRIPS problem is a tuple $P = \langle A,O,I,G\rangle$ consisting of an atom set $A$, operator set $O$, initial state $I \subset A$ and goal condition $G \subset A$.
+Each operator $op\in O$ is defined by its cost and its precondition, add and delete lists: $Cost(op) \in \mathbb{R}^+$ and $Prec(op),Add(op),Del(op) \subset A$.
+
+The STRIPS problem $P$ defines a directed state graph $(V,c)$ where $V$ is the power set of $A$ (i.e. states $v\in V$ correspond to collections of atoms), and
+\begin{eqnarray*} c(u,v) = \inf\{Cost(op) \mid u\in Prec(op),
+\\v = u - Del(op) \cup Add(op)\} \end{eqnarray*}
+%consists of states transitions $(u,v)$ for which there exists an operator $op\in O$ with $u\in Prec(op)$ and $v = u - Del(op) \cup Add(op)$; the weight of this edge is the minimum cost of such an $op$.
+Naturally, $c(u,v) = \infty$ when there is no operator directly linking $u$ to $v$.
+Given a STRIPS problem $P$, we seek a low-cost path from the initial state $I\in V$ to any of the goal states $g\in V$ such that $g \supset G$.
+
+Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP planner, which we now describe.
+It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
+Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the resulting heuristic is admissible.
+
+However, even the relaxed STRIPS planning problem includes subset-sum as a special case, making it NP-hard.
+Intuitively, we see that the search space is still exponential.
+To simplify things, we decouple the atoms, instead estimating the cost to achieving each individual atom.
+
+Let's say we want to compute a distance-to-$G$ heuristic for a state $S$. Estimate the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+\[\begin{cases} 0  &\mbox{if } a \in S
+\\ \min_{op,a\in Add(op)} \left(g_S(Prec(op) + Cost(op))\right)  &\mbox{if } a \notin S \end{cases}\]
+
+Define the HSP-max heuristic by $h^{HSP}(S) = g_S(G)$, the estimated cost of achieving all atoms in $G$.
+In order to cheaply compute $g_S(G)$ and $g_S(Prec(op))$, we define $g_S(P) = \max_{p\in P} g_S(p)$ for sets of atoms $P$.
+This admissible and consistent.
+If the atoms were truly independent, a much tighter estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
+Despite its inadmissibility in general, the latter HSP-plus heuristic is often useful in practice, as it uses more information and biases more greedily toward the goal.
+
+From a computational perspective, the HSP heuristic must compute $g_S(a)$ for all $a\in A$ whenever a new state $S$ is generated.
+This can be done by dynamic programming, essentially searching forward from the atoms in $S$.
+In a sense, it seems we are wasting a lot of work by estimating the cost to reach every atom when we only require $g_S(G)$.
+Later, we'll see how to make fuller use of this computation.
+
+\section{Experience Graphs}
+
+E-graphs are used to optimize search time over multiple instances on the same graph.
+Between instances, we update the set of edges which constitute the E-graph, typically by adding the previous search's resulting path.
+If the heuristic search is done on a reduced state space by projection, the E-graph is considered as a subgraph of the latter.
+
+Suppose we are given a consistent heuristic $h(u,v)$ for the distance between arbitrary pairs of states.
+That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(g) = 0$ for every goal state $g$.
+In order to derive a related heuristic which biases in favor of using the E-Graph, we inflate the heuristic by a factor $\epsilon^E > 1$, but allow it to use uninflated ``shortcuts" on the E-graph.
+To be precise, the E-graph heuristic is defined by
+
+\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(s_i,s_{i+1}),c^E(s_i,s_{i+1})\}\]
+over all paths $\pi = \langle s_0,s_1,...,s_N \rangle$ with $s_0 = S$ and $s_N = G$.
+
+In the limit as $\epsilon^E \rightarrow 1$, the ``shortcuts" become pointless, so \[h^E(S) = \min_\pi \sum_i h(s_i,s_{i+1}) = h(s_0,s_N) = h(S,G)\]
+by the triangle inequality.
+Conversely as $\epsilon^E \rightarrow\infty$, the minimizing path becomes the one which uses the fewest edges outside the E-graph, and the cost remains finite iff $S$ and $G$ are in the same E-graph component.
+
+We cannot afford to compute $h^E$ according to its literal definition, as there are too many paths to consider.
+Fortunately, there is a practical means of computing it.
+By the triangle inequality, any pair of consecutive $h(s_i,s_{i+1})$ terms can be combined into one.
+Thus, we only need be concerned with states $s_i$ lying on the E-graph for $0 < i < N$.
+
+Let $V^E$ consist of the goal state G plus all endpoints of the E-graph's edges.
+In a preprocessing stage before a search, we can apply Dijkstra's algorithm once in reverse to compute the estimated distance $h^E(S)$ to $G$ from every point $S\in V^E$, using any combination of E-graph edges and ``jumps" with cost $\epsilon^E h(s_i,s_{i+1})$.
+This runs in $O(|V^E|^2)$ time, which is negligible when the E-graph is small.
+
+Later when expanding $S \notin V^E$, we see that we've already precomputed all but the first leg of the journey in the definition of $h^E(S)$. Thus, we derive the simpler computation
+\[h^E(S) = \min_{S'\in V^E} \left(\epsilon^E h(S,S') + h^E(S')\right)\]
+
+$h^E$ is $\epsilon^E$-consistent [cite].
+
+\section{Algorithm Discussion and Analysis}
+
+Now we combine the ideas from HSP and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
+In STRIPS, the consistent heuristic $h(u,v)$ is given by the HSP-max estimate $h^{HSP}_u(v)$.
+Thus, we can compute $h^{HSP}_u(v)$ for all $u,v\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before.
+Thus, our preprocessing work is roughly equivalent to that of generating $|V^E|$ states, which will be small.
+As before, Dijkstra's algorithm combines an inflation of these estimates with the E-graph edges themselves to derive $h^E(S)$ for all $S\in V^E$.
+
+Upon encountering a new state $S\notin V^E$, we use dynamic programming as before to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-graph heuristic as
+
+\[h^E(S) = \min_{S'\in V^E} \left( \epsilon^E g_S(S') + h^E(S') \right)\]
+
+Here we see that, when E-graphs are involved, $g_S(S')$ is computed for many states S', not just the goal.
+Thus, we consult the E-graph essentially for free since HSP would compute all the $g$-values anyway.
+The only additional work here is the minimization over $S'\in V^E$, which is negligible for small E-graphs.
+
+We should remark that, although STRIPS problem as we defined them have multiple goal states defined by the goal condition $G$, the heuristic's monotonicity implies that the set of atoms precisely matching $G$ will be the lowest-cost goal to reach in the heuristic approximation.
+
+\section{Experiments}
+
+\section{Conclusion and Extensions}
 

### 2014-05-09 AAAI_AuthorKit/paper.tex
minor, preparing for backup
Cleaned up algorithm discussion and analysis

--- 2014-04-11 AAAI_AuthorKit/paper.tex
@@
 \usepackage{courier}
+% Additional packages
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \frenchspacing
@@
 /Title (Bootstrapping Abstract Planning with Experience Graphs)
-/Author (Aram Ebtekar, Maxim Likhachev)}
+/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)}
 \setcounter{secnumdepth}{0}  
@@
 \title{Bootstrapping Abstract Planning with Experience Graphs}
-\author{Aram Ebtekar, Maxim Likhachev\\
+\author{Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig\\
 Carnegie Mellon University\\
@@
 \section{Introduction}
-asdf
+Planning entails finding action sequences that achieve a goal state.
+In order to apply the language of graph theory, states are often thought of as nodes connected by action transitions.
+A \textit{plan} is a path from start to goal.
+Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.
+The reason usually is that the graphs involved are very large, too large to store explicitly.
+By either recording newly observed states or using a compressed representation of the graph's structure, states may be generated dynamically as the search progresses.
+In motion planning, the space may be a continuous geometric set which is dynamically discretized.
 
-\section{Algorithm}
-When planning over possible states of the world, it's typically more efficient to describe the states in terms of a set of features.
-The set of states is exponential in the number of features, so even a small problem description may imply a large graph.
-In general, planning over such a large space is computationally infeasible.
+In high-level logical planning, a domain language such as STRIPS, SAS+, ADL or PDDL encode a graph whose size may be exponential in its description length. 
+These short descriptions sometimes encode exploitable structure.
+In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret information about the problem.
 
 We may view planning as a process that generates distance-to-goal labels for each node of a graph.
-Given these distance labels, it's a simple matter to generate a plan by successively moving to the cheapest neighbour.
-Since there is no deterministic polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try an approximation algorithm.
-The resulting labels we call \textbf{heuristics}, and we use them in hopes of achieving optimal or near-optimal plans more efficiently.
-If the heuristic precisely reflects the true distances, we find a path immediately.
-Algorithms such as A* are designed to find solutions quickly whenever the heuristic is reasonably tight and \textbf{$\epsilon$-consistent}.
-Note that in practice any subexponential algorithm can only afford to look at a subset of the nodes, so it is only for these that we compute the heuristic.
-If the heuristic is good, we hope not to have to look at (i.e.
-generate) too many nodes.
-Thus, there is a tradeoff between spending more time to get a tight heuristic, vs evaluating a weaker heuristic more quickly but also more frequently.
+Given these distance labels, it's a simple matter to generate a plan by tracing steps from the goal, successively taking the optimal predecessor.
+Since there is no worst-case polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try to roughly approximate the distance labels.
+The approximate labels we call \textbf{heuristics}, and we use them in hopes of finding plans more efficiently.
+If the heuristic precisely reflects the true distances, we saw how to immediately find a path.
+Algorithms such as A* are designed to find solutions quickly whenever the heuristic is of reasonable quality.
+Note that in practice, any subexponential algorithm can only afford to look at a small fraction of all states, so it is only for these that we compute the heuristic.
+If the heuristic is good, we hope not to have to look at (i.e. generate) too many states.
+Hence, there is a tradeoff between spending more time to compute a tighter heuristic, vs evaluating a weaker heuristic more quickly but at many more states.
+
+In practice, even with a domain-independent means of generating heuristics, STRIPS problems can be very difficult.
+Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
+Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
+A recent approach builds \textit{Experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks.
+The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be more quickly generated by reusing subpaths from the E-graph.
+However, E-graphs have never before been applied to high-level representations such as STRIPS. This is our present contribution.
+
+In section [???], we present the HSP heuristic for STRIPS.
+Then, we discuss E-graphs in more technical detail.
+This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by using it to augment the HSP heuristic. 
+The resulting A* search is complete with a configurable suboptimality bound.
+Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over plain HSP in several planning domains.
+
+\section{Related Work}
+
+\section{HSP}
+
+A STRIPS problem is a tuple $P = \langle A,O,I,G\rangle$ consisting of an atom set $A$, operator set $O$, initial state $I \subseteq A$ and goal condition $G \subseteq A$.
+Each operator $op\in O$ is defined by its cost and its precondition, add and delete lists: $Cost(op) \in \mathbb{R}^+$ and $Prec(op),Add(op),Del(op) \subseteq A$.
+
+The problem $P$ defines a directed state graph $(V,c)$ where $V$ is the power set of $A$ (i.e. states $S\in V$ correspond to collections of atoms), and the edge costs are
+\begin{eqnarray*} c(S,S') = \inf\{Cost(op) \mid S\subseteq Prec(op)\text{ and}
+\\S' = S - Del(op) \cup Add(op)\} \end{eqnarray*}
+%consists of states transitions $(u,v)$ for which there exists an operator $op\in O$ with $u\in Prec(op)$ and $v = u - Del(op) \cup Add(op)$; the weight of this edge is the minimum cost of such an $op$.
+Naturally, $c(S,S') = \infty$ when there is no operator directly transitioning from $S$ to $S'$.
+Given a STRIPS problem $P$, we seek a low-cost path from the initial state $I\in V$ to any of the goal states $S\in V$ such that $S \supset G$.
+
+Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP planner, which we now describe.
+It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
+Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the resulting heuristic is admissible.
+
+However, even the relaxed STRIPS planning problem includes set-cover as a special case, making it NP-hard.
+Intuitively, we see that the relaxed search space remains exponential.
+To reduce it, we decouple the atoms, instead estimating the cost of achieving each individual atom.
+
+Let's say we want to compute a distance-to-$G$ heuristic from a state $S$. Estimate the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+\[\begin{cases} 0  &\mbox{if } a \in S
+\\ \min_{op,a\in Add(op)} \left(g_S(Prec(op)) + Cost(op)\right)  &\mbox{if } a \notin S \end{cases}\]
+
+Define the HSP-max heuristic by \[h^{HSP}(S) = g_S(G),\] the estimated cost of achieving all atoms in $G$.
+In order to cheaply compute $g_S(G)$ and $g_S(Prec(op))$, we define $g_S(P) = \max_{p\in P} g_S(p)$ for sets of atoms $P$.
+This is admissible and consistent.
+If the atoms were truly independent, a much tighter estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
+Despite its inadmissibility in general, the latter HSP-plus heuristic is often useful in practice, as it uses more information and biases more greedily toward the goal.
+
+From a computational perspective, the HSP heuristic must compute $g_S(a)$ for all $a\in A$ whenever a new state $S$ is generated.
+This can be done by dynamic programming, iterating the recursive formula to a fixpoint in Bellman-Ford-like fashion.
+In a sense, it seems we are wasting a lot of work by estimating the cost to reach every atom when we only require $g_S(G)$.
+Later, we'll see how to make fuller use of this computation.
+
+\section{Experience Graphs}
+
+E-graphs can improve total search time over a series of related queries on the same graph.
+Between queries, we update the set of edges which constitute the E-graph, typically by adding the solution path from the previous search.
+In cases where the heuristic compution is done by searching on a state space that was reduced by projection, the E-graph is considered as a subgraph of the reduced space.
+
+Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
+That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(G) = 0$ whenever $G$ is a goal.
+In order to derive a related heuristic which biases in favor of using the E-Graph, we inflate the heuristic by a factor $\epsilon^E > 1$, but allow it to use uninflated ``shortcuts" on the E-graph.
+To be precise, the E-graph heuristic is defined by
+
+\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(s_i,s_{i+1}),c^E(s_i,s_{i+1})\}\]
+over all paths $\pi = \langle s_0,s_1,...,s_N \rangle$ with $s_0 = S$ and $s_N$ being any goal. $c^E$ are E-graph costs, or $\infty$ if the E-graph edge doesn't exist.
+
+In the limit as $\epsilon^E \rightarrow 1$, taking ``shortcuts" along the E-graph loses its advantage, so \[h^E(S) = \min_\pi \sum_i h(s_i,s_{i+1}) = \min_\pi h(s_0,s_N) = h(S,G)\]
+by the triangle inequality, where $G$ is the minimizing goal.
+
+Conversely as $\epsilon^E \rightarrow\infty$, the minimizing path becomes the one which uses the fewest edges outside the E-graph, and the cost remains finite iff the E-graph component of $S$ contains a goal state.
+
+We cannot afford to compute $h^E$ according to its literal definition, as there are far too many paths to consider.
+Fortunately, there exists a practical means of computing it.
+By the triangle inequality, any pair of consecutive $h(s_i,s_{i+1})$ terms can be combined into one.
+Thus for $0 < i < N$, we only need be concerned with states $s_i$ lying on the E-graph.
+
+Let $V^E$ consist of all goal states plus all endpoints of the E-graph's edges.
+In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$, optimizing over combinations of E-graph edges and ``jumps" of cost $\epsilon^E h(s_i,s_{i+1})$.
+If the blackbox heuristic $h$ is cheap to compute, this preprocessing runs in $O(|V^E|^2)$ time, which is negligible for small E-graphs.
+
+Later, when generating $S \notin V^E$, we see that we have already precomputed all but the first ``leg" of the path in the definition of $h^E(S)$.
+Thus, we derive the mathematically equivalent but much cheaper computation
+\[h^E(S) = \min_{S'\in V^E} \left(\epsilon^E h(S,S') + h^E(S')\right)\]
+
+$h^E$ is $\epsilon^E$-consistent [cite].
+
+\section{Algorithm Discussion and Analysis}
+
+Now we combine the ideas from HSP and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
+In STRIPS, the consistent heuristic $h(S,S')$ is given by the HSP-max estimate $h^{HSP}_S(S')$.
+We can compute $h^{HSP}_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before.
+
+Thus, our preprocessing work is roughly equivalent to that of generating $|V^E|$ states, which will be small.
+As before, Dijkstra's algorithm combines an inflation of these estimates with the E-graph edges to derive $h^E(S)$ for all $S\in V^E$.
+Note that in STRIPS, $V^E$ need not include every goal state: the minimal goal $G$ suffices as it's always the easiest to reach in the heuristic relaxation.
+
+Upon encountering a new state $S\notin V^E$, we run dynamic programming procedure again to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-graph heuristic by
+
+\[h^E(S) = \min_{S'\in V^E} \left( \epsilon^E g_S(S') + h^E(S') \right)\]
+
+Here we remark that, when E-graphs are involved, the values $g_S(S')$ appear on the right-hand side for multiple states S', not just $g_S(G)$.
+Since HSP would be computing all the $g$-values anyway, we get to consult the E-graph essentially for free.
+The only additional work here is the minimization over $S'\in V^E$, which is negligible for small E-graphs.
+A pseudocode implementation is listed in Algorithms \ref{alg:ComputeG} and \ref{alg:Search}.
+
+\begin{algorithm}
+\caption{ComputeG(S)}
+\label{alg:ComputeG}
+\begin{algorithmic}
+\FORALL{$a \in A$}
+\IF{$a \in S$}
+\STATE $g_S(a) \leftarrow 0$
+\ELSE
+\STATE $g_S(a) \leftarrow \infty$
+\ENDIF
+\ENDFOR
+\REPEAT
+\FORALL{$op \in O$}
+\STATE $pCost \leftarrow g_S(Prec(op))$
+\FORALL{$a \in Add(op)$}
+\STATE $g_S(a) \leftarrow \min \left(g_S(a),~pCost + Cost(op)\right)$
+\ENDFOR
+\ENDFOR
+\UNTIL{no further change in $g$-values}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Search()}
+\label{alg:Search}
+\begin{algorithmic}
+\STATE Let $c(S,S')$ for $S,S'\in V^E$ represent E-graph edge costs.
+\FORALL{$S \in V^E$}
+\STATE ComputeG(S)
+\FORALL{$S' \in V^E$}
+\STATE $c'(S,S') \leftarrow \min\left(c(S,S'),~\epsilon^E g_S(S')\right)$
+\ENDFOR
+\ENDFOR
+\STATE Compute $h^E$ on $V^E$ by reverse Dijkstra from $G$ with $c'$.
+\STATE Do $\epsilon$-weighted A* from $I$ on full graph with heuristic $h^E$:
+\FOR{$S \notin V^E$ when generated}
+\STATE ComputeG(S)
+\STATE $h^E(S) \leftarrow \min_{S'\in V^E} \left( \epsilon^E g_S(S') + h^E(S') \right)$
+\ENDFOR
+\IF{A* successfully found a path to some goal state $S \supseteq G$}
+\STATE Add all edges of the solution path to the E-graph.
+\RETURN solution path
+\ELSE
+\RETURN failure
+\ENDIF
+\end{algorithmic}
+\end{algorithm}
+
+ComputeG implements the dynamic programming computation of $g$-values.
+Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
+Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound is $O(\mathbf{A^2O})$.
+Thus, each state generated costs $O(\mathbf{A^2O + V^E})$ time, and the preprocessing cost is asymptotically equivalent to preemptively generating every state in $V^E$.
+
+\section{Experiments}
+
+\section{Conclusion and Extensions}
 

### 2014-05-09 AAAI_AuthorKit/paper.tex
Abstract and pentagon picture

@@
 \usepackage{algorithmic}
+\usepackage{graphicx}
 \frenchspacing
@@
 \pdfinfo{
-/Title (Bootstrapping Abstract Planning with Experience Graphs)
+/Title (STRIPS Planning with Experience Graphs)
 /Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)}
@@
 %
-\title{Bootstrapping Abstract Planning with Experience Graphs}
+\title{Experience-Biased Planning in STRIPS}
 \author{Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig\\
@@
 \begin{quote}
-A* and variants are regularly applied to plan paths in a graph.
-Rather than planning each query from scratch, we follow the recent trend across AI and robotics of collecting and reusing information, i.e.
-learning.
-Experience-graphs (E-graphs) store past plans in order to speed up related planning episodes in the future.
-New challenges arise when we try to apply E-graphs in high-level planning, where the state graph is implicitly exponentially sized in its description length.
-We describe an algorithm that combines E-graphs with a standard STRIPS relaxation to form $\epsilon$-admissible heuristics in a domain-independent manner.
+Experience graphs provide a means to augment existing heuristics with a bias toward using a select set of edges, typically taken from solutions to past queries.
+Thus, a planner can learn to bias its search toward well-understood regions and reuse parts of old plans.
+We show how to extend the HSP STRIPS planner with E-graphs at minimal cost, and in doing so speed up subsequent planning episodes across multiple domains.
 \end{quote}
@@
 
-\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(s_i,s_{i+1}),c^E(s_i,s_{i+1})\}\]
-over all paths $\pi = \langle s_0,s_1,...,s_N \rangle$ with $s_0 = S$ and $s_N$ being any goal. $c^E$ are E-graph costs, or $\infty$ if the E-graph edge doesn't exist.
+\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(S_i,S_{i+1}),c^E(S_i,S_{i+1})\}\]
+over all paths $\pi = \langle S_0,S_1,...,S_N \rangle$ with $S_0 = S$ and $S_N$ being any goal. $c^E$ are E-graph costs, or $\infty$ if the E-graph edge doesn't exist.
 
-In the limit as $\epsilon^E \rightarrow 1$, taking ``shortcuts" along the E-graph loses its advantage, so \[h^E(S) = \min_\pi \sum_i h(s_i,s_{i+1}) = \min_\pi h(s_0,s_N) = h(S,G)\]
+In the limit as $\epsilon^E \rightarrow 1$, taking ``shortcuts" along the E-graph loses its advantage, so \[h^E(S) = \min_\pi \sum_i h(S_i,S_{i+1}) = \min_\pi h(S_0,S_N) = h(S,G)\]
 by the triangle inequality, where $G$ is the minimizing goal.
 
-Conversely as $\epsilon^E \rightarrow\infty$, the minimizing path becomes the one which uses the fewest edges outside the E-graph, and the cost remains finite iff the E-graph component of $S$ contains a goal state.
+Conversely as $\epsilon^E \rightarrow\infty$, the minimizing path becomes the one which uses the fewest edges outside the E-graph, and the cost remains finite iff $S$ is in an E-graph component which also contains a goal state.
 
@@
 Fortunately, there exists a practical means of computing it.
-By the triangle inequality, any pair of consecutive $h(s_i,s_{i+1})$ terms can be combined into one.
-Thus for $0 < i < N$, we only need be concerned with states $s_i$ lying on the E-graph.
+By the triangle inequality, any pair of consecutive $h(S_i,S_{i+1})$ terms can be combined into one.
+Thus for $0 < i < N$, we only need be concerned with states $S_i$ lying on the E-graph.
 
 Let $V^E$ consist of all goal states plus all endpoints of the E-graph's edges.
-In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$, optimizing over combinations of E-graph edges and ``jumps" of cost $\epsilon^E h(s_i,s_{i+1})$.
+In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$, optimizing over combinations of E-graph edges and ``jumps" of cost $\epsilon^E h(S_i,S_{i+1})$.
 If the blackbox heuristic $h$ is cheap to compute, this preprocessing runs in $O(|V^E|^2)$ time, which is negligible for small E-graphs.
@@
 
-\section{Experiments}
+By comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
+The E-graph search maintains completeness and $\epsilon \epsilon^E$-suboptimality bounds on the path found.
+However, it makes no guarantee of improving the search time.
+Potential gains depend entirely on choosing a good small set of edges to call our E-graph.
+In our experiments we simply keep the previous solution path, but different choices remain a topic of investigation for future research.
 
-\section{Conclusion and Extensions}
+\includegraphics[scale=0.4]{Pentagon.png}
+
+\section{Experimental Setup}
+
+We augmented the HSP planner code [CITE] which won [AI COMPETITION IN 2000] with E-graphs.
+Our aim is to observe the effect of E-graphs on planning time given that we've already solved a closely related problem.
+To measure this, we run three searches for each problem instance.
+First, we run the original problem using standard HSP.
+Then, we generate a modified problem by moving the start and goal nodes randomly for X steps each.
+The second search solves the modified problem in the standard way.
+Finally, the third search solves the modified problem using as E-graph a random Y\% of the path returned from the first search.
+The reason for saving only a portion of the previous experience is to simulate the effects of disconnected E-graphs, as might arise after multiple searches.
+Our main comparisons will be between the number of nodes generated in the second and third searches.
+In practice, the times followed similar ratios to the number of nodes generated; as one would expect from the analyis in [PREVIOUS SECTION] since the E-graph resulting from Y\% of a single path is very small.
+
+\section{Experimental Results}
+
+\begin{center}
+    \begin{tabular}{| l | l | l | l |}
+    \hline
+    Domain & 0 steps & 10 steps & 20 steps
+    \\ \hline
+    BlocksWord & 0 & 0 & 0
+    \\ \hline
+    Grid & 0 & 0 & 0
+    \\ \hline
+    Satellite & 0 & 0 & 0
+    \\ \hline
+    \end{tabular}
+\end{center}
+
+\section{Conclusions and Extensions}
+
+Generalization from experiences
+
+Alternative E-graph edge-selection schemes (complete graph on $V^E$?)
+
+What if graph changes? Anytime incremental...
 

### 2014-05-10 AAAI_AuthorKit/paper.tex
Mike's edits

@@
 \pdfinfo{
-/Title (STRIPS Planning with Experience Graphs)
+/Title (Experience-Biased Symbolic Planning)
 /Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)}
@@
 %
-\title{Experience-Biased Planning in STRIPS}
+\title{Experience-Biased Symbolic Planning}
 \author{Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig\\
@@
 \begin{quote}
+Weighted-heuristic A* search is a standard technique in currently state-of-the-art domain-independent symbolic planners.
 Experience graphs provide a means to augment existing heuristics with a bias toward using a select set of edges, typically taken from solutions to past queries.
 Thus, a planner can learn to bias its search toward well-understood regions and reuse parts of old plans.
-We show how to extend the HSP STRIPS planner with E-graphs at minimal cost, and in doing so speed up subsequent planning episodes across multiple domains.
+We show how to extend the HSP STRIPS planner with E-graphs at minimal cost.
+In doing so, we maintain the ability to configure path cost suboptimality guarantees, while in practice speeding up subsequent planning episodes across multiple domains.
 \end{quote}
@@
 In order to apply the language of graph theory, states are often thought of as nodes connected by action transitions.
-A \textit{plan} is a path from start to goal.
+A \textbf{plan} is a path from the start state to one of many goal states.
 Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.
-The reason usually is that the graphs involved are very large, too large to store explicitly.
-By either recording newly observed states or using a compressed representation of the graph's structure, states may be generated dynamically as the search progresses.
-In motion planning, the space may be a continuous geometric set which is dynamically discretized.
 
-In high-level logical planning, a domain language such as STRIPS, SAS+, ADL or PDDL encode a graph whose size may be exponential in its description length. 
-These short descriptions sometimes encode exploitable structure.
-In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret information about the problem.
+The reason usually is that the graphs involved are very large; indeed, too large for explicit storage.
+In motion planning, the state space may be a continuous geometric set whose desired discretization is very fine.
+In symbolic planning, a planning language such as STRIPS, SAS+, ADL or PDDL [CITE] is chosen to give a compressed symbolic representation.
+
+The graph is exponentially larger than its encoding so, in both cases, states are generated only as needed.
+The compressed representation sometimes encodes exploitable structure.
+In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret structural information about the problem.
 
 We may view planning as a process that generates distance-to-goal labels for each node of a graph.
-Given these distance labels, it's a simple matter to generate a plan by tracing steps from the goal, successively taking the optimal predecessor.
+Given these distance labels, it's a simple matter to generate a plan by tracing steps from the start, successively taking the optimal successor.
 Since there is no worst-case polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try to roughly approximate the distance labels.
+
 The approximate labels we call \textbf{heuristics}, and we use them in hopes of finding plans more efficiently.
-If the heuristic precisely reflects the true distances, we saw how to immediately find a path.
+If the heuristic precisely reflects the true distances, we can immediately retrieve a path.
 Algorithms such as A* are designed to find solutions quickly whenever the heuristic is of reasonable quality.
-Note that in practice, any subexponential algorithm can only afford to look at a small fraction of all states, so it is only for these that we compute the heuristic.
+If we hope to take subexponential time, we can only afford to examine a vanishing fraction of the states, and it is only for these that we compute the heuristic.
 If the heuristic is good, we hope not to have to look at (i.e. generate) too many states.
-Hence, there is a tradeoff between spending more time to compute a tighter heuristic, vs evaluating a weaker heuristic more quickly but at many more states.
+Hence, there is a tradeoff between spending more time to compute a more accurage heuristic, vs evaluating a weaker heuristic quickly but at many more states.
 
@@
 A recent approach builds \textit{Experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks.
-The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be more quickly generated by reusing subpaths from the E-graph.
+The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be quickly generated by reusing subpaths from the E-graph.
 However, E-graphs have never before been applied to high-level representations such as STRIPS. This is our present contribution.
@@
 This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by using it to augment the HSP heuristic. 
-The resulting A* search is complete with a configurable suboptimality bound.
-Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over plain HSP in several planning domains.
+The resulting A* search is complete with a configurable suboptimality guarantee.
+Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over experience-free HSP in several planning domains.
 
@@
 
-\section{HSP}
+\section{STRIPS Language}
 
 A STRIPS problem is a tuple $P = \langle A,O,I,G\rangle$ consisting of an atom set $A$, operator set $O$, initial state $I \subseteq A$ and goal condition $G \subseteq A$.
-Each operator $op\in O$ is defined by its cost and its precondition, add and delete lists: $Cost(op) \in \mathbb{R}^+$ and $Prec(op),Add(op),Del(op) \subseteq A$.
+Each operator $op\in O$ is defined by its cost, preconditions, add effects and delete effects: $Cost(op) \in \mathbb{R}^+$ and $Prec(op),Add(op),Del(op) \subseteq A$.
 
 The problem $P$ defines a directed state graph $(V,c)$ where $V$ is the power set of $A$ (i.e. states $S\in V$ correspond to collections of atoms), and the edge costs are
-\begin{eqnarray*} c(S,S') = \inf\{Cost(op) \mid S\subseteq Prec(op)\text{ and}
-\\S' = S - Del(op) \cup Add(op)\} \end{eqnarray*}
+\begin{eqnarray*} c(S,S') = \min\{Cost(op) \mid S\subseteq Prec(op)\text{ and}
+\\S' = \left(S \setminus Del(op)\right) \cup Add(op)\} \end{eqnarray*}
 %consists of states transitions $(u,v)$ for which there exists an operator $op\in O$ with $u\in Prec(op)$ and $v = u - Del(op) \cup Add(op)$; the weight of this edge is the minimum cost of such an $op$.
-Naturally, $c(S,S') = \infty$ when there is no operator directly transitioning from $S$ to $S'$.
+By default, $c(S,S') = \infty$ when there is no operator directly transitioning from $S$ to $S'$.
 Given a STRIPS problem $P$, we seek a low-cost path from the initial state $I\in V$ to any of the goal states $S\in V$ such that $S \supset G$.
+
+\section{HSP Heuristic}
 
@@
 It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
-Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the resulting heuristic is admissible.
+Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the resulting heuristic never overestimates the true cost.
 
@@
 Intuitively, we see that the relaxed search space remains exponential.
-To reduce it, we decouple the atoms, instead estimating the cost of achieving each individual atom.
+To reduce it, HSP decouples the atoms, instead estimating the cost of achieving each individual atom.
 
-Let's say we want to compute a distance-to-$G$ heuristic from a state $S$. Estimate the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+Let's say we want to compute a distance-to-$G$ heuristic from a state $S$. HSP estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
 \[\begin{cases} 0  &\mbox{if } a \in S
-\\ \min_{op,a\in Add(op)} \left(g_S(Prec(op)) + Cost(op)\right)  &\mbox{if } a \notin S \end{cases}\]
+\\ \min_{op\mid a\in Add(op)} \left(g_S(Prec(op)) + Cost(op)\right)  &\mbox{if } a \notin S \end{cases}\]
 
-Define the HSP-max heuristic by \[h^{HSP}(S) = g_S(G),\] the estimated cost of achieving all atoms in $G$.
-In order to cheaply compute $g_S(G)$ and $g_S(Prec(op))$, we define $g_S(P) = \max_{p\in P} g_S(p)$ for sets of atoms $P$.
-This is admissible and consistent.
-If the atoms were truly independent, a much tighter estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
-Despite its inadmissibility in general, the latter HSP-plus heuristic is often useful in practice, as it uses more information and biases more greedily toward the goal.
+The HSP heuristic is defined by
+\[h^{HSP}(S) = g_S(G),\]
+the estimated cost of achieving all atoms in $G$. Note that $g_S(\cdot)$ is evaluated on certain atom sets, namely $Prec(op)$ and $G$.
+To keep the computations feasible, define $g_S(P) = \max_{p\in P} g_S(p)$ for atom sets $P$.
+The resulting HSP-max heuristic is an underestimate; indeed, it satisfies a stronger property called \textbf{consistency}.
+
+\textbf{Definition+Theorem (needs TeX formatting):} a heuristic $h$ is called $\epsilon$-consistent if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
+This property suffices to guarantee that each state is expanded only once by A*, and that the path it finds costs no more than $\epsilon$ times the optimal path.
+Consistency is synonymous with $1$-consistency.
+
+If the atoms were truly independent, a more accurate estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
+Despite its inconsistency in general, the latter HSP-plus heuristic is often useful in practice, as it uses more information and biases more greedily toward the goal.
 
@@
 In a sense, it seems we are wasting a lot of work by estimating the cost to reach every atom when we only require $g_S(G)$.
-Later, we'll see how to make fuller use of this computation.
+Later, we'll see how to make better use of this computation.
 
@@
 E-graphs can improve total search time over a series of related queries on the same graph.
-Between queries, we update the set of edges which constitute the E-graph, typically by adding the solution path from the previous search.
-In cases where the heuristic compution is done by searching on a state space that was reduced by projection, the E-graph is considered as a subgraph of the reduced space.
+Formally, an E-graph is a subgraph of the state space.
+We update it between queries, typically by adding the solution path from the previous search query.
 
 Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
-That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(G) = 0$ whenever $G$ is a goal.
-In order to derive a related heuristic which biases in favor of using the E-Graph, we inflate the heuristic by a factor $\epsilon^E > 1$, but allow it to use uninflated ``shortcuts" on the E-graph.
-To be precise, the E-graph heuristic is defined by
+That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(S,S) = 0$ for all $S\in V$.
+The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
+To be precise, define
 
-\[h^E(S) = \min_\pi \sum_i \min \{\epsilon^E h(S_i,S_{i+1}),c^E(S_i,S_{i+1})\}\]
-over all paths $\pi = \langle S_0,S_1,...,S_N \rangle$ with $S_0 = S$ and $S_N$ being any goal. $c^E$ are E-graph costs, or $\infty$ if the E-graph edge doesn't exist.
+\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \{\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\}\]
+over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$.
 
-In the limit as $\epsilon^E \rightarrow 1$, taking ``shortcuts" along the E-graph loses its advantage, so \[h^E(S) = \min_\pi \sum_i h(S_i,S_{i+1}) = \min_\pi h(S_0,S_N) = h(S,G)\]
-by the triangle inequality, where $G$ is the minimizing goal.
+$c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.
 
-Conversely as $\epsilon^E \rightarrow\infty$, the minimizing path becomes the one which uses the fewest edges outside the E-graph, and the cost remains finite iff $S$ is in an E-graph component which also contains a goal state.
+In the limit as $\epsilon^E \rightarrow 1$, following E-graph edges offers no advantage as $h$ is already an underestimate. Hence, using the triangle inequality to coalesce the sum,
+\begin{eqnarray*}h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N h(S_{i-1},S_i) = \min_{N,S_N,\pi} h(S_0,S_N)
+\\= \min_{S_N} h(S_0,S_N)\end{eqnarray*}
+
+Conversely as $\epsilon^E \rightarrow\infty$, the cost remains bounded iff $S_0$ is in an E-graph component which also contains a goal state, and the minimizing path becomes the one which uses the fewest edges outside the E-graph.
 
@@
 Fortunately, there exists a practical means of computing it.
-By the triangle inequality, any pair of consecutive $h(S_i,S_{i+1})$ terms can be combined into one.
-Thus for $0 < i < N$, we only need be concerned with states $S_i$ lying on the E-graph.
+By the triangle inequality, any consecutive pair of $h(S_{i-1},S_i)$ terms can be merged into one.
+Thus we lose no generality in restricting $S_i$ to lie on the E-graph for $0 < i < N$.
 
-Let $V^E$ consist of all goal states plus all endpoints of the E-graph's edges.
-In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$, optimizing over combinations of E-graph edges and ``jumps" of cost $\epsilon^E h(S_i,S_{i+1})$.
+Let $V^E$ be the union of the goal states and the E-graph's vertices.
+In addition to following E-graph edges, we imagine it's possible to ``jump" from $S$ to $S'$ with cost $\epsilon^E h(S,S')$. That is, let $c'(S,S') = \min\left(c(S,S'),~\epsilon^E g_S(S')\right)$
+
+In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
 If the blackbox heuristic $h$ is cheap to compute, this preprocessing runs in $O(|V^E|^2)$ time, which is negligible for small E-graphs.
 
-Later, when generating $S \notin V^E$, we see that we have already precomputed all but the first ``leg" of the path in the definition of $h^E(S)$.
+Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of $\pi$ according to the definition of $h^E(S)$.
 Thus, we derive the mathematically equivalent but much cheaper computation
@@
 In STRIPS, the consistent heuristic $h(S,S')$ is given by the HSP-max estimate $h^{HSP}_S(S')$.
-We can compute $h^{HSP}_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before.
+We can compute $h^{HSP}_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before: each run gives us $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.
 
@@
 
-Here we remark that, when E-graphs are involved, the values $g_S(S')$ appear on the right-hand side for multiple states S', not just $g_S(G)$.
-Since HSP would be computing all the $g$-values anyway, we get to consult the E-graph essentially for free.
-The only additional work here is the minimization over $S'\in V^E$, which is negligible for small E-graphs.
+We remark that, when E-graphs are involved, the values $g_S(S')$ on the right-hand side range over a variety of different states $S'$.
+Compare this to the formula for $h^{HSP}$, which uses only $g_S(G)$.
+HSP would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-graph essentially for free.
+The only additional work is the minimization over $S'\in V^E$, which is negligible for small E-graphs.
 A pseudocode implementation is listed in Algorithms \ref{alg:ComputeG} and \ref{alg:Search}.

### 2014-05-11 AAAI_AuthorKit/paper.tex
SoCS Abstract-ready version

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{algorithm}
@@
 \usepackage{graphicx}
+\newtheorem{thm}{Theorem}
+\newtheorem{defn}{Definition}
+% END Additional packages
 \frenchspacing
@@
 \begin{quote}
-Weighted-heuristic A* search is a standard technique in currently state-of-the-art domain-independent symbolic planners.
-Experience graphs provide a means to augment existing heuristics with a bias toward using a select set of edges, typically taken from solutions to past queries.
-Thus, a planner can learn to bias its search toward well-understood regions and reuse parts of old plans.
-We show how to extend the HSP STRIPS planner with E-graphs at minimal cost.
-In doing so, we maintain the ability to configure path cost suboptimality guarantees, while in practice speeding up subsequent planning episodes across multiple domains.
+Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
+An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
+Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
+In this paper, we demonstrate how to augment symbolic planners with
+experience graphs, using the HSP STRIPS planner as a representative
+example.
+The resulting planners are able to trade off seamlessly
+between plan quality and runtime and thus have advantages over past
+plan-reuse techniques, such as planning by analogy.
+We demonstrate
+experimentally that our planner speeds up HSP by a factor of 2 or more on
+many domains while achieving about the same plan quality.
 \end{quote}
@@
 
-\textbf{Definition+Theorem (needs TeX formatting):} a heuristic $h$ is called $\epsilon$-consistent if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
-This property suffices to guarantee that each state is expanded only once by A*, and that the path it finds costs no more than $\epsilon$ times the optimal path.
-Consistency is synonymous with $1$-consistency.
+\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
+$h$ is \textbf{consistent} if it is $1$-consistent.
+\end{defn}
+\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost.  \end{thm}
 
@@
 In the limit as $\epsilon^E \rightarrow 1$, following E-graph edges offers no advantage as $h$ is already an underestimate. Hence, using the triangle inequality to coalesce the sum,
-\begin{eqnarray*}h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N h(S_{i-1},S_i) = \min_{N,S_N,\pi} h(S_0,S_N)
-\\= \min_{S_N} h(S_0,S_N)\end{eqnarray*}
+\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N h(S_{i-1},S_i) = \min_{S_N} h(S_0,S_N)\]
 
@@
 
-In a preprocessing stage before the main search, we can apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
-If the blackbox heuristic $h$ is cheap to compute, this preprocessing runs in $O(|V^E|^2)$ time, which is negligible for small E-graphs.
+In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
+If the blackbox heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is negligible for small E-graphs.
 
@@
 
-$h^E$ is $\epsilon^E$-consistent [cite].
+\begin{thm}$h^E$ is $\epsilon^E$-consistent. [cite]\end{thm}
 
-\section{Algorithm Discussion and Analysis}
+\includegraphics[scale=0.4]{Pentagon.png}
+
+This figure illustrates the idea.
+Dark edges have cost 3 and are in the E-graph.
+Light edges represent the jumps $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
+Dijkstra's algorithm is used to compute the $h^E$ values shown alongside each node.
+
+\section{Experience-Biased HSP}
 
@@
 A pseudocode implementation is listed in Algorithms \ref{alg:ComputeG} and \ref{alg:Search}.
+The parameter $\epsilon^E$ controls bias toward the E-graph, while $\epsilon$ provides an additional goal-directed bias.
 
@@
 \STATE Compute $h^E$ on $V^E$ by reverse Dijkstra from $G$ with $c'$.
-\STATE Do $\epsilon$-weighted A* from $I$ on full graph with heuristic $h^E$:
+\STATE Run A* on the full graph from $I$ with heuristic $\epsilon h^E$:
 \FOR{$S \notin V^E$ when generated}
@@
 Thus, each state generated costs $O(\mathbf{A^2O + V^E})$ time, and the preprocessing cost is asymptotically equivalent to preemptively generating every state in $V^E$.
+For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
 
-By comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
-The E-graph search maintains completeness and $\epsilon \epsilon^E$-suboptimality bounds on the path found.
+By $\epsilon\epsilon^E$-consistency of the weighted heuristic $\epsilon h^E$, the E-graph search is complete and the path it finds is guaranteed to be at most $\epsilon \epsilon^E$-suboptimal.
 However, it makes no guarantee of improving the search time.
 Potential gains depend entirely on choosing a good small set of edges to call our E-graph.
-In our experiments we simply keep the previous solution path, but different choices remain a topic of investigation for future research.
-
-\includegraphics[scale=0.4]{Pentagon.png}
+In our experiments we simply keep the previous solution path; different choices remain a topic of investigation for future research.
 

### 2014-05-11 AAAI_AuthorKit/paper.tex
Grad AI version

@@
 /Title (Experience-Biased Symbolic Planning)
-/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)}
+/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)
+/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
+}
 \setcounter{secnumdepth}{0}  
@@
 \title{Experience-Biased Symbolic Planning}
-\author{Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig\\
+\author{Aram Ebtekar \and Mike Phillips \and Maxim Likhachev\\
 Carnegie Mellon University\\
@@
 Pittsburgh, PA 15213\\
+\And Sven Koenig\\
+University of Southern California\\
+Los Angeles, CA 90089
 }
@@
 
-In practice, even with a domain-independent means of generating heuristics, STRIPS problems can be very difficult.
+In practice, even using state-of-the-art methods to generate heuristics on isolated planning instances, STRIPS problems can be very difficult to solve without domain knowledge.
 Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
 Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
-A recent approach builds \textit{Experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks.
+A recent approach builds \textbf{Experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
 The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be quickly generated by reusing subpaths from the E-graph.
@@
 
-Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP planner, which we now describe.
+Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP planner \cite{bonet2001planning}, which we now describe.
 It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
@@
 
-Let's say we want to compute a distance-to-$G$ heuristic from a state $S$. HSP estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+Let's say we want a heuristic estimate of the distance from $S$ to a goal that contains $G$. HSP estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
 \[\begin{cases} 0  &\mbox{if } a \in S
@@
 
-The HSP heuristic is defined by
+The HSP heuristic is then defined by
 \[h^{HSP}(S) = g_S(G),\]
@@
 
-\begin{thm}$h^E$ is $\epsilon^E$-consistent. [cite]\end{thm}
+\begin{thm}$h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}
 
@@
 
-This figure illustrates the idea.
-Dark edges have cost 3 and are in the E-graph.
-Light edges represent the jumps $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
-Dijkstra's algorithm is used to compute the $h^E$ values shown alongside each node.
+The above figure illustrates the idea.
+Suppose the dark edges have cost 3 and make up the E-graph.
+Non-E-graph edges are not shown; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
+Dijkstra's algorithm follows the edges backward to compute the $h^E$ values shown alongside each node.
+
+$G$ is on the E-graph, though this need not be the case in general.
+$V^E$ is the pentagon on the right, and its $h^E$ values are precomputed before the search.
+$h^E(S)$ is computed only when A* generates $S\notin V^E$.
 
@@
 Now we combine the ideas from HSP and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
-In STRIPS, the consistent heuristic $h(S,S')$ is given by the HSP-max estimate $h^{HSP}_S(S')$.
+In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $h^{HSP}_S(S')$.
 We can compute $h^{HSP}_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before: each run gives us $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.
@@
 \STATE Run A* on the full graph from $I$ with heuristic $\epsilon h^E$:
-\FOR{$S \notin V^E$ when generated}
+\FOR{$S \notin V^E$ when generated by A*}
 \STATE ComputeG(S)
@@
 Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound is $O(\mathbf{A^2O})$.
-Thus, each state generated costs $O(\mathbf{A^2O + V^E})$ time, and the preprocessing cost is asymptotically equivalent to preemptively generating every state in $V^E$.
+Thus, each state generated costs $O(\mathbf{A^2O + V^E})$ time.
+The preprocessing cost is $O(\mathbf{A^2OV^E + (V^E)^2})$, asymptotically equivalent to preemptively generating every state in $V^E$.
 For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
@@
 
-We augmented the HSP planner code [CITE] which won [AI COMPETITION IN 2000] with E-graphs.
+We augmented the HSP planner code \cite{bonet2001planning} which won [AI COMPETITION IN 2000] with E-graphs.
 Our aim is to observe the effect of E-graphs on planning time given that we've already solved a closely related problem.
@@
 The second search solves the modified problem in the standard way.
-Finally, the third search solves the modified problem using as E-graph a random Y\% of the path returned from the first search.
+Finally, the third search solves the modified problem using as E-graph a random Y\% of the path obtained from the first search.
 The reason for saving only a portion of the previous experience is to simulate the effects of disconnected E-graphs, as might arise after multiple searches.
@@
 \section{Experimental Results}
+
+\includegraphics[scale=0.4]{AIPlot.png}
+
+The plot shows speedup (i.e.
+ratio of nodes generated in the second and third searches) against a measure of problem size (i.e.
+nodes generated in the second search).
+Planning times followed similar trends as node generation counts, as one would expect from the analyis since the E-graph resulting from a half-path is very small.
+We see considerable speedups in many domains, while the plan costs stayed roughly the same (in fact, they became slightly shorter on average).
+Many domains saw no discernable effect, but none were significantly hurt by E-graphs.
 
@@
 
-Generalization from experiences
+We saw that by reusing pieces from past plans, planning time can often be reduced.
+Many interesting directions remain for future investigation.
+The E-graph cannot be allowed to grow without bound over countless planning episodes, so a better scheme is needed for expansion and pruning as the agent learns.
 
-Alternative E-graph edge-selection schemes (complete graph on $V^E$?)
+Distinct states in STRIPS can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches.
 
@@
 
+\bibliographystyle{aaai}
+\bibliography{paper.bib}
+
 \end{document}

### 2014-05-11 AAAI_AuthorKit/paper.tex
Theorem 3

@@
 
-By $\epsilon\epsilon^E$-consistency of the weighted heuristic $\epsilon h^E$, the E-graph search is complete and the path it finds is guaranteed to be at most $\epsilon \epsilon^E$-suboptimal.
-However, it makes no guarantee of improving the search time.
-Potential gains depend entirely on choosing a good small set of edges to call our E-graph.
-In our experiments we simply keep the previous solution path; different choices remain a topic of investigation for future research.
+\begin{thm}
+Provided there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
+\end{thm}
+
+This follows directly from Theorems 1 and 2, since the weighted heuristic $\epsilon h^E$ is $\epsilon \epsilon^E$-consistent.
+However, E-graphs make no guarantee of improving the search time. Indeed, biasing toward bad regions could trap the planner inside large local optima.
+Potential gains depend entirely on choosing a good small set of edges to form our E-graph.
+In our experiments, we simply keep the previous solution path; different choices remain a topic for future investigations.
 

### 2014-05-12 AAAI_AuthorKit/paper.tex
Expanded notes on epsilon -> infinity

@@
 
-Conversely as $\epsilon^E \rightarrow\infty$, the cost remains bounded iff $S_0$ is in an E-graph component which also contains a goal state, and the minimizing path becomes the one which uses the fewest edges outside the E-graph.
+Conversely, as $\epsilon^E \rightarrow\infty$, the inflated terms dominate.
+Hence, the minimizing path becomes the one which incurs the least estimated cost outside the E-graph.
+In particular, $h^E$ has the following property:
+
+\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A* guided by $h^E$ with large bias term $\epsilon^E$ will never leave the E-graph.
+If the E-graph is small, a solution would promptly be discovered.
 

### 2014-05-12 AAAI_AuthorKit/paper.tex
References section

@@
 Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
-That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(S,S) = 0$ for all $S\in V$.
+That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
 The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
@@
 
-\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A* guided by $h^E$ with large bias term $\epsilon^E$ will never leave the E-graph.
+\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-graph.
 If the E-graph is small, a solution would promptly be discovered.
@@
 In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
-If the blackbox heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is negligible for small E-graphs.
+If the heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-graphs and goal sets.
 
@@
 Suppose the dark edges have cost 3 and make up the E-graph.
-Non-E-graph edges are not shown; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
-Dijkstra's algorithm follows the edges backward to compute the $h^E$ values shown alongside each node.
+Off-E-graph edges are not shown, as they are only accessed indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
+Dijkstra's algorithm follows dark and light edges backward to compute the $h^E$ values shown alongside each node.
 
@@
 $V^E$ is the pentagon on the right, and its $h^E$ values are precomputed before the search.
-$h^E(S)$ is computed only when A* generates $S\notin V^E$.
+For $S\notin V^E$, $h^E(S)$ is computed only when A* generates $S$.
 
@@
 \bibliographystyle{aaai}
-\bibliography{paper.bib}
+\bibliography{paper}
 

### 2014-05-12 AAAI_AuthorKit/paper.tex
New section: Analysis of HSPr

@@
 
-\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-graph.
+\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.}
+
+This means, for instance, that if the E-graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-graph.
 If the E-graph is small, a solution would promptly be discovered.
+In this manner, little work is needed to solve previously encountered subproblems.
 
@@
 HSP would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-graph essentially for free.
-The only additional work is the minimization over $S'\in V^E$, which is negligible for small E-graphs.
+The only additional work is the minimization over $S'\in V^E$, which takes O($|V^E||A|$) time.
 A pseudocode implementation is listed in Algorithms \ref{alg:ComputeG} and \ref{alg:Search}.
@@
 \begin{algorithm}
-\caption{ComputeG(S)}
+\caption{ComputeG($S$)}
 \label{alg:ComputeG}
@@
 \FORALL{$S \in V^E$}
-\STATE ComputeG(S)
+\STATE ComputeG($S$)
 \FORALL{$S' \in V^E$}
@@
 \FOR{$S \notin V^E$ when generated by A*}
-\STATE ComputeG(S)
+\STATE ComputeG($S$)
 \STATE $h^E(S) \leftarrow \min_{S'\in V^E} \left( \epsilon^E g_S(S') + h^E(S') \right)$
@@
 Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound is $O(\mathbf{A^2O})$.
-Thus, each state generated costs $O(\mathbf{A^2O + V^E})$ time.
-The preprocessing cost is $O(\mathbf{A^2OV^E + (V^E)^2})$, asymptotically equivalent to preemptively generating every state in $V^E$.
+Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
+The preprocessing cost is $O(\mathbf{V^EA^2O + (V^E)^2A})$, asymptotically equivalent to preemptively generating every state in $V^E$.
 For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
+Provided the number of E-graph vertices is limited to $O(\mathbf{AO})$, the asymptotic cost of node generation is unchanged.
 
@@
 
-\section{Conclusions and Extensions}
+\section{Analysis of HSPr}
+
+Whether or not E-graphs are used, the call to ComputeG($S$) at each node generation is quite substantial.
+For this reason, a variant of HSP, called HSPr, searches the regression space of STRIPS, where each node represents a ``subgoal".
+The search proceeds backward from the goal.
+In this case, the heuristic must estimate the cost to achieve a given state $S$ (considered as a subgoal) from the initial state $I$.
+A single preprocessing call to ComputeG($I$) allows each $h^{HSPr}(S) = g_I(S)$ to be computed in $O(\mathbf{A})$ time.
+
+With E-graphs, in backward as well as forward search, we call ComputeG($S$) for all $S\in V^E$; only now, $V^E$ includes $I$ instead of $G$.
+From $I$, a forward Dijkstra yields $h^E(S)$ for all $S\in V^E$.
+Then for $S\notin V^E$, the E-graph heuristic estimate of the cost from $I$ to $S$ is given by
+\[h^E(S) = \min_{S'\in V^E}\left(h^E(S') + \epsilon^E g_{S'}(S) \right)\]
+
+Since $g_{S'}$ was precomputed, the cost of generating a state is reduced to just $O(\mathbf{V^EA})$.
+Nonetheless, the overhead of using E-graphs is much more substantial in backward than in forward search, contributing a $|V^E|$ factor on the state generation cost.
+
+Since a major benefit of backward HSP is being able to generate states in $O(\mathbf{A})$ time, it appears E-graphs in their present form are less likely to be of much help.
+However, in domains where forward search is more practical, we saw that E-graphs can effectively provide free hints.
+
+\section{Conclusions}
 

### 2014-05-12 planner/planner.cpp

@@ -3895,8 +3895,8 @@ readEGraph(string fileName)
         eDist[i][j].max = min(eDist[i][j].max, eDist[i][k].max + eDist[k][j].max);
       }
   // TODO remove debug code
-  fprintf(statsFile, "EgSize= %u ", experience.size());
-  /*for (size_t i = 0; i < eNode.size(); ++i)
+  /*fprintf(statsFile, "EgSize= %u ", experience.size());
+  for (size_t i = 0; i < eNode.size(); ++i)
   {
       fprintf( stdout, "%d'th distance to goal is %d:\t", i, eDist[i][0].max );
       for( size_t p = 1; p < SIZE_ATOMS; ++p )

### 2014-05-12 AAAI_AuthorKit/paper.tex
Minor edits

@@
 This can be done by dynamic programming, iterating the recursive formula to a fixpoint in Bellman-Ford-like fashion.
-In a sense, it seems we are wasting a lot of work by estimating the cost to reach every atom when we only require $g_S(G)$.
+Pseudocode is listed in Algorithm \ref{alg:ComputeG}.
+
+\begin{algorithm}
+\caption{ComputeG($S$)}
+\label{alg:ComputeG}
+\begin{algorithmic}
+\FORALL{$a \in A$}
+\IF{$a \in S$}
+\STATE $g_S(a) \leftarrow 0$
+\ELSE
+\STATE $g_S(a) \leftarrow \infty$
+\ENDIF
+\ENDFOR
+\REPEAT
+\FORALL{$op \in O$}
+\STATE $pCost \leftarrow g_S(Prec(op))$
+\FORALL{$a \in Add(op)$}
+\STATE $g_S(a) \leftarrow \min \left(g_S(a),~pCost + Cost(op)\right)$
+\ENDFOR
+\ENDFOR
+\UNTIL{no further change in $g_S$-values}
+\end{algorithmic}
+\end{algorithm}
+
+In a sense, a lot of work is wasted by estimating the cost to reach every atom, when we only require $g_S(G)$.
 Later, we'll see how to make better use of this computation.
@@
 Now we combine the ideas from HSP and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
-In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $h^{HSP}_S(S')$.
-We can compute $h^{HSP}_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of the dynamic programming we saw before: each run gives us $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.
+In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$.
+We can compute $g_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of Algorithm \ref{alg:ComputeG}: each run provides us with $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.
 
-Thus, our preprocessing work is roughly equivalent to that of generating $|V^E|$ states, which will be small.
 As before, Dijkstra's algorithm combines an inflation of these estimates with the E-graph edges to derive $h^E(S)$ for all $S\in V^E$.
@@
 
-Upon encountering a new state $S\notin V^E$, we run dynamic programming procedure again to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-graph heuristic by
+Upon encountering a new state $S\notin V^E$, we run Algorithm \ref{alg:ComputeG} again to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-graph heuristic by
 
@@
 The only additional work is the minimization over $S'\in V^E$, which takes O($|V^E||A|$) time.
-A pseudocode implementation is listed in Algorithms \ref{alg:ComputeG} and \ref{alg:Search}.
+A pseudocode implementation is listed in Algorithm \ref{alg:Search}.
 The parameter $\epsilon^E$ controls bias toward the E-graph, while $\epsilon$ provides an additional goal-directed bias.
-
-\begin{algorithm}
-\caption{ComputeG($S$)}
-\label{alg:ComputeG}
-\begin{algorithmic}
-\FORALL{$a \in A$}
-\IF{$a \in S$}
-\STATE $g_S(a) \leftarrow 0$
-\ELSE
-\STATE $g_S(a) \leftarrow \infty$
-\ENDIF
-\ENDFOR
-\REPEAT
-\FORALL{$op \in O$}
-\STATE $pCost \leftarrow g_S(Prec(op))$
-\FORALL{$a \in Add(op)$}
-\STATE $g_S(a) \leftarrow \min \left(g_S(a),~pCost + Cost(op)\right)$
-\ENDFOR
-\ENDFOR
-\UNTIL{no further change in $g$-values}
-\end{algorithmic}
-\end{algorithm}
 
@@
 
-ComputeG implements the dynamic programming computation of $g$-values.
+ComputeG($S$) implements the dynamic programming computation of $g_S$-values.
 Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
-Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound is $O(\mathbf{A^2O})$.
+Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
 Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
 The preprocessing cost is $O(\mathbf{V^EA^2O + (V^E)^2A})$, asymptotically equivalent to preemptively generating every state in $V^E$.
-For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate a state, and does not incur the cost of generating a state unless the A* encounters it.
-Provided the number of E-graph vertices is limited to $O(\mathbf{AO})$, the asymptotic cost of node generation is unchanged.
+
+For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate each state, and does not incur the cost of generating a state unless the A* frontier encounters it.
+When HSP is augmented with small E-graphs, the same asymptotic bound continues to hold, provided that the number of E-graph vertices is limited to $O(\mathbf{AO})$.
+Furthermore, we retain completeness and the ability to configure suboptimality bounds by adjusting the bias parameters:
 

### 2014-05-12 AAAI_AuthorKit/paper.tex
ComputeG

@@
 \FORALL{$op \in O$}
-\STATE $pCost \leftarrow g_S(Prec(op))$
+\STATE $cost\_estimate \leftarrow g_S(Prec(op)) + Cost(op)$
 \FORALL{$a \in Add(op)$}
-\STATE $g_S(a) \leftarrow \min \left(g_S(a),~pCost + Cost(op)\right)$
+\STATE $g_S(a) \leftarrow \min \left(g_S(a),~cost\_estimate\right)$
 \ENDFOR
@@
 \[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \{\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\}\]
-over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$.
-
-$c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.
+with the minimization taking place over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$. $c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.
 

### 2014-05-13 AAAI_AuthorKit/paper.tex
Added paragraph on parallelizability

@@
 
+Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially.
+Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors.
+With minor adjustments, then, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$.
+With $\mathbf{AO}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$.
+Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.
+
 \section{Experimental Setup}
@@
 
-\section{Analysis of HSPr}
+\section{Analysis of HSPr (section might be deleted, but please have a look)}
 

### 2014-05-13 AAAI_AuthorKit/paper.tex
Mike's Edits Part 2, now 4 pages done

@@
 
-We may view planning as a process that generates distance-to-goal labels for each node of a graph.
-Given these distance labels, it's a simple matter to generate a plan by tracing steps from the start, successively taking the optimal successor.
-Since there is no worst-case polynomial-time algorithm that can solve the shortest-paths problem in STRIPS (recall the graph is exponential-sized), we may try to roughly approximate the distance labels.
+In forward weighted A* search, a frontier of nodes expands from the start until it hits a goal, at which point a solution is found.
+Rather than blindly searching the entire exponential-sized space, A* tries to focus toward the goal by expanding nodes which seem likely to lie on a short solution path.
+The minimum length of a solution passing through a given frontier node is the sum of distances from the start to this node, and from this node to a goal.
+The better we estimate these, the sooner we'll reach a solution.
 
-The approximate labels we call \textbf{heuristics}, and we use them in hopes of finding plans more efficiently.
-If the heuristic precisely reflects the true distances, we can immediately retrieve a path.
+Since A* expands in a fairly conservative fashion from the start state onward, the start-to-frontier estimates are computed quite accurately by construction of a valid path.
+Thus, the principal issue is the derivation of frontier-to-goal estimates.
+Given exact distances, it would be a simple matter to trace a valid path from the start, successively taking optimal successors until a goal is reached.
+In practice, we are forced to use estimates, which sometimes mislead us into local optima, wasting time on dead-end nodes.
+
+These distance approximations are called \textbf{heuristics}, and we use them in hopes of finding good plans more efficiently.
 Algorithms such as A* are designed to find solutions quickly whenever the heuristic is of reasonable quality.
 If we hope to take subexponential time, we can only afford to examine a vanishing fraction of the states, and it is only for these that we compute the heuristic.
-If the heuristic is good, we hope not to have to look at (i.e. generate) too many states.
-Hence, there is a tradeoff between spending more time to compute a more accurage heuristic, vs evaluating a weaker heuristic quickly but at many more states.
+If the heuristic is good, we hope not to have to visit (i.e. generate) too many states.
+Hence, there is a tradeoff between spending more time to compute a more accurate heuristic, vs evaluating a weaker heuristic quickly but at many more states.
 
@@
 Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
-A recent approach builds \textbf{Experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
+A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
 The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be quickly generated by reusing subpaths from the E-graph.
@@
 This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by using it to augment the HSP heuristic. 
-The resulting A* search is complete with a configurable suboptimality guarantee.
+The resulting weighted A* search is complete and has a configurable suboptimality guarantee.
 Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over experience-free HSP in several planning domains.
@@
 The problem $P$ defines a directed state graph $(V,c)$ where $V$ is the power set of $A$ (i.e. states $S\in V$ correspond to collections of atoms), and the edge costs are
-\begin{eqnarray*} c(S,S') = \min\{Cost(op) \mid S\subseteq Prec(op)\text{ and}
+\begin{eqnarray*} c(S,S') = \min\{Cost(op) \mid S\supseteq Prec(op)\text{ and}
 \\S' = \left(S \setminus Del(op)\right) \cup Add(op)\} \end{eqnarray*}
@@
 By default, $c(S,S') = \infty$ when there is no operator directly transitioning from $S$ to $S'$.
-Given a STRIPS problem $P$, we seek a low-cost path from the initial state $I\in V$ to any of the goal states $S\in V$ such that $S \supset G$.
+Given a STRIPS problem $P$, we seek a low-cost path from the initial state $I\in V$ to any of the goal states $S\in V$ such that $S \supseteq G$.
+In this paper, we are particularly concerned with sequences of problems in which $A$ and $O$ are fixed, but various pairs $\langle I,G\rangle$ are queried.
 
@@
 \end{defn}
-\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost.  \end{thm}
+\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost.
+[CITE ARA*] \end{thm}
 
@@
 
-In the limit as $\epsilon^E \rightarrow 1$, following E-graph edges offers no advantage as $h$ is already an underestimate. Hence, using the triangle inequality to coalesce the sum,
+In the limit as $\epsilon^E \rightarrow 1$, E-graph edges offer no advantage as $h(S_{i-1},S_i) \le c^E(S_{i-1},S_i)$. Hence, using the triangle inequality to coalesce the sum,
 \[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N h(S_{i-1},S_i) = \min_{S_N} h(S_0,S_N)\]
@@
 We cannot afford to compute $h^E$ according to its literal definition, as there are far too many paths to consider.
-Fortunately, there exists a practical means of computing it.
-By the triangle inequality, any consecutive pair of $h(S_{i-1},S_i)$ terms can be merged into one.
-Thus we lose no generality in restricting $S_i$ to lie on the E-graph for $0 < i < N$.
+Fortunately, there exists a practical means of computing it. By the triangle inequality, any consecutive pair of $h(S_{i-1},S_i)$ terms can be merged into one.
+Thus, we lose no generality in restricting $S_i$ to lie on the E-graph for $0 < i < N$.
+The heuristic computation can focus on the E-graph, using $h(S_{i-1},S_i)$ to estimate the cost of leaving the E-graph at $S_{i-1}$ before re-entering it at $S_i$.
 
 Let $V^E$ be the union of the goal states and the E-graph's vertices.
-In addition to following E-graph edges, we imagine it's possible to ``jump" from $S$ to $S'$ with cost $\epsilon^E h(S,S')$. That is, let $c'(S,S') = \min\left(c(S,S'),~\epsilon^E g_S(S')\right)$
+In addition to following E-graph edges, we imagine it's possible to ``jump" from $S$ to $S'$ at cost $\epsilon^E h(S,S')$.
+That is, let $c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)$
 
 In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
-If the heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-graphs and goal sets.
+Ignoring the computation of $h$ (presently considered as a blackbox), this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-graphs and goal sets.
 
@@
 A pseudocode implementation is listed in Algorithm \ref{alg:Search}.
-The parameter $\epsilon^E$ controls bias toward the E-graph, while $\epsilon$ provides an additional goal-directed bias.
+The parameter $\epsilon^E$ controls bias toward the E-graph, while the weight $\epsilon$ provides a uniform goal-directed bias.
 
@@
 \begin{algorithmic}
-\STATE Let $c(S,S')$ for $S,S'\in V^E$ represent E-graph edge costs.
 \FORALL{$S \in V^E$}
@@
 \FORALL{$S' \in V^E$}
-\STATE $c'(S,S') \leftarrow \min\left(c(S,S'),~\epsilon^E g_S(S')\right)$
+\STATE $c'(S,S') \leftarrow \min\left(c^E(S,S'),~\epsilon^E g_S(S')\right)$
 \ENDFOR
@@
 Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
-Multiplying everything together and ignoring cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
+Multiplying nested loop iterations together and ignoring cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
 Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
+
 The preprocessing cost is $O(\mathbf{V^EA^2O + (V^E)^2A})$, asymptotically equivalent to preemptively generating every state in $V^E$.
+In fact, most of the preprocessing requires no knowledge of $G$, so it can be done in advance of the new planning query.
+Once the query $\langle I,G\rangle$ is given, the remaining work consists of completing the $c'(S,G)$ computations from $g_S(a),a\in G$, and then running Dijkstra's algorithm from $G$.
+This costs only $O(\mathbf{V^E(A + V^E)})$ time.
 
@@
 Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors.
-With minor adjustments, then, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$.
-With $\mathbf{AO}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$.
+Therefore, with minor adjustments, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$.
+With $\mathbf{A\max(O,V^E)}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$.
 Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.
+If still more processors are available, some may dedicate to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g.
+near the A* frontier.
 
@@
 
-\section{Analysis of HSPr (section might be deleted, but please have a look)}
+\section{Analysis of HSPr (section to be deleted)}
 
@@
 
+Another use of E-graphs: if something goes wrong along the path, we can replan using the E-graph to get a faster and less disruptive result.
+
 \bibliographystyle{aaai}

### 2014-05-13 AAAI_AuthorKit/paper.tex
bib update

@@
 In this paper, we demonstrate how to augment symbolic planners with
-experience graphs, using the HSP STRIPS planner as a representative
+experience graphs, using the HSP2 planner as a representative
 example.
@@
 We demonstrate
-experimentally that our planner speeds up HSP by a factor of 2 or more on
+experimentally that our planner speeds up HSP2 by a factor of 2 or more on
 many domains while achieving about the same plan quality.
@@
 The graph is exponentially larger than its encoding so, in both cases, states are generated only as needed.
-The compressed representation sometimes encodes exploitable structure.
+The symbolic representation sometimes encodes exploitable structure.
 In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret structural information about the problem.
@@
 
-Since A* expands in a fairly conservative fashion from the start state onward, the start-to-frontier estimates are computed quite accurately by construction of a valid path.
+Since A* expands in a fairly conservative fashion from the start state onward, the start-to-frontier estimates are very well-approximated by construction of a valid path.
 Thus, the principal issue is the derivation of frontier-to-goal estimates.
-Given exact distances, it would be a simple matter to trace a valid path from the start, successively taking optimal successors until a goal is reached.
+Given exact distances, it would be a simple matter to trace a valid path from the start, taking optimal successors at each step, until a goal is reached.
 In practice, we are forced to use estimates, which sometimes mislead us into local optima, wasting time on dead-end nodes.
@@
 
-In practice, even using state-of-the-art methods to generate heuristics on isolated planning instances, STRIPS problems can be very difficult to solve without domain knowledge.
+In practice, even using state-of-the-art methods to generate heuristics on isolated planning instances, STRIPS problems can be very difficult to solve without expert domain knowledge.
 Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
 Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
+
 A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
-The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be quickly generated by reusing subpaths from the E-graph.
-However, E-graphs have never before been applied to high-level representations such as STRIPS. This is our present contribution.
+The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
+A variant of weighted A* is employed which biases its focus toward the E-graph.
+While this work demonstrates promising results in robot motion planning, E-graphs have never before been applied to symbolic domain representations such as the STRIPS language.
 
-In section [???], we present the HSP heuristic for STRIPS.
-Then, we discuss E-graphs in more technical detail.
-This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by using it to augment the HSP heuristic. 
-The resulting weighted A* search is complete and has a configurable suboptimality guarantee.
-Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over experience-free HSP in several planning domains.
+Our present contribution is to investigate the use of E-graphs in STRIPS domains.
+In particular, we take the HSP planner \cite{bonet2001planning} as a representative of the class of modern weighted A* based symbolic planners, and augment its heuristic with a bias toward its E-graph.
+After presenting the related works, we begin by describing the STRIPS language and the original HSP heuristic.
+In the following section, we formally introduce E-graphs in technical detail.
+Then we combine the two approaches, resulting in the new Experience-Biased HSP planner.
+We present the algorithm and discuss its theoretical properties.
+This is followed by experiments showing promise for the application of E-graphs to symbolic problem solving.
+Finally, we conclude with some thoughts on extensions worth investigating.
 
 \section{Related Work}
+
+In recent times, a lot of symbolic planners have emerged based on forward weighted A* search.
+This paper focuses on augmenting HSP2 as a representative example, because it is fairly simple and forms the foundation of many modern planners.
+The use of E-graphs is orthogonal to most recent improvements, so our methods can in principle be adapted to any heuristic A* planner.
+
+After HSP2, fast downward and LAMA...
 

### 2014-05-13 AAAI_AuthorKit/paper.tex
Shallow Related Works

@@
 Our present contribution is to investigate the use of E-graphs in STRIPS domains.
-In particular, we take the HSP planner \cite{bonet2001planning} as a representative of the class of modern weighted A* based symbolic planners, and augment its heuristic with a bias toward its E-graph.
+In particular, we take the HSP2 planner \cite{bonet2001planning} as a representative of the class of modern weighted A* based symbolic planners, and augment its heuristic with a bias toward its E-graph.
 After presenting the related works, we begin by describing the STRIPS language and the original HSP heuristic.
@@
 
-In recent times, a lot of symbolic planners have emerged based on forward weighted A* search.
-This paper focuses on augmenting HSP2 as a representative example, because it is fairly simple and forms the foundation of many modern planners.
-The use of E-graphs is orthogonal to most recent improvements, so our methods can in principle be adapted to any heuristic A* planner.
+Alot of symbolic planners that have emerged in recent years are based on forward weighted A* search.
+This paper focuses on HSP2 as a representative example, because it is fairly simple and embodies the core ideas common to many state-of-the-art planners.
+The use of E-graphs is orthogonal to many of the latest improvements, so our methods can in principle be adapted to any A* planner.
 
-After HSP2, fast downward and LAMA...
+Fast Downward \cite{helmert2006fast} is a planner that decomposes planning tasks using a contruct called the causal graph heuristic.
+The LAMA planner \cite{richter2010lama}, which won the International Planning Competition 2008, replaces the causal graph with landmark heuristics.
+
+While many of these planners perform preprocessing in an attempt to automatically extract knowledge about the domain, none are capable of using their own fully generated plans to inform later searches.
+A few works were made in similar directions, for example \cite{fikes1972learning} are able to generalize their plans, \cite{veloso1992learning} is able to relate by analogy to known solutions, and \cite{borrajo2012probabilistically} probabilistically chooses whether to step along past plans or explore new paths.
 
@@
 
-Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP planner \cite{bonet2001planning}, which we now describe.
+Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP2 planner \cite{bonet2001planning}, which we now describe.
 It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
@@
 Intuitively, we see that the relaxed search space remains exponential.
-To reduce it, HSP decouples the atoms, instead estimating the cost of achieving each individual atom.
+To reduce it, HSP2 decouples the atoms, instead estimating the cost of achieving each individual atom.
 
-Let's say we want a heuristic estimate of the distance from $S$ to a goal that contains $G$. HSP estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+Let's say we want a heuristic estimate of the distance from $S$ to a goal that contains $G$. HSP2 estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
 \[\begin{cases} 0  &\mbox{if } a \in S
@@
 
-The HSP heuristic is then defined by
+The HSP heuristic (also used in HSP2) is then defined by
 \[h^{HSP}(S) = g_S(G),\]
@@
 
-Now we combine the ideas from HSP and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
+Now we combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
 In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$.
@@
 Compare this to the formula for $h^{HSP}$, which uses only $g_S(G)$.
-HSP would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-graph essentially for free.
+HSP2 would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-graph essentially for free.
 The only additional work is the minimization over $S'\in V^E$, which takes O($|V^E||A|$) time.
@@
 Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
-Multiplying nested loop iterations together and ignoring cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
+Multiplying nested loop iterations together and dropping cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
 Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
@@
 
-For comparison, standard HSP without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate each state, and does not incur the cost of generating a state unless the A* frontier encounters it.
-When HSP is augmented with small E-graphs, the same asymptotic bound continues to hold, provided that the number of E-graph vertices is limited to $O(\mathbf{AO})$.
+For comparison, standard HSP2 without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate each state, and does not incur the cost of generating a state unless the A* frontier encounters it.
+When HSP2 is augmented with small E-graphs, the same asymptotic bound continues to hold, provided that the number of E-graph vertices is limited to $O(\mathbf{AO})$.
 Furthermore, we retain completeness and the ability to configure suboptimality bounds by adjusting the bias parameters:
@@
 
-We augmented the HSP planner code \cite{bonet2001planning} which won [AI COMPETITION IN 2000] with E-graphs.
+We augmented the HSP2 planner code \cite{bonet2001planning} which won [AI COMPETITION IN 2000] with E-graphs.
 Our aim is to observe the effect of E-graphs on planning time given that we've already solved a closely related problem.
 To measure this, we run three searches for each problem instance.
-First, we run the original problem using standard HSP.
+First, we run the original problem using standard HSP2.
 Then, we generate a modified problem by moving the start and goal nodes randomly for X steps each.

### 2014-05-14 TestSuite.sh
New test data, the ods file has one sheet per parameter setting

@@ -1,5 +1,5 @@
-#!/bin/sh
-#rm -r Test/*
+!/bin/sh
+rm -r Test/*
 
 #for prob in "6-0" "7-0" "8-0" "9-0" "10-0" "11-0" "12-0" "13-0" "14-0" "14-1" "15-0" "15-1" "16-1" "16-2" "17-0"
 #do
@@ -14,20 +14,18 @@
 #  echo "--------------------------------------------------------------------------------"
 #done
 
-#for dir in examples/*/
-#for dir in "examples/mprime/" "examples/openstacks/" "examples/parcprinter-strips/" "examples/pegsolitaire/"
-#for dir in "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
-for dir in "examples/blocks/" "examples/elevators/" "examples/rovers/" "examples/satellite/"
+for dir in examples/*/
+#for dir in "examples/blocks/" "examples/driverlog/" "examples/elevators/" "examples/freecell/" "examples/grid/" "examples/logistics00/" "examples/logistics98/" "examples/mprime/" "examples/openstacks/" "examples/pegsolitaire/" "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
 do
 	mkdir -p Test/${dir}
-	for filename in ${dir}p*.pddl
+	for filename in ${dir}p*
 	do
-	if [ "${filename}" != "${dir}p*.pddl" ]
+	if [ "${filename}" != "${dir}p*" ]
 	then
 		#without file extension: Test/$(basename "$filename" .pddl).eg
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/${filename}.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/trash.eg -S [forward,h1eplus,2000] ${filename} ${dir}domain.pddl
[…]

### 2014-05-14 planner/planner.cpp

@@ -3540,8 +3540,8 @@ initialize( void )
   /* TODO make random walks configurable: randomly move start and goal */
   if (EGraphOut == "Test/trash.eg")
   {
-    randomWalk(staticInitialState, 0);
-    randomWalk(staticGoalState, 0);
+    randomWalk(staticInitialState, 50);
+    randomWalk(staticGoalState, 50);
     p = _low_initialAtoms;
     for (size_t at = 1; at < SIZE_ATOMS; ++at)
       if ( asserted( staticInitialState, at ) )
@@ -3921,7 +3921,7 @@ printEGraph(string fileName, double proportion = 1)
   }
   
   // TODO remove debug code
-  fprintf(statsFile, "ExpSize= %u ", experience.size());
+  //fprintf(statsFile, "ExpSize= %u ", experience.size());
   
   int n = experience.size();
   int k = std::round(n * proportion);
@@ -4108,7 +4108,7 @@ printStatistics( void )
   if (statsFile != nullptr)
   {
    if (EGraphIn == "Test/none.eg")
-      fprintf( statsFile, "Gen= %d ", generatedNodes );
+      fprintf( statsFile, "Gen= %d", generatedNodes );
     else
       fprintf( statsFile, "Gen= %d\t%s\n", generatedNodes, problemFile );
   }
@@ -4573,7 +4573,7 @@ scheduler( schedule_t *schedule )
       fprintf( stderr, "SOLUTION: no solution found\n" );
       // TODO debug remove extra prints
       if (statsFile != nullptr )
-          fprintf( statsFile, "!" );
+          fprintf( statsFile, "!SolSize= 0 " );
     }
     else
     {

### 2014-05-14 AAAI_AuthorKit/paper.tex
ALL EXPERIMENTS

@@
 /Title (Experience-Biased Symbolic Planning)
-/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)
+/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
 /Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
@@
 \title{Experience-Biased Symbolic Planning}
-\author{Aram Ebtekar \and Mike Phillips \and Maxim Likhachev\\
-Carnegie Mellon University\\
-5000 Forbes Ave,\\
-Pittsburgh, PA 15213\\
-\And Sven Koenig\\
-University of Southern California\\
-Los Angeles, CA 90089
+\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA} \and Maxim Likhachev% <-this % stops a space
+\thanks{Carnegie Mellon University, Pittsburgh, PA.
+We thank Willow Garage for their support of this work. This research was also sponsored by ARL, under the Robotics CTA program grant W911NF-10-2-0016.}% <-this % stops a space
+%
 }
@@
 \section{Related Work}
+
+Classically, case-based reasoning methods 
+such as PRIAR~\cite{Kamb:92}, SPA~\cite{Hank:95}, MRL~\cite{Koeh:94}, and NoLimit~\cite{mljournal}
+have been used recall 
+previous plans that appear similar to the current problem and 
+then adapt them to meet the new specifications.
+Compared to these methods, our work reuses prior experience in
+the context of modern weighted A* methods. We also provide
+a bound on the suboptimality of the solution.
+
+Recently there has been work on incorporating prior knowledge 
+into modern planners (based on weighted A* and powerful heuristics).
+For instance, GPG~\cite{Gere:00} uses planning graphs to adapt a prior path to the 
+new scenario by searching locally within windows around plan 
+inconsistencies. To guarantee completeness, the windows can grow 
+if solutions are not found until they contrain the whole plan.
+In this work~\cite{DBLP:conf/iccbr/RosaOB07} case-based reasoning is used to choose the 
+order of state evaluations of EHC (enforced hill-climbing) which 
+is a component in modern planners such as FF.
+
+OAKplan~\cite{Serina:2010:KFC:1860143.1860472} is a recent 
+case-based reasoning method which converts 
+planning instances to into a compact graph representation and 
+then uses recent kernel methods for matching labeled graphs to select
+a similar case to the problem at hand. The selected case is then 
+adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method 
+encourages \textit{plan stability}, which tries to make 
+sure that the new plan is as similar to the previous plan as possible. 
+The method also uses a modern heuristic search approach.
+
+ERRT-PLAN~\cite{workshop-icaps12-errtplan} presents a very different 
+approach to reuse in planning. 
+Similar to E-Graphs, ERRT has its roots in motion planning~\cite{Bruce:2002}.
+ERRT-PLAN applies this sampling-based motion planner that leverages 
+reuse to symbolic planning. The planner randomly chooses to extend 
+the search tree toward the goal, toward goals from previous 
+plans, or to reuse an action from a previous plan. 
+The extension operations are based on modern heuristic search
+planners.
+The stochastic nature of the direction the search progresses toward
+allows it to overcome local minima caused by misleading heuristics.
+
+The primary difference between our approach and previous ones 
+is that we plan with prior experience in a way that have provable
+bounds on suboptimality of the solution. The use of E-Graphs also
+allows us to formulate this in a way that the user has control over
+this suboptimality bound with an intuitive parameter that trades
+reuse (speed) for solution quality.
+
+\section{Old version of related works (to delete)}
 
@@
 
-\includegraphics[scale=0.4]{Pentagon.png}
+\begin{center}
+\includegraphics[scale=0.5]{Pentagon.png}
+\end{center}
 
@@
 
-\section{Experimental Setup}
+\section{Experiment 1}
 
@@
 
-\section{Experimental Results}
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_20_0.png}
+	\end{center}
+	\caption{20\% E-graph}
+	 \label{fig:s_20_0}
+\end{figure}
 
-\includegraphics[scale=0.4]{AIPlot.png}
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_50_0.png}
+	\end{center}
+	\caption{50\% E-graph}
+	 \label{fig:s_50_0}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_80_0.png}
+	\end{center}
+	\caption{80\% E-graph}
+	 \label{fig:s_80_0}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_20_0.png}
+	\end{center}
+	\caption{20\% E-graph}
+	 \label{fig:c_20_0}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_50_0.png}
+	\end{center}
+	\caption{50\% E-graph}
+	 \label{fig:c_50_0}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_80_0.png}
+	\end{center}
+	\caption{80\% E-graph}
+	 \label{fig:c_80_0}
+\end{figure}
+
+\begin{table}
+	\begin{center}
+	    \begin{tabular}{| l | l | l | l | l |}
+	    \hline
+	    Domain & Inst & 20\% & 50\% & 80\%
+	    \\ \hline
+	    blocksworld & 35 & 1.08-1.82 & 1.37-3.73 & 1.90-5.84
+	    \\ \hline
+	    driverlog & 14 & 1.00-1.49 & 1.11-1.58 & 1.15-1.60
+	    \\ \hline
+	    elevators & 30 & 1.00-1.62 & 1.00-2.84 & 1.04-3.19
+	    \\ \hline
+	    freecell & 34 & 1.00-1.06 & 1.00-1.12 & 1.00-1.08
+	    \\ \hline
+	    grid & 2 & 1.07-1.18 & 2.16-3.57 & 2.22-3.75
+	    \\ \hline
+	    logistics00 & 28 & 0.91-1.04 & 0.98-1.13 & 1.03-1.19
+	    \\ \hline
+	    logistics98 & 5 & 0.95-1.01 & 1.09-1.62 & 1.24-3.00
+	    \\ \hline
+	    mprime & 19 & 1.00-1.00 & 1.00-1.07 & 1.00-2.46
+	    \\ \hline
+	    pegsolitaire & 29 & 1.00-3.57 & 1.13-4.49 & 1.68-6.63
+	    \\ \hline
+	    pipesworld-notankage & 15 & 1.00-3.27 & 1.00-7.07 & 1.00-9.95
+	    \\ \hline
+	    pipesworld-tankage & 8 & 1.00-1.00 & 1.00-1.02 & 1.00-1.45
+	    \\ \hline
+	    rovers & 13 & 0.97-1.23 & 1.23-7.09 & 1.23-7.17
+	    \\ \hline
+	    satellite & 16 & 0.99-1.00 & 1.00-1.26 & 1.00-1.26
+	    \\ \hline
+	    scananalyzer & 16 & 1.00-1.15 & 0.93-1.20 & 1.00-1.36
+	    \\ \hline
+	    sokoban & 11 & 1.12-2.10 & 1.32-3.02 & 1.56-7.80
+	    \\ \hline
+	    tpp & 10 & 1.00-1.00 & 1.00-1.23 & 1.00-2.31
+	    \\ \hline
+	    transport & 23 & 1.00-1.14 & 1.09-1.86 & 1.19-1.89
+	    \\ \hline
+	    zenotravel & 13 & 1.02-1.15 & 1.08-1.44 & 1.14-1.58
+	    \\ \hline
+	    TOTAL & 321 & 1.00-1.29 & 1.00-1.91 & 1.02-2.68
+	    \\ \hline
+	    \end{tabular}
+	\end{center}
+	\caption{Speedups for various E-graph \%s over various domains.}
+	 \label{tab:percent}
+\end{table}
+
+\section{Experiment 2}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_5.png}
+	\end{center}
+	\caption{5 random steps}
+	 \label{fig:s_100_5}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_20.png}
+	\end{center}
+	\caption{20 random steps}
+	 \label{fig:s_100_20}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_50.png}
+	\end{center}
+	\caption{50 random steps}
+	 \label{fig:s_100_50}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_100_5.png}
+	\end{center}
+	\caption{5 random steps}
+	 \label{fig:c_100_5}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_100_20.png}
+	\end{center}
+	\caption{20 random steps}
+	 \label{fig:c_100_20}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Cost_100_50.png}
+	\end{center}
+	\caption{50 random steps}
+	 \label{fig:c_100_50}
+\end{figure}
 
@@
 
+\begin{table}
 	\begin{center}
-    \begin{tabular}{| l | l | l | l |}
+	    \begin{tabular}{| l | l | l | l | l |}
 	    \hline
-    Domain & 0 steps & 10 steps & 20 steps
+	    Domain & Inst & 5 steps & 20 steps & 50 steps
 	    \\ \hline
-    BlocksWord & 0 & 0 & 0
+	    blocksworld & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
 	    \\ \hline
-    Grid & 0 & 0 & 0
+	    driverlog & 14 & 0.86-2.42 & 0.85-1.30 & 0.82-1.20
 	    \\ \hline
-    Satellite & 0 & 0 & 0
+	    elevators & 30 & 1.09-4.04 & 0.99-2.76 & 0.90-2.06
+	    \\ \hline
+	    grid & 2 & 2.21-3.71 & 1.11-1.34 & 1.10-1.30
+	    \\ \hline
+	    logistics00 & 28 & 1.00-1.15 & 0.90-1.11 & 0.84-1.18
+	    \\ \hline
+	    logistics98 & 5 & 1.01-2.95 & 0.82-2.06 & 0.80-2.41
+	    \\ \hline
+	    pipesworld-notankage & 15 & 1.09-5.30 & 1.00-5.46 & 1.00-2.88
+	    \\ \hline
+	    pipesworld-tankage & 8 & 1.00-1.20 & 0.99-1.00 & 1.00-1.13
+	    \\ \hline
+	    rovers & 13 & 1.00-1.50 & 1.00-1.00 & 1.00-1.00
+	    \\ \hline
+	    satellite & 16 & 0.91-1.25 & 0.87-1.15 & 0.90-1.43
+	    \\ \hline
+	    scananalyzer & 16 & 0.74-1.52 & 1.00-1.00 & 1.00-1.00
+	    \\ \hline
+	    transport & 23 & 1.26-1.91 & 0.93-1.87 & 0.98-1.46
+	    \\ \hline
+	    zenotravel & 13 & 0.80-1.27 & 0.84-1.02 & 1.00-1.00
+	    \\ \hline
+	    TOTAL & 218 & 0.99-2.72 & 1.00-2.07 & 1.00-1.88
 	    \\ \hline
@@
 	\end{center}
+	\caption{Speedups for various random walk distances over different domains.}
+	 \label{tab:walk}
+\end{table}
 

### 2014-05-14 TestSuite.sh

@@ -14,7 +14,8 @@ rm -r Test/*
 #  echo "--------------------------------------------------------------------------------"
 #done
 
-for dir in examples/*/
+#for dir in examples/*/
+for dir in "examples/satellite/" "examples/blocks/"
 #for dir in "examples/blocks/" "examples/driverlog/" "examples/elevators/" "examples/freecell/" "examples/grid/" "examples/logistics00/" "examples/logistics98/" "examples/mprime/" "examples/openstacks/" "examples/pegsolitaire/" "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
 do
 	mkdir -p Test/${dir}
@@ -24,8 +25,8 @@ do
 	then
 		#without file extension: Test/$(basename "$filename" .pddl).eg
 		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/${filename}.eg -S [forward,h1eplus,5000] ${filename} ${dir}domain.pddl
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/trash.eg -S [forward,h1eplus,5000] ${filename} ${dir}domain.pddl
-		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/${filename}.eg Test/trash.eg -S [forward,h1eplus,5000] ${filename} ${dir}domain.pddl
+		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/none.eg Test/trash.eg -S [forward,h1eplus,975000] ${filename} ${dir}domain.pddl
+		./bin/hsp2 -v 0 -w 1 -e 5 -f Test/${filename}.eg Test/trash.eg -S [forward,h1eplus,975000] ${filename} ${dir}domain.pddl
 	fi
 	done
 done

### 2014-05-14 AAAI_AuthorKit/paper.tex
predinner version

@@
 \title{Experience-Biased Symbolic Planning}
-\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA} \and Maxim Likhachev% <-this % stops a space
-\thanks{Carnegie Mellon University, Pittsburgh, PA.
-We thank Willow Garage for their support of this work. This research was also sponsored by ARL, under the Robotics CTA program grant W911NF-10-2-0016.}% <-this % stops a space
+\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA 90089} \and Maxim Likhachev% <-this % stops a space
+\thanks{Carnegie Mellon University, Pittsburgh, PA 15217}% <-this % stops a space
 %
@@
 
-Alot of symbolic planners that have emerged in recent years are based on forward weighted A* search.
+A lot of symbolic planners that have emerged in recent years are based on forward weighted A* search.
 This paper focuses on HSP2 as a representative example, because it is fairly simple and embodies the core ideas common to many state-of-the-art planners.
@@
 \end{defn}
-\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost.
-[CITE ARA*] \end{thm}
+\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}.
+\end{thm}
 
@@
 
+\begin{figure}
 	\begin{center}
@@
 	\end{center}
+	\caption{An example E-graph and corresponding heuristic computations.}
+	\label{fig:example}
+\end{figure}
 
-The above figure illustrates the idea.
+Figure \ref{fig:example} illustrates the idea.
 Suppose the dark edges have cost 3 and make up the E-graph.

### 2014-05-15 AAAI_AuthorKit/paper.tex
All sections draft ready, 1 day remains

@@
 The use of E-graphs is orthogonal to many of the latest improvements, so our methods can in principle be adapted to any A* planner.
+
+HSP2 is based on the HSP planner [CITE] which performed well in the AIPS-98 planning competition.
+HSP combined a novel heuristic with a hill-climbing algorithm.
+HSP2 used the same heuristic, but with a weighted A* search, and produced even better results.
+FF and GRT develop these heuristics further.
 
@@
 Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
-Multiplying nested loop iterations together and dropping cardinality signs for brevity, the runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
+Multiplying nested loop iterations together and dropping cardinality signs for brevity, a conservative runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
 Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
@@
 
-We augmented the HSP2 planner code \cite{bonet2001planning} which won [AI COMPETITION IN 2000] with E-graphs.
-Our aim is to observe the effect of E-graphs on planning time given that we've already solved a closely related problem.
-To measure this, we run three searches for each problem instance.
-First, we run the original problem using standard HSP2.
-Then, we generate a modified problem by moving the start and goal nodes randomly for X steps each.
-The second search solves the modified problem in the standard way.
-Finally, the third search solves the modified problem using as E-graph a random Y\% of the path obtained from the first search.
-The reason for saving only a portion of the previous experience is to simulate the effects of disconnected E-graphs, as might arise after multiple searches.
-Our main comparisons will be between the number of nodes generated in the second and third searches.
-In practice, the times followed similar ratios to the number of nodes generated; as one would expect from the analyis in [PREVIOUS SECTION] since the E-graph resulting from Y\% of a single path is very small.
+We augmented the original HSP2 planner code \cite{bonet2001planning} with E-graphs.
+Since HSP-plus performs better in practice than HSP-max, we take the former heuristic as our baseline.
+Our aim is to observe the planning time speedup achieved by applying E-graphs on a variety of STRIPS domains.
+To measure this, we prepared two sets of experiments, of which this section describes the first.
+
+In this experiment set, we solve several hundred problem instances across 18 domains taken from the HSP2 test suite.
+For each problem, we first plan without experiences, using the HSP-plus heuristic in an A* search with weight $\epsilon=5$.
+This search acts as our scientific \textbf{control}.
+If the control fails to find a solution within 5 seconds, we discard the problem instance as being too difficult.
+Otherwise, we record the plan cost and the number of states that were generated during the search.
+Thus, we end up considering 321 problem instances.
+
+For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound.
+The E-graphs consist of 20\%, 50\% and 80\% of the edges from the control's solution path, respectively, selected at random.
+For each of these, we again record the solution cost and number of nodes generated, and compare these figures to the control.
+Define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
+Likewise, define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.
+We use nodes generated instead of time to produce deterministic results which are independent of most engineering details.
+The times taken generally seemed to follow similar trends; as suggested by the analysis, the time spent per node changes little when small E-graphs are used.
+
+The results are summarized in Figure \ref{tab:percent}.
+We see that while performance in virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
+For example, results are strongly positive in the Blocks World.
+Furthermore, figures [CITE numbers] show that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.
+
+Note that saving 100\% of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
+In practice, since we fixed the bias parameter $\epsilon^E$ to 5 rather than raising it to an extremely large value, the search expands a fair number of states even if we remember most or all of the path.
+This is necessary to ensure the suboptimality bound, as the planner does not know whether the E-graph can be ``trusted" to yield an efficient path.
 
@@
 	    \\ \hline
-	    blocksworld & 35 & 1.08-1.82 & 1.37-3.73 & 1.90-5.84
+	    blocks & 35 & 1.08-1.82 & 1.37-3.73 & 1.90-5.84
 	    \\ \hline
@@
 	\end{center}
-	\caption{Speedups for various E-graph \%s over various domains.}
+	\caption{Speedups for various E-graph \%s over various domains. Statistics are presented in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:percent}
@@
 \section{Experiment 2}
+
+The previous experimental setup tested our ability to generalize from incomplete partial plans stored in memory; however, the new planning instances solved were identical to that used by the control to generate the E-graph.
+Now, we try moving the start and goal nodes by having each of them take 5, 20 or 50 random walk steps in the state space. 
+In this manner, we test how well E-graphs can generalize to nearby but non-identical queries.
+
+We narrow our focus to 13 domains, and take from each of them the same set of instances as in the previous experiment, yielding 218 problem instances in all.
+This time, we save 100\% of the solution path found by the control.
+Then for each problem, we run 3 queries using this E-graph, moving each the start and goal by 5, 20 and 50 random steps, respectively.
+
+Results are summarized in Figure \ref{fig:c_100_50}.
+Again we observe encouraging speedups, though they decrease as we walk farther distances from the original query.
 
@@
 
-The plot shows speedup (i.e.
-ratio of nodes generated in the second and third searches) against a measure of problem size (i.e.
-nodes generated in the second search).
-Planning times followed similar trends as node generation counts, as one would expect from the analyis since the E-graph resulting from a half-path is very small.
-We see considerable speedups in many domains, while the plan costs stayed roughly the same (in fact, they became slightly shorter on average).
-Many domains saw no discernable effect, but none were significantly hurt by E-graphs.
-
 \begin{table}
@@
 	    \\ \hline
-	    blocksworld & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
+	    blocks & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
 	    \\ \hline
@@
 	\end{center}
-	\caption{Speedups for various random walk distances over different domains.}
+	\caption{Statistics are presented in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:walk}
@@
 
-\section{Conclusions}
+\section{Conclusions (needs citations)}
 
-We saw that by reusing pieces from past plans, planning time can often be reduced.
+We saw that by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences.
 Many interesting directions remain for future investigation.
-The E-graph cannot be allowed to grow without bound over countless planning episodes, so a better scheme is needed for expansion and pruning as the agent learns.
+It remains unclear how the bias parameters should be set.
+In addition, more advanced schemes will be needed to expand and prune E-graphs if they get large due to collecting a lot of solutions.
+Saving each computed plan seems like a good idea intuitively, but other possibilities may be worth investigating.
 
-Distinct states in STRIPS can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches.
+For STRIPS in particular, distinct states can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches.
+However, it's crucial not to overgeneralize as that might simply lead to most of the graph being reweighted uniformly.
+The problem of generalization seem related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.
 
-What if graph changes? Anytime incremental...
+E-Graphs should be thought of not so much as a specific algorithm, but as a tool which is orthogonal to a lot of the major planning techniques out there.
+Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to get anytime, incremental search using experiences in symbolic domains.
 
-Another use of E-graphs: if something goes wrong along the path, we can replan using the E-graph to get a faster and less disruptive result.
+Finally, E-Graphs could potentially find other uses, in particular for replanning.
+If an unexpected event invalidates a robot's plan mid-execution, the replanner can remember the original solution as an E-graph to encourage reparations along the old path.
+In addition to speeding replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
+Minimizing disruption is important when resources must be allocated according to the plan, or cognitively-burdened humans are involved with its execution.
 

### 2014-05-15 AAAI_AuthorKit/paper.tex
5:30 version

@@
 plan-reuse techniques, such as planning by analogy.
-We demonstrate
-experimentally that our planner speeds up HSP2 by a factor of 2 or more on
-many domains while achieving about the same plan quality.
+We demonstrate experimentally that on many symbolic domains, our approach reduces the number of nodes that the HSP2 planner needs to consider by a factor of 2 or more while achieving about the same plan quality.
 \end{quote}
@@
 
-\section{Related Work}
+\section{Related Works}
 
@@
 
-\section{Old version of related works (to delete)}
-
-A lot of symbolic planners that have emerged in recent years are based on forward weighted A* search.
-This paper focuses on HSP2 as a representative example, because it is fairly simple and embodies the core ideas common to many state-of-the-art planners.
-The use of E-graphs is orthogonal to many of the latest improvements, so our methods can in principle be adapted to any A* planner.
-
-HSP2 is based on the HSP planner [CITE] which performed well in the AIPS-98 planning competition.
-HSP combined a novel heuristic with a hill-climbing algorithm.
-HSP2 used the same heuristic, but with a weighted A* search, and produced even better results.
-FF and GRT develop these heuristics further.
-
-Fast Downward \cite{helmert2006fast} is a planner that decomposes planning tasks using a contruct called the causal graph heuristic.
-The LAMA planner \cite{richter2010lama}, which won the International Planning Competition 2008, replaces the causal graph with landmark heuristics.
-
-While many of these planners perform preprocessing in an attempt to automatically extract knowledge about the domain, none are capable of using their own fully generated plans to inform later searches.
-A few works were made in similar directions, for example \cite{fikes1972learning} are able to generalize their plans, \cite{veloso1992learning} is able to relate by analogy to known solutions, and \cite{borrajo2012probabilistically} probabilistically chooses whether to step along past plans or explore new paths.
+The HSP2 \cite{bonet2001planning} planner uses the heuristic pioneered by HSP, but replaces greedy hill-climbing with weighted A* search.
+We test our approach on HSP2 because the latter is straightforward to describe and it is representative of the core techniques that are common to many state-of-the-art domain-independent symbolic planners.
+Some newer additions to the field include the causal graph heuristic of the Fast Downward planner \cite{helmert2006fast} and the landmark heuristic of the LAMA planner \cite{richter2010lama}.
+Our approach is orthogonal to these developments and can, in principle, be adapted to work with any search heuristic.
 
@@
 
-\section{Experiment 1}
+\section{Experimental Analysis}
 
@@
 Since HSP-plus performs better in practice than HSP-max, we take the former heuristic as our baseline.
-Our aim is to observe the planning time speedup achieved by applying E-graphs on a variety of STRIPS domains.
-To measure this, we prepared two sets of experiments, of which this section describes the first.
+The purpose is to measure how E-graphs affect the number of states generated by the planner in various STRIPS domains.
+We prepared two sets of experiments, each presenting scenarios in which we hope to learn from experience.
+The STRIPS problems are taken from the HSP2 test suite; we note that every operator in these problems has cost 1.
 
-In this experiment set, we solve several hundred problem instances across 18 domains taken from the HSP2 test suite.
+\subsection{Experiment 1: Plan Completion}
+
+In this experiment set, we solve several hundred problem instances across 18 domains from the test suite.
 For each problem, we first plan without experiences, using the HSP-plus heuristic in an A* search with weight $\epsilon=5$.
 This search acts as our scientific \textbf{control}.
-If the control fails to find a solution within 5 seconds, we discard the problem instance as being too difficult.
+If the control fails to find a solution within 5 seconds (on an Intel Core i7-2600), we discard the problem instance as being too difficult.
 Otherwise, we record the plan cost and the number of states that were generated during the search.
-Thus, we end up considering 321 problem instances.
+Thus, we end up recording data for 321 problem instances.
 
 For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound.
-The E-graphs consist of 20\%, 50\% and 80\% of the edges from the control's solution path, respectively, selected at random.
-For each of these, we again record the solution cost and number of nodes generated, and compare these figures to the control.
+Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
+The latter may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.
+
+The E-graph consists of 20\%, 50\% or 80\% of the edges selected at random from the control's solution path, over the 3 respective searches.
+For each of these, we again record the solution cost and number of nodes generated, and compare these figures against the control.
 Define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
 Likewise, define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.
-We use nodes generated instead of time to produce deterministic results which are independent of most engineering details.
-The times taken generally seemed to follow similar trends; as suggested by the analysis, the time spent per node changes little when small E-graphs are used.
 
-The results are summarized in Figure \ref{tab:percent}.
+The results are summarized in Table \ref{tab:percent}.
 We see that while performance in virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
-For example, results are strongly positive in the Blocks World.
-Furthermore, figures [CITE numbers] show that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.
+For example, results are highly encouraging in the Blocks World.
+Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.
 
-Note that saving 100\% of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
-In practice, since we fixed the bias parameter $\epsilon^E$ to 5 rather than raising it to an extremely large value, the search expands a fair number of states even if we remember most or all of the path.
+Note that 100\%, or perhaps even 80\%, of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
+In practice, since we fixed the bias parameter to $\epsilon^E=5$ rather than raising it to an extremely large value, the search expands a fair number of states even if we remember most or all of the path.
 This is necessary to ensure the suboptimality bound, as the planner does not know whether the E-graph can be ``trusted" to yield an efficient path.
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_20_0.png}
-	\end{center}
-	\caption{20\% E-graph}
-	 \label{fig:s_20_0}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_50_0.png}
-	\end{center}
-	\caption{50\% E-graph}
-	 \label{fig:s_50_0}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_80_0.png}
-	\end{center}
-	\caption{80\% E-graph}
-	 \label{fig:s_80_0}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Cost_20_0.png}
-	\end{center}
-	\caption{20\% E-graph}
-	 \label{fig:c_20_0}
-\end{figure}
 
@@
 	\end{center}
-	\caption{50\% E-graph}
+	\caption{Relative costs when planning with 50\% of the control experience, displaced 0 steps from the control query.}
 	 \label{fig:c_50_0}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Cost_80_0.png}
-	\end{center}
-	\caption{80\% E-graph}
-	 \label{fig:c_80_0}
 \end{figure}
@@
 	\end{center}
-	\caption{Speedups for various E-graph \%s over various domains. Statistics are presented in the form (1st quartile)-(3rd quartile).}
+	\caption{Experiment 1 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:percent}
@@
 
-\section{Experiment 2}
+\subsection{Experiment 2: Plan Generalization}
 
-The previous experimental setup tested our ability to generalize from incomplete partial plans stored in memory; however, the new planning instances solved were identical to that used by the control to generate the E-graph.
-Now, we try moving the start and goal nodes by having each of them take 5, 20 or 50 random walk steps in the state space. 
-In this manner, we test how well E-graphs can generalize to nearby but non-identical queries.
+The previous experimental setup tested our ability to interpolate and extrapolate from incomplete partial plans stored in memory; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
+Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
+In this manner, we test how well E-graphs enable the planner to generalize to nearby but non-identical queries.
 
-We narrow our focus to 13 domains, and take from each of them the same set of instances as in the previous experiment, yielding 218 problem instances in all.
-This time, we save 100\% of the solution path found by the control.
-Then for each problem, we run 3 queries using this E-graph, moving each the start and goal by 5, 20 and 50 random steps, respectively.
+We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
+This time, we save 100\% of the solution path found by the same control used in Experiment 1.
+Then for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.
 
-Results are summarized in Figure \ref{fig:c_100_50}.
-Again we observe encouraging speedups, though they decrease as we walk farther distances from the original query.
+Note that due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
+In exactly one case out of the 3*218 = 654, this resulted in the goal already being achieved at the start state, with no nodes generated.
+In this case, we simply resolved the indeterminate form $\frac 00$ of the speedup to 1.
 
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_100_5.png}
-	\end{center}
-	\caption{5 random steps}
-	 \label{fig:s_100_5}
-\end{figure}
+Now for each of the displaced problems, we run 2 searches: the first uses no E-graph and acts as our new control, while the second uses the E-graph from the undisplaced original problem, consisting of the path found by the Experiment 1 control.
 
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_100_20.png}
-	\end{center}
-	\caption{20 random steps}
-	 \label{fig:s_100_20}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Speedup_100_50.png}
-	\end{center}
-	\caption{50 random steps}
-	 \label{fig:s_100_50}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Cost_100_5.png}
-	\end{center}
-	\caption{5 random steps}
-	 \label{fig:c_100_5}
-\end{figure}
+Results are summarized in Table \ref{tab:walk}.
+Again we observe encouraging speedups in some domains.
+As one would expect, the advantage provided by the E-graph decreases as we walk farther distances from the original query.
+Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is not typically made worse by using E-graphs.
 
@@
 	\end{center}
-	\caption{20 random steps}
+	\caption{Relative costs when planning with 100\% of the control experience, displaced 20 steps from the control query.}
 	 \label{fig:c_100_20}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.5]{Cost_100_50.png}
-	\end{center}
-	\caption{50 random steps}
-	 \label{fig:c_100_50}
 \end{figure}
@@
 	\end{center}
-	\caption{Statistics are presented in the form (1st quartile)-(3rd quartile).}
+	\caption{Experiment 2 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:walk}
@@
 
-\section{Analysis of HSPr (section to be deleted)}
+\subsection{Discussion}
 
-Whether or not E-graphs are used, the call to ComputeG($S$) at each node generation is quite substantial.
-For this reason, a variant of HSP, called HSPr, searches the regression space of STRIPS, where each node represents a ``subgoal".
-The search proceeds backward from the goal.
-In this case, the heuristic must estimate the cost to achieve a given state $S$ (considered as a subgoal) from the initial state $I$.
-A single preprocessing call to ComputeG($I$) allows each $h^{HSPr}(S) = g_I(S)$ to be computed in $O(\mathbf{A})$ time.
+Figures \ref{fig:s_20_0} to \ref{fig:s_100_50} display the individual speedups achieved over all of our experimental trials.
+We observe that cases in which E-graphs mislead the planner into generating more states are quite rare, so it seems experiences can only help.
+We set the bias parameters arbitrarily; tuning them by domain or problem size may well yield even better results.
 
-With E-graphs, in backward as well as forward search, we call ComputeG($S$) for all $S\in V^E$; only now, $V^E$ includes $I$ instead of $G$.
-From $I$, a forward Dijkstra yields $h^E(S)$ for all $S\in V^E$.
-Then for $S\notin V^E$, the E-graph heuristic estimate of the cost from $I$ to $S$ is given by
-\[h^E(S) = \min_{S'\in V^E}\left(h^E(S') + \epsilon^E g_{S'}(S) \right)\]
+On the other hand, there is some overhead to E-graph usage.
+Although we explained in the theoretical analysis that this overhead is not too large, constant factors do matter in practice, particularly when the speedups are still in the single-digits.
+We measured nodes generated instead of time to produce deterministic results which are independent of most engineering details.
+Our experiments serve as a proof-of-concept for our approach. Some additional work remains before state-of-the-art performance is achieved.
+Aside optimizations, parameter tuning, and integration with newer state-of-the-art heuristics, future work will need to consider ways to intelligently generalize from its experiences.
+This challenge does not arise to a great extent in domains such as geometric motion planning, making it unique to symbolic planning: distinct, even graphically distant, states can be conceptually related.
+(need to expand on this..)
 
-Since $g_{S'}$ was precomputed, the cost of generating a state is reduced to just $O(\mathbf{V^EA})$.
-Nonetheless, the overhead of using E-graphs is much more substantial in backward than in forward search, contributing a $|V^E|$ factor on the state generation cost.
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_20_0.png}
+	\end{center}
+	\caption{Speedups when planning with 20\% of the control experience, displaced 0 steps from the control query.}
+	 \label{fig:s_20_0}
+\end{figure}
 
-Since a major benefit of backward HSP is being able to generate states in $O(\mathbf{A})$ time, it appears E-graphs in their present form are less likely to be of much help.
-However, in domains where forward search is more practical, we saw that E-graphs can effectively provide free hints.
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_50_0.png}
+	\end{center}
+	\caption{Speedups when planning with 50\% of the control experience, displaced 0 steps from the control query.}
+	 \label{fig:s_50_0}
+\end{figure}
 
-\section{Conclusions (needs citations)}
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_80_0.png}
+	\end{center}
+	\caption{Speedups when planning with 80\% of the control experience, displaced 0 steps from the control query.}
+	 \label{fig:s_80_0}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_5.png}
+	\end{center}
+	\caption{Speedups when planning with 100\% of the control experience, displaced 5 steps from the control query.}
+	 \label{fig:s_100_5}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_20.png}
+	\end{center}
+	\caption{Speedups when planning with 100\% of the control experience, displaced 20 steps from the control query.}
+	 \label{fig:s_100_20}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.5]{Speedup_100_50.png}
+	\end{center}
+	\caption{Speedups when planning with 100\% of the control experience, displaced 50 steps from the control query.}
+	 \label{fig:s_100_50}
+\end{figure}
+
+\section{Conclusions (may need citations)}
 

### 2014-05-15 TestSuite.sh

@@ -14,8 +14,7 @@ rm -r Test/*
 #  echo "--------------------------------------------------------------------------------"
 #done
 
-#for dir in examples/*/
-for dir in "examples/satellite/" "examples/blocks/"
+for dir in examples/*/
 #for dir in "examples/blocks/" "examples/driverlog/" "examples/elevators/" "examples/freecell/" "examples/grid/" "examples/logistics00/" "examples/logistics98/" "examples/mprime/" "examples/openstacks/" "examples/pegsolitaire/" "examples/pipesworld-notankage/" "examples/pipesworld-tankage/" "examples/rovers/" "examples/satellite/" "examples/scananalyzer/" "examples/sokoban/" "examples/tpp/" "examples/transport/" "examples/zenotravel/"
 do
 	mkdir -p Test/${dir}

### 2014-05-15 AAAI_AuthorKit/paper.tex
Version for Sven

@@
 
-The results are summarized in Table \ref{tab:percent}.
+Results are summarized in Table \ref{tab:percent}.
+To estimate the typical range of speedups, we present the 25th and 75th percentile speedups among the instances of each domain.
+The full data is plotted in Figured \ref{fig:s_20_0} to \ref{fig:s_80_0}.
 We see that while performance in virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
-For example, results are highly encouraging in the Blocks World.
+For example, results are highly encouraging in the Blocks domain.
 Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.
 
-Note that 100\%, or perhaps even 80\%, of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
+Note that using 100\%, or perhaps even 80\%, of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
 In practice, since we fixed the bias parameter to $\epsilon^E=5$ rather than raising it to an extremely large value, the search expands a fair number of states even if we remember most or all of the path.
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Cost_50_0.png}
-	\end{center}
-	\caption{Relative costs when planning with 50\% of the control experience, displaced 0 steps from the control query.}
+	\caption{Relative plan costs using 50\% of the control experience, displaced 0 steps from the control query.}
 	 \label{fig:c_50_0}
@@
 \begin{table}
-	\begin{center}
-	    \begin{tabular}{| l | l | l | l | l |}
+	\centering
+	\resizebox{\columnwidth}{!}{%
+	    \begin{tabular}{| r | c | c | c | c |}
 	    \hline
-	    Domain & Inst & 20\% & 50\% & 80\%
+	    Domain & Count & 20\% exp & 50\% exp & 80\% exp
 	    \\ \hline
 	    blocks & 35 & 1.08-1.82 & 1.37-3.73 & 1.90-5.84
-	    \\ \hline
+	    \\ 
 	    driverlog & 14 & 1.00-1.49 & 1.11-1.58 & 1.15-1.60
-	    \\ \hline
+	    \\ 
 	    elevators & 30 & 1.00-1.62 & 1.00-2.84 & 1.04-3.19
-	    \\ \hline
+	    \\ 
 	    freecell & 34 & 1.00-1.06 & 1.00-1.12 & 1.00-1.08
-	    \\ \hline
+	    \\ 
 	    grid & 2 & 1.07-1.18 & 2.16-3.57 & 2.22-3.75
-	    \\ \hline
+	    \\ 
 	    logistics00 & 28 & 0.91-1.04 & 0.98-1.13 & 1.03-1.19
-	    \\ \hline
+	    \\ 
 	    logistics98 & 5 & 0.95-1.01 & 1.09-1.62 & 1.24-3.00
-	    \\ \hline
+	    \\ 
 	    mprime & 19 & 1.00-1.00 & 1.00-1.07 & 1.00-2.46
-	    \\ \hline
+	    \\ 
 	    pegsolitaire & 29 & 1.00-3.57 & 1.13-4.49 & 1.68-6.63
-	    \\ \hline
+	    \\ 
 	    pipesworld-notankage & 15 & 1.00-3.27 & 1.00-7.07 & 1.00-9.95
-	    \\ \hline
+	    \\ 
 	    pipesworld-tankage & 8 & 1.00-1.00 & 1.00-1.02 & 1.00-1.45
-	    \\ \hline
+	    \\ 
 	    rovers & 13 & 0.97-1.23 & 1.23-7.09 & 1.23-7.17
-	    \\ \hline
+	    \\ 
 	    satellite & 16 & 0.99-1.00 & 1.00-1.26 & 1.00-1.26
-	    \\ \hline
+	    \\ 
 	    scananalyzer & 16 & 1.00-1.15 & 0.93-1.20 & 1.00-1.36
-	    \\ \hline
+	    \\ 
 	    sokoban & 11 & 1.12-2.10 & 1.32-3.02 & 1.56-7.80
-	    \\ \hline
+	    \\ 
 	    tpp & 10 & 1.00-1.00 & 1.00-1.23 & 1.00-2.31
-	    \\ \hline
+	    \\ 
 	    transport & 23 & 1.00-1.14 & 1.09-1.86 & 1.19-1.89
-	    \\ \hline
+	    \\ 
 	    zenotravel & 13 & 1.02-1.15 & 1.08-1.44 & 1.14-1.58
@@
 	    \\ \hline
-	    \end{tabular}
-	\end{center}
+	    \end{tabular}%
+	}
 	\caption{Experiment 1 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
@@
 In exactly one case out of the 3*218 = 654, this resulted in the goal already being achieved at the start state, with no nodes generated.
-In this case, we simply resolved the indeterminate form $\frac 00$ of the speedup to 1.
+In this case, we resolved the indeterminate form of the speedup $\frac 00$ to 1.
 
-Now for each of the displaced problems, we run 2 searches: the first uses no E-graph and acts as our new control, while the second uses the E-graph from the undisplaced original problem, consisting of the path found by the Experiment 1 control.
+Now on each of the displaced problems, we run 2 searches: the first uses no E-graph and acts as our new control, while the second uses the E-graph created using the undisplaced original problem, consisting of the path found by the Experiment 1 control.
 
@@
 As one would expect, the advantage provided by the E-graph decreases as we walk farther distances from the original query.
-Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is not typically made worse by using E-graphs.
+Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is typically not made much worse by using E-graphs.
+Nonetheless, this time we do observe a slight cost degradation on average.
 
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Cost_100_20.png}
-	\end{center}
-	\caption{Relative costs when planning with 100\% of the control experience, displaced 20 steps from the control query.}
+	\caption{Relative plan costs using 100\% of the control experience, displaced 20 steps from the control query.}
 	 \label{fig:c_100_20}
@@
 \begin{table}
-	\begin{center}
-	    \begin{tabular}{| l | l | l | l | l |}
+	\centering
+	\resizebox{\columnwidth}{!}{%
+	    \begin{tabular}{| r | c | c | c | c |}
 	    \hline
@@
 	    blocks & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
-	    \\ \hline
+	    \\ 
 	    driverlog & 14 & 0.86-2.42 & 0.85-1.30 & 0.82-1.20
-	    \\ \hline
+	    \\ 
 	    elevators & 30 & 1.09-4.04 & 0.99-2.76 & 0.90-2.06
-	    \\ \hline
+	    \\ 
 	    grid & 2 & 2.21-3.71 & 1.11-1.34 & 1.10-1.30
-	    \\ \hline
+	    \\ 
 	    logistics00 & 28 & 1.00-1.15 & 0.90-1.11 & 0.84-1.18
-	    \\ \hline
+	    \\ 
 	    logistics98 & 5 & 1.01-2.95 & 0.82-2.06 & 0.80-2.41
-	    \\ \hline
+	    \\ 
 	    pipesworld-notankage & 15 & 1.09-5.30 & 1.00-5.46 & 1.00-2.88
-	    \\ \hline
+	    \\ 
 	    pipesworld-tankage & 8 & 1.00-1.20 & 0.99-1.00 & 1.00-1.13
-	    \\ \hline
+	    \\ 
 	    rovers & 13 & 1.00-1.50 & 1.00-1.00 & 1.00-1.00
-	    \\ \hline
+	    \\ 
 	    satellite & 16 & 0.91-1.25 & 0.87-1.15 & 0.90-1.43
-	    \\ \hline
+	    \\ 
 	    scananalyzer & 16 & 0.74-1.52 & 1.00-1.00 & 1.00-1.00
-	    \\ \hline
+	    \\ 
 	    transport & 23 & 1.26-1.91 & 0.93-1.87 & 0.98-1.46
-	    \\ \hline
+	    \\ 
 	    zenotravel & 13 & 0.80-1.27 & 0.84-1.02 & 1.00-1.00
@@
 	    \\ \hline
-	    \end{tabular}
-	\end{center}
+	    \end{tabular}%
+	}
 	\caption{Experiment 2 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
@@
 Although we explained in the theoretical analysis that this overhead is not too large, constant factors do matter in practice, particularly when the speedups are still in the single-digits.
-We measured nodes generated instead of time to produce deterministic results which are independent of most engineering details.
-Our experiments serve as a proof-of-concept for our approach. Some additional work remains before state-of-the-art performance is achieved.
-Aside optimizations, parameter tuning, and integration with newer state-of-the-art heuristics, future work will need to consider ways to intelligently generalize from its experiences.
-This challenge does not arise to a great extent in domains such as geometric motion planning, making it unique to symbolic planning: distinct, even graphically distant, states can be conceptually related.
-(need to expand on this..)
+We measured the number of nodes generated instead of the time taken to complete each search, so as to produce deterministic results which are independent of most engineering details.
+Our experiments serve as a proof-of-concept for our approach.
+
+However, some additional work remains before state-of-the-art performance can be achieved.
+Aside from engineering optimizations, parameter tuning, and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
+This presents a unique challenge in symbolic planning, as many distinct states which may even be a large distance apart in the state graph, may still be conceptually related.
+Thus, a planner could potentially benefit by learning to transfer experiences between parts of the state space which are somehow related.
+With such an approach, it would be essential to limit overgeneralization, so as not to waste time on a lot of false leads.
 
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_20_0.png}
-	\end{center}
 	\caption{Speedups when planning with 20\% of the control experience, displaced 0 steps from the control query.}
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_50_0.png}
-	\end{center}
 	\caption{Speedups when planning with 50\% of the control experience, displaced 0 steps from the control query.}
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_80_0.png}
-	\end{center}
 	\caption{Speedups when planning with 80\% of the control experience, displaced 0 steps from the control query.}
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_100_5.png}
-	\end{center}
 	\caption{Speedups when planning with 100\% of the control experience, displaced 5 steps from the control query.}
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_100_20.png}
-	\end{center}
 	\caption{Speedups when planning with 100\% of the control experience, displaced 20 steps from the control query.}
@@
 \begin{figure}
-	\begin{center}
+	\centering
 	\includegraphics[scale=0.5]{Speedup_100_50.png}
-	\end{center}
 	\caption{Speedups when planning with 100\% of the control experience, displaced 50 steps from the control query.}
@@
 
-\section{Conclusions (may need citations)}
+\section{Conclusions (will be revised)}
 

### 2014-05-16 AAAI_AuthorKit/paper.tex
premidnight version with shorter intro

@@
 \usepackage{graphicx}
+\usepackage{comment}
 \newtheorem{thm}{Theorem}
@@
 \section{Introduction}
+
+\begin{comment}
 Planning entails finding action sequences that achieve a goal state.
@@
 
-A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
+\end{comment}
+
+In forward weighted A* search, a frontier of nodes expands from the start until it hits a goal, at which point a solution is found.
+\textbf{Heuristics} are cheaply computable approximations of the remaining distance from a goal to the node.
+A* uses these to focus the search toward the goal.
+
+However, without domain expert knowledge, symbolic planning problems can be very difficult.
+A state-of-the-art domain-independent planner, or even a human faced with an unfamiliar kind of puzzle, might have great difficulty.
+Like a human, then, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
+
+A recent approach builds \textbf{experience graphs} (E-graphs) to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
 The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
@@
 such as PRIAR~\cite{Kamb:92}, SPA~\cite{Hank:95}, MRL~\cite{Koeh:94}, and NoLimit~\cite{mljournal}
-have been used recall 
+have been used to recall 
 previous plans that appear similar to the current problem and 
@@
 Compared to these methods, our work reuses prior experience in
-the context of modern weighted A* methods. We also provide
+the context of modern weighted A* based methods for symbolic planning. We also provide
 a bound on the suboptimality of the solution.
@@
 case-based reasoning method which converts 
-planning instances to into a compact graph representation and 
+planning instances into a compact graph representation and 
 then uses recent kernel methods for matching labeled graphs to select
@@
 adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method
-encourages \textit{plan stability}, which tries to make 
+that encourages \textit{plan stability}, which tries to make 
 sure that the new plan is as similar to the previous plan as possible. 
@@
 
-\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
+\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} iff $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
 $h$ is \textbf{consistent} if it is $1$-consistent.
 \end{defn}
-\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}.
-\end{thm}
+\begin{thm} Given an $\epsilon$-consistent heuristic, A* without reexpansions is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}. \end{thm}
 
@@
 
+% TODO delete
 In a sense, a lot of work is wasted by estimating the cost to reach every atom, when we only require $g_S(G)$.
@@
 Formally, an E-graph is a subgraph of the state space.
-We update it between queries, typically by adding the solution path from the previous search query.
+It is updated between queries, typically by adding the solution path from the previous search query.
 
@@
 That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
+%TODO Planning with E-graph is simply running A* or WA* with heuristic h^E.
 The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
@@
 Let $V^E$ be the union of the goal states and the E-graph's vertices.
-In addition to following E-graph edges, we imagine it's possible to ``jump" from $S$ to $S'$ at cost $\epsilon^E h(S,S')$.
+In addition to following E-graph edges, we imagine it's possible to ``jump" from any $S\in V^E$ to any $S'\in V^E$ at cost $\epsilon^E h(S,S')$.
 That is, let $c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)$
@@
 
-Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of $\pi$ according to the definition of $h^E(S)$.
+Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of the minimizing path $\pi$ in the definition of $h^E(S)$.
 Thus, we derive the mathematically equivalent but much cheaper computation
@@
 
-\begin{thm}$h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}
+\begin{thm} If the base heuristic $h$ is consistent, then $h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}
 
@@
 	\end{center}
-	\caption{An example E-graph and corresponding heuristic computations.}
+	\caption{An example E-graph and corresponding $h^E$-values.}
 	\label{fig:example}
@@
 
-Now we combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
+We now combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
 In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$.
@@
 Multiplying nested loop iterations together and dropping cardinality signs for brevity, a conservative runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
-Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.
+Therefore, it costs $O(\mathbf{A^2O + V^EA})$ time to generate each state.
 
@@
 \begin{thm}
-Provided there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
+If there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP-max search algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
 \end{thm}
@@
 
-Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially.
+%TODO Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially.
 Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors.
@@
 Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.
-If still more processors are available, some may dedicate to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g.
+If still more processors are available, some may be dedicated to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g.
 near the A* frontier.
@@
 
-\subsection{Experiment 1: Plan Completion}
+\subsection{Experiment 1: Reusing Fragmented Experiences}
 
@@
 This search acts as our scientific \textbf{control}.
-If the control fails to find a solution within 5 seconds (on an Intel Core i7-2600), we discard the problem instance as being too difficult.
+If the control fails to find a solution within 5 seconds (on an Intel Core i7-2600), we discard the problem instance.
 Otherwise, we record the plan cost and the number of states that were generated during the search.
@@
 
-For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound.
-Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
-The latter may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.
+For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound as planning without E-graphs weighted by $\epsilon=5$.
+(Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
+HSP-plus may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.)
 
@@
 For each of these, we again record the solution cost and number of nodes generated, and compare these figures against the control.
-Define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
-Likewise, define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.
+We define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
+Likewise, we define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.
 
@@
 To estimate the typical range of speedups, we present the 25th and 75th percentile speedups among the instances of each domain.
-The full data is plotted in Figured \ref{fig:s_20_0} to \ref{fig:s_80_0}.
-We see that while performance in virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
+The full data is plotted in Figures \ref{fig:s_20_0} to \ref{fig:s_80_0}.
+We see that, while performance is virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
 For example, results are highly encouraging in the Blocks domain.
@@
 
-\subsection{Experiment 2: Plan Generalization}
+\subsection{Experiment 2: Reusing Nearby Experiences}
 
-The previous experimental setup tested our ability to interpolate and extrapolate from incomplete partial plans stored in memory; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
+The previous experimental setup tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
 Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
@@
 This time, we save 100\% of the solution path found by the same control used in Experiment 1.
-Then for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.
-
-Note that due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
-In exactly one case out of the 3*218 = 654, this resulted in the goal already being achieved at the start state, with no nodes generated.
-In this case, we resolved the indeterminate form of the speedup $\frac 00$ to 1.
+Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.
+Note that, due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
 
@@
 
+%TODO trend speedup vs nodesgen
 Figures \ref{fig:s_20_0} to \ref{fig:s_100_50} display the individual speedups achieved over all of our experimental trials.
@@
 However, some additional work remains before state-of-the-art performance can be achieved.
-Aside from engineering optimizations, parameter tuning, and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
+Aside from engineering optimizations and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
 This presents a unique challenge in symbolic planning, as many distinct states which may even be a large distance apart in the state graph, may still be conceptually related.
@@
 
-We saw that by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences.
+We saw that, by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences.
 Many interesting directions remain for future investigation.
@@
 However, it's crucial not to overgeneralize as that might simply lead to most of the graph being reweighted uniformly.
-The problem of generalization seem related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.
+The problem of generalization seems related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.
 
 E-Graphs should be thought of not so much as a specific algorithm, but as a tool which is orthogonal to a lot of the major planning techniques out there.
-Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to get anytime, incremental search using experiences in symbolic domains.
+Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to obtain anytime, incremental search for using experiences in symbolic domains.
 
@@
 If an unexpected event invalidates a robot's plan mid-execution, the replanner can remember the original solution as an E-graph to encourage reparations along the old path.
-In addition to speeding replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
+In addition to speeding up replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
 Minimizing disruption is important when resources must be allocated according to the plan, or cognitively-burdened humans are involved with its execution.

### 2014-05-16 AAAI_AuthorKit/paper.tex
SoCS 2014 submission

@@
 /Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
-/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
+/Keywords (symbolic planning, E-Graph, experience-biased, weighted A* search, STRIPS, HSP)
 }
@@
 }
+\author{SoCS 2014 Submission 2}% anonymizer
 \maketitle
@@
 Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
-
 \end{comment}
 
+Modern state-of-the-art symbolic planners tend to rely on weighted A* search as their core algorithm.
 In forward weighted A* search, a frontier of nodes expands from the start until it hits a goal, at which point a solution is found.
-\textbf{Heuristics} are cheaply computable approximations of the remaining distance from a goal to the node.
-A* uses these to focus the search toward the goal.
+The performance of weighted A* depends heavily on its \textit{heuristics}, cheaply computable approximations of the remaining distance from a given node to the goal.
+Heuristics focus the efforts of weighted A* toward the goal and can greatly impact the runtime of the search.
+Consequently, much research has been devoted to developing new heuristic functions and different techniques for combining multiple heuristic functions together, all with the aim of providing more effective guidance to the weighted A* search.
 
-However, without domain expert knowledge, symbolic planning problems can be very difficult.
-A state-of-the-art domain-independent planner, or even a human faced with an unfamiliar kind of puzzle, might have great difficulty.
-Like a human, then, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
+However, even with good heuristic functions, many symbolic planning problems can be very difficult to solve.
+A state-of-the-art domain-independent planner, or even a human faced with an unfamiliar kind of problem, might have great difficulty in solving it.
+After having solved several instances of a problem, humans tend to utilize their experience and learn how to solve similar problems quickly.
+Similarly, it is beneficial to develop planning algorithms that can learn to solve repeated planning problems faster over time.
 
-A recent approach builds \textbf{experience graphs} (E-graphs) to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
-The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
-A variant of weighted A* is employed which biases its focus toward the E-graph.
-While this work demonstrates promising results in robot motion planning, E-graphs have never before been applied to symbolic domain representations such as the STRIPS language.
+In robotics, Experience Graphs (E-Graphs) have recently been introduced as a means of accelerating motion planning from experience~\cite{phillips2012graphs}.
+Based on previously computed plans (a.k.a. experiences), this methods computes an E-Graph that models the high-level connectivity of the free space in motion planning tasks.
+The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-Graph.
+A variant of weighted A* is employed which biases its focus toward the E-Graph.
+While this work demonstrates promising results in robot motion planning, E-Graphs have never before been applied to symbolic domain representations such as the STRIPS language.
 
-Our present contribution is to investigate the use of E-graphs in STRIPS domains.
-In particular, we take the HSP2 planner \cite{bonet2001planning} as a representative of the class of modern weighted A* based symbolic planners, and augment its heuristic with a bias toward its E-graph.
+Our present contribution is to investigate the use of E-Graphs in STRIPS domains.
+In particular, we take the HSP2 planner~\cite{bonet2001planning} as a representative of the class of modern symbolic planners that are based on weighted A*, and augment its heuristic with a bias toward its E-Graph.
 After presenting the related works, we begin by describing the STRIPS language and the original HSP heuristic.
-In the following section, we formally introduce E-graphs in technical detail.
+In the following section, we formally introduce E-Graphs in technical detail.
 Then we combine the two approaches, resulting in the new Experience-Biased HSP planner.
 We present the algorithm and discuss its theoretical properties.
-This is followed by experiments showing promise for the application of E-graphs to symbolic problem solving.
+This is followed by experiments showing promise for the application of E-Graphs to symbolic problem solving.
 Finally, we conclude with some thoughts on extensions worth investigating.
@@
 have been used to recall 
-previous plans that appear similar to the current problem and 
+previous plans that appear similar to the current problem, and 
 then adapt them to meet the new specifications.
 Compared to these methods, our work reuses prior experience in
-the context of modern weighted A* based methods for symbolic planning. We also provide
+the context of modern weighted A*-based methods for symbolic planning. We also provide
 a bound on the suboptimality of the solution.
 
-Recently there has been work on incorporating prior knowledge 
+Recently, there has been work on incorporating prior knowledge 
 into modern planners (based on weighted A* and powerful heuristics).
@@
 inconsistencies. To guarantee completeness, the windows can grow 
-if solutions are not found until they contrain the whole plan.
-In this work~\cite{DBLP:conf/iccbr/RosaOB07} case-based reasoning is used to choose the 
-order of state evaluations of EHC (enforced hill-climbing) which 
+if solutions are not found until they constrain the whole plan.
+In this work~\cite{DBLP:conf/iccbr/RosaOB07}, case-based reasoning is used to choose the 
+order of state evaluations of EHC (enforced hill-climbing), which 
 is a component in modern planners such as FF.
@@
 case-based reasoning method which converts 
-planning instances into a compact graph representation and 
+planning instances into a compact graph representation, and 
 then uses recent kernel methods for matching labeled graphs to select
 a similar case to the problem at hand. The selected case is then 
-adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method
-that encourages \textit{plan stability}, which tries to make 
+adapted using LPG-ADAPT~\cite{Fox06planstability}. LPG-ADAPT is a replanning method
+that encourages \textit{plan stability}: it tries to make 
 sure that the new plan is as similar to the previous plan as possible. 
 The method also uses a modern heuristic search approach.
+While E-Graphs too can encourage stability by reusing old plans, our primary purpose is efficient planning with cost suboptimality bounds, rather than stability.
 
@@
 reuse to symbolic planning. The planner randomly chooses to extend 
-the search tree toward the goal, toward goals from previous 
+the search tree toward the goal, toward subgoals from previous 
 plans, or to reuse an action from a previous plan. 
@@
 
-The primary difference between our approach and previous ones 
-is that we plan with prior experience in a way that have provable
-bounds on suboptimality of the solution. The use of E-Graphs also
-allows us to formulate this in a way that the user has control over
+The primary difference between our approach and previous works 
+is that we plan with prior experience in a way that comes with provable
+bounds on the suboptimality of the solution. The use of E-Graphs also
+allows us to formulate this in such a way that the user has control over
 this suboptimality bound with an intuitive parameter that trades
@@
 
-The HSP2 \cite{bonet2001planning} planner uses the heuristic pioneered by HSP, but replaces greedy hill-climbing with weighted A* search.
-We test our approach on HSP2 because the latter is straightforward to describe and it is representative of the core techniques that are common to many state-of-the-art domain-independent symbolic planners.
-Some newer additions to the field include the causal graph heuristic of the Fast Downward planner \cite{helmert2006fast} and the landmark heuristic of the LAMA planner \cite{richter2010lama}.
+The HSP2~\cite{bonet2001planning} planner uses the heuristic pioneered by HSP, but replaces greedy hill-climbing with weighted A* search.
+We test our approach on HSP2 because the latter is straightforward to describe, and because it is representative of the core techniques that are common to many state-of-the-art domain-independent symbolic planners.
+Some newer additions to the field include the causal graph heuristic of the Fast Downward planner~\cite{helmert2006fast} and the landmark heuristic of the LAMA planner~\cite{richter2010lama}.
 Our approach is orthogonal to these developments and can, in principle, be adapted to work with any search heuristic.
@@
 
-Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP2 planner \cite{bonet2001planning}, which we now describe.
+Many of today's state-of-the-art domain-independent STRIPS planners are based on the HSP2 planner~\cite{bonet2001planning}, which we now describe.
 It's common to compute heuristics by solving an easier, relaxed version of the original problem. In STRIPS, one might ignore the delete lists of operations.
-Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the resulting heuristic never overestimates the true cost.
+Since having more atoms makes preconditions and the goal condition more likely to hold, this can only make the problem easier, so the heuristic derived from relaxation never overestimates the true cost.
 
 However, even the relaxed STRIPS planning problem includes set-cover as a special case, making it NP-hard.
-Intuitively, we see that the relaxed search space remains exponential.
+Intuitively, we see that the relaxed search space remains exponential in size.
 To reduce it, HSP2 decouples the atoms, instead estimating the cost of achieving each individual atom.
 
-Let's say we want a heuristic estimate of the distance from $S$ to a goal that contains $G$. HSP2 estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
+Let's say we want a heuristic estimate of the distance from state $S$ to a goal that contains $G$. HSP2 estimates the cost to achieve an atom $a\in A$ from $S$ by $g_S(a) = $
 \[\begin{cases} 0  &\mbox{if } a \in S
@@
 To keep the computations feasible, define $g_S(P) = \max_{p\in P} g_S(p)$ for atom sets $P$.
-The resulting HSP-max heuristic is an underestimate; indeed, it satisfies a stronger property called \textbf{consistency}.
+The resulting HSP-max heuristic is an underestimate; indeed, it satisfies a stronger property called consistency.
 
 \begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} iff $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$.
-$h$ is \textbf{consistent} if it is $1$-consistent.
+$h$ is \textbf{consistent} iff it is $1$-consistent.
 \end{defn}
-\begin{thm} Given an $\epsilon$-consistent heuristic, A* without reexpansions is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}. \end{thm}
+\begin{thm} Given an $\epsilon$-consistent heuristic, A* without reexpansions is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost~\cite{LikGorThr-ara}. \end{thm}
 
-If the atoms were truly independent, a more accurate estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
-Despite its inconsistency in general, the latter HSP-plus heuristic is often useful in practice, as it uses more information and biases more greedily toward the goal.
+If the atoms were completely independent, a more accurate estimate would be $g_S(P) = \sum_{p\in P} g_S(p)$.
+Despite its inconsistency in general, the latter HSP-plus heuristic is often useful in practice, as it uses more state information: it decreases if progress is made towards \textit{any} goal atom, instead of just the most distant goal.
 
@@
 
-% TODO delete
-In a sense, a lot of work is wasted by estimating the cost to reach every atom, when we only require $g_S(G)$.
-Later, we'll see how to make better use of this computation.
-
 \section{Experience Graphs}
 
-E-graphs can improve total search time over a series of related queries on the same graph.
-Formally, an E-graph is a subgraph of the state space.
+E-Graphs can improve total search time over a series of related queries on the same graph.
+Formally, an E-Graph is a subgraph of the state space.
 It is updated between queries, typically by adding the solution path from the previous search query.
@@
 That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
-%TODO Planning with E-graph is simply running A* or WA* with heuristic h^E.
-The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
+
+Planning with E-Graphs is simply a matter of running weighted A* search with the \textbf{E-graph heuristic} $h^E$, derived from $h$.
+$h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
 To be precise, define
 
-\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \{\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\}\]
-with the minimization taking place over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$. $c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.
+\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \left(\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\right)\]
+with the minimization taking place over all goal states $S_N$ and all paths $\pi = \langle S_0,S_1,...,S_N \rangle$ of arbitrary length.
 
-In the limit as $\epsilon^E \rightarrow 1$, E-graph edges offer no advantage as $h(S_{i-1},S_i) \le c^E(S_{i-1},S_i)$. Hence, using the triangle inequality to coalesce the sum,
+$c^E$ encodes E-Graph edge costs, or $\infty$ if the corresponding edge is not a part of the E-Graph.
+
+In the limit as $\epsilon^E \rightarrow 1$, E-Graph edges offer no advantage because $h(S_{i-1},S_i) \le c^E(S_{i-1},S_i)$. Hence, using the triangle inequality to coalesce the sum,
 \[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N h(S_{i-1},S_i) = \min_{S_N} h(S_0,S_N)\]
@@
 Conversely, as $\epsilon^E \rightarrow\infty$, the inflated terms dominate.
-Hence, the minimizing path becomes the one which incurs the least estimated cost outside the E-graph.
+Hence, the minimizing path becomes one which incurs the least estimated cost outside the E-Graph.
 In particular, $h^E$ has the following property:
 
-\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.}
+\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-Graph component which includes a goal state, no node outside the E-Graph will ever again need to be expanded.}
 
-This means, for instance, that if the E-graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-graph.
-If the E-graph is small, a solution would promptly be discovered.
+This means, for instance, that if the E-Graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-Graph.
+If the E-Graph is small, a solution would promptly be discovered.
 In this manner, little work is needed to solve previously encountered subproblems.
@@
 Fortunately, there exists a practical means of computing it. By the triangle inequality, any consecutive pair of $h(S_{i-1},S_i)$ terms can be merged into one.
-Thus, we lose no generality in restricting $S_i$ to lie on the E-graph for $0 < i < N$.
-The heuristic computation can focus on the E-graph, using $h(S_{i-1},S_i)$ to estimate the cost of leaving the E-graph at $S_{i-1}$ before re-entering it at $S_i$.
+Thus, we lose no generality in restricting $S_i$ to lie on the E-Graph for $0 < i < N$.
+The heuristic computation can focus on the E-Graph, using $h(S_{i-1},S_i)$ to estimate the cost of leaving the E-Graph at $S_{i-1}$ before reentering it at $S_i$.
 
-Let $V^E$ be the union of the goal states and the E-graph's vertices.
-In addition to following E-graph edges, we imagine it's possible to ``jump" from any $S\in V^E$ to any $S'\in V^E$ at cost $\epsilon^E h(S,S')$.
-That is, let $c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)$
+Let $V^E$ be the union of the goal states and the E-Graph's vertices.
+In addition to following E-Graph edges, we imagine it's possible to ``jump" from any $S\in V^E$ to any $S'\in V^E$ at cost $\epsilon^E h(S,S')$.
+That is, let
+\[c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)\]
 
 In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$.
-Ignoring the computation of $h$ (presently considered as a blackbox), this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-graphs and goal sets.
+Ignoring the computation of $h$ (presently considered as a blackbox), this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-Graphs and goal sets.
 
-Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of the minimizing path $\pi$ in the definition of $h^E(S)$.
+Later, when A* generates $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of the minimizing path $\pi$ in the definition of $h^E(S)$.
 Thus, we derive the mathematically equivalent but much cheaper computation
@@
 
-\begin{thm} If the base heuristic $h$ is consistent, then $h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}
+\begin{thm} If the base heuristic $h$ is consistent, then $h^E$ is $\epsilon^E$-consistent~\cite{phillips2012graphs}.\end{thm}
 
@@
 	\end{center}
-	\caption{An example E-graph and corresponding $h^E$-values.}
+	\caption{An example E-Graph with three edges, and corresponding $h^E$-values. $S$ is not on the E-graph.}
 	\label{fig:example}
@@
 Figure \ref{fig:example} illustrates the idea.
-Suppose the dark edges have cost 3 and make up the E-graph.
-Off-E-graph edges are not shown, as they are only accessed indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
+Suppose the dark edges have cost 3 and make up the E-Graph.
+Off-E-Graph edges are not shown, as they are only referenced indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively).
 Dijkstra's algorithm follows dark and light edges backward to compute the $h^E$ values shown alongside each node.
 
-$G$ is on the E-graph, though this need not be the case in general.
+$G$ is on the E-Graph, though this need not be the case in general.
 $V^E$ is the pentagon on the right, and its $h^E$ values are precomputed before the search.
@@
 
-We now combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience.
+We now combine the ideas from HSP2 and E-Graphs to construct a domain-independent STRIPS planner which learns from experience.
 In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$.
-We can compute $g_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of Algorithm \ref{alg:ComputeG}: each run provides us with $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.
+We can compute $g_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of Algorithm \ref{alg:ComputeG}: each run provides us with $|V^E|$ of these values, yielding $|V^E|^2$ values in total.
 
-As before, Dijkstra's algorithm combines an inflation of these estimates with the E-graph edges to derive $h^E(S)$ for all $S\in V^E$.
+As before, Dijkstra's algorithm inflates and combines these estimates with the E-Graph edges to derive $h^E(S)$ for all $S\in V^E$.
 Note that in STRIPS, $V^E$ need not include every goal state: the minimal goal $G$ suffices as it's always the easiest to reach in the heuristic relaxation.
 
-Upon encountering a new state $S\notin V^E$, we run Algorithm \ref{alg:ComputeG} again to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-graph heuristic by
+Upon encountering a new state $S\notin V^E$, we run Algorithm \ref{alg:ComputeG} again to compute $g_S(a)$ for all atoms $a\in A$. Then it's a simple matter to compute the E-Graph heuristic by
 
@@
 
-We remark that, when E-graphs are involved, the values $g_S(S')$ on the right-hand side range over a variety of different states $S'$.
+We remark that, when E-Graphs are involved, the values $g_S(S')$ on the right-hand side range over a variety of different states $S'$.
 Compare this to the formula for $h^{HSP}$, which uses only $g_S(G)$.
-HSP2 would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-graph essentially for free.
+HSP2 would still compute all the $g_S$-values despite using them only once, so here we get to consult the E-Graph essentially for free.
 The only additional work is the minimization over $S'\in V^E$, which takes O($|V^E||A|$) time.
 A pseudocode implementation is listed in Algorithm \ref{alg:Search}.
-The parameter $\epsilon^E$ controls bias toward the E-graph, while the weight $\epsilon$ provides a uniform goal-directed bias.
+The parameter $\epsilon^E$ controls bias toward the E-Graph, while the weight $\epsilon$ provides a uniform goal-directed bias.
 
@@
 \IF{A* successfully found a path to some goal state $S \supseteq G$}
-\STATE Add all edges of the solution path to the E-graph.
+\STATE Add all edges of the solution path to the E-Graph.
 \RETURN solution path
@@
 
-For comparison, standard HSP2 without E-graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate each state, and does not incur the cost of generating a state unless the A* frontier encounters it.
-When HSP2 is augmented with small E-graphs, the same asymptotic bound continues to hold, provided that the number of E-graph vertices is limited to $O(\mathbf{AO})$.
+For comparison, standard HSP2 without E-Graphs takes $O(\mathbf{A^2O})$ time (with essentially the same constant factors) to generate each state, and does not incur the cost of generating a state unless the A* frontier encounters it.
+When HSP2 is augmented with small E-Graphs, the same asymptotic bound continues to hold, provided that the number of E-Graph vertices is limited to $O(\mathbf{AO})$.
 Furthermore, we retain completeness and the ability to configure suboptimality bounds by adjusting the bias parameters:
@@
 This follows directly from Theorems 1 and 2, since the weighted heuristic $\epsilon h^E$ is $\epsilon \epsilon^E$-consistent.
-However, E-graphs make no guarantee of improving the search time. Indeed, biasing toward bad regions could trap the planner inside large local optima.
-Potential gains depend entirely on choosing a good small set of edges to form our E-graph.
+However, E-Graphs make no guarantee of improving the search time. Indeed, biasing toward bad regions could trap the planner inside large local optima.
+Potential gains depend entirely on choosing a good small set of edges to form our E-Graph.
 In our experiments, we simply keep the previous solution path; different choices remain a topic for future investigations.
 
-%TODO Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially.
-Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors.
-Therefore, with minor adjustments, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$.
-With $\mathbf{A\max(O,V^E)}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$.
-Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.
-If still more processors are available, some may be dedicated to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g.
-near the A* frontier.
+\section{Experiments}
 
-\section{Experimental Analysis}
-
-We augmented the original HSP2 planner code \cite{bonet2001planning} with E-graphs.
+We augmented the original HSP2 planner code~\cite{bonet2001planning} with E-Graphs.
 Since HSP-plus performs better in practice than HSP-max, we take the former heuristic as our baseline.
-The purpose is to measure how E-graphs affect the number of states generated by the planner in various STRIPS domains.
-We prepared two sets of experiments, each presenting scenarios in which we hope to learn from experience.
+The purpose is to measure how E-Graphs affect the number of states generated by the planner in various STRIPS domains.
+We prepared two experiments, each presenting scenarios in which we hope for the planner to learn from experience.
 The STRIPS problems are taken from the HSP2 test suite; we note that every operator in these problems has cost 1.
@@
 
-In this experiment set, we solve several hundred problem instances across 18 domains from the test suite.
+In this experiment, we solve several hundred problem instances spanning 18 symbolic domains.
 For each problem, we first plan without experiences, using the HSP-plus heuristic in an A* search with weight $\epsilon=5$.
@@
 
-For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound as planning without E-graphs weighted by $\epsilon=5$.
+For each of these, we run 3 additional searches using E-Graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound as planning with no E-Graph weighted by $\epsilon=5$.
 (Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
-HSP-plus may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.)
+HSP-plus may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are extremely highly coupled.)
 
-The E-graph consists of 20\%, 50\% or 80\% of the edges selected at random from the control's solution path, over the 3 respective searches.
+The E-Graph consists of 20\%, 50\% or 80\% of the edges selected at random from the control's solution path, over the 3 respective searches.
 For each of these, we again record the solution cost and number of nodes generated, and compare these figures against the control.
-We define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
-Likewise, we define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.
+We define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-Graph search.
+Likewise, we define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-Graph search.
 
@@
 To estimate the typical range of speedups, we present the 25th and 75th percentile speedups among the instances of each domain.
-The full data is plotted in Figures \ref{fig:s_20_0} to \ref{fig:s_80_0}.
-We see that, while performance is virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
+The full data from Experiment 1 is plotted in Figures \ref{fig:s_20_0} to \ref{fig:s_80_0}.
+We see that, while performance is virtually unaffected in some domains, it's never substantially worsened and, in certain domains, the experience helps greatly.
 For example, results are highly encouraging in the Blocks domain.
-Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.
+Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-Graphs are employed, the path cost is slightly reduced on average.
 
-Note that using 100\%, or perhaps even 80\%, of the E-graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
+Note that using 100\%, or perhaps even 80\%, of the E-Graph would seem to trivially grant us the solution, as we could simply follow the remembered path depth-first.
 In practice, since we fixed the bias parameter to $\epsilon^E=5$ rather than raising it to an extremely large value, the search expands a fair number of states even if we remember most or all of the path.
-This is necessary to ensure the suboptimality bound, as the planner does not know whether the E-graph can be ``trusted" to yield an efficient path.
+This is necessary to ensure the suboptimality bound, as the planner does not know whether the E-Graph can be ``trusted" to yield an efficient path.
+E-graphs are used as suggestions, not as a trusted form of knowledge; the planner remains responsible for proving suboptimality.
 
@@
 	}
-	\caption{Experiment 1 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
+	\caption{Experiment 1 speedup statistics, summarized in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:percent}
@@
 
-The previous experimental setup tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
+The previous experiment tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-Graph.
 Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
-In this manner, we test how well E-graphs enable the planner to generalize to nearby but non-identical queries.
+In this manner, we test how well E-Graphs enable the planner to generalize to nearby but non-identical queries.
 
 We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
-This time, we save 100\% of the solution path found by the same control used in Experiment 1.
-Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.
+This time, we save 100\% of the solution path found by the problem's corresponding control from Experiment 1.
+Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps, respectively, of random walk along the graph.
 Note that, due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
 
-Now on each of the displaced problems, we run 2 searches: the first uses no E-graph and acts as our new control, while the second uses the E-graph created using the undisplaced original problem, consisting of the path found by the Experiment 1 control.
+Now, on each of the displaced problems, we run 2 searches: the first uses no E-Graph and acts as our new control, while the second uses the E-Graph created using the undisplaced original problem, consisting of the path found by the Experiment 1 control.
+Speedup and cost improvement ratios are taken with respect to Experiment 2 controls; this is to provide an apples-to-apples comparison, as the displaced problem is different from the original.
 
-Results are summarized in Table \ref{tab:walk}.
+Results are summarized in Table \ref{tab:walk}, with the full distributions plotted in Figures \ref{fig:s_100_5} to \ref{fig:s_100_50}.
 Again we observe encouraging speedups in some domains.
-As one would expect, the advantage provided by the E-graph decreases as we walk farther distances from the original query.
-Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is typically not made much worse by using E-graphs.
+As one would expect, the advantage provided by the E-Graph decreases as we walk farther distances from the original query.
+Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is typically not made much worse by using E-Graphs.
 Nonetheless, this time we do observe a slight cost degradation on average.
@@
 	}
-	\caption{Experiment 2 speedup statistics, summarized by domain in the form (1st quartile)-(3rd quartile).}
+	\caption{Experiment 2 speedup statistics, summarized in the form (1st quartile)-(3rd quartile).}
 	 \label{tab:walk}
@@
 
-\subsection{Discussion}
+\section{Discussion}
 
-%TODO trend speedup vs nodesgen
 Figures \ref{fig:s_20_0} to \ref{fig:s_100_50} display the individual speedups achieved over all of our experimental trials.
-We observe that cases in which E-graphs mislead the planner into generating more states are quite rare, so it seems experiences can only help.
+We observe that cases in which E-Graphs mislead the planner into generating more states (i.e.
+speedup $<$ 1) are quite rare, so it seems experiences can only help.
 We set the bias parameters arbitrarily; tuning them by domain or problem size may well yield even better results.
+Interestingly, we observe a clear positive correlation between problem size or difficulty, as measured by the number of nodes generated in the control, and the speedup factor.
+This suggests E-graphs may be especially helpful on the hardest problems.
 
-On the other hand, there is some overhead to E-graph usage.
-Although we explained in the theoretical analysis that this overhead is not too large, constant factors do matter in practice, particularly when the speedups are still in the single-digits.
+On the other hand, there is some overhead to E-Graph usage.
+Although we explained in the theoretical analysis that the overhead is not too large, constant factors do matter in practice, particularly when the speedups are still in the single-digits.
 We measured the number of nodes generated instead of the time taken to complete each search, so as to produce deterministic results which are independent of most engineering details.
@@
 However, some additional work remains before state-of-the-art performance can be achieved.
-Aside from engineering optimizations and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
-This presents a unique challenge in symbolic planning, as many distinct states which may even be a large distance apart in the state graph, may still be conceptually related.
+Aside from engineering optimizations and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-Graphs.
+This presents a unique challenge in symbolic planning, as distinct states, even if separated by a large distance in the state transition graph, may still be conceptually related.
 Thus, a planner could potentially benefit by learning to transfer experiences between parts of the state space which are somehow related.
-With such an approach, it would be essential to limit overgeneralization, so as not to waste time on a lot of false leads.
+With such an approach, it would be essential to limit overgeneralization, so as not to waste too much time on false leads.
+
+Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially.
+Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors.
+Therefore, with minor adjustments, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$.
+With $\mathbf{A\max(O,V^E)}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$.
+Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.
+If still more processors are available, some may be dedicated to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g.
+near the E-graph or A* frontier.
 
@@
 
-\section{Conclusions (will be revised)}
+\section{Conclusions}
 
-We saw that, by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences.
+We saw that, by reusing pieces from past plans, E-Graph-based planners can find solutions more quickly as they learn and acquire experiences.
 Many interesting directions remain for future investigation.
 It remains unclear how the bias parameters should be set.
-In addition, more advanced schemes will be needed to expand and prune E-graphs if they get large due to collecting a lot of solutions.
-Saving each computed plan seems like a good idea intuitively, but other possibilities may be worth investigating.
+In addition, more advanced schemes will be needed to expand and prune E-Graphs if they grow large from collecting a lot of solutions.
+Keeping track of the most recently computed plans seems like a good idea intuitively, but other possibilities may be worth trying.
 
-For STRIPS in particular, distinct states can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches.
-However, it's crucial not to overgeneralize as that might simply lead to most of the graph being reweighted uniformly.
+As mentioned in the discussion, generalization and parallelization certainly merit further investigation.
+Generalization is a particularly important problem in AI learning theory, and there is plenty of literature on the topic.
+For example, \cite{fikes1972learning} generalize plans on the original STRIPS problem solver.
 The problem of generalization seems related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.
+Works such as \cite{helmert2007flexible} project symbolic state graphs onto smaller spaces; one could potentially apply E-graphs on the projected space to achieve the desired generalization.
 
 E-Graphs should be thought of not so much as a specific algorithm, but as a tool which is orthogonal to a lot of the major planning techniques out there.
-Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to obtain anytime, incremental search for using experiences in symbolic domains.
+In principle, one could apply E-Graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to obtain anytime, incremental search using experiences as in \cite{phillips2013anytime}, but in symbolic domains.
 
-Finally, E-Graphs could potentially find other uses, in particular for replanning.
-If an unexpected event invalidates a robot's plan mid-execution, the replanner can remember the original solution as an E-graph to encourage reparations along the old path.
-In addition to speeding up replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
-Minimizing disruption is important when resources must be allocated according to the plan, or cognitively-burdened humans are involved with its execution.
+Finally, E-Graphs might find other uses, such as in replanning.
+If an unexpected event invalidates a robot's plan mid-execution, the replanner can recall the original solution as an E-Graph to encourage reparations along the old path.
+In addition to speeding up replanning, the E-Graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
+Minimizing disruption is important when resources must be allocated in advance according to the plan, or when cognitively-burdened humans are involved with its execution.
 

### 2014-05-16 AAAI_AuthorKit/paper.tex
Morning submission

@@
 
-\subsection{Experiment 2: Reusing Nearby Experiences}
-
-The previous experiment tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-Graph.
-Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
-In this manner, we test how well E-Graphs enable the planner to generalize to nearby but non-identical queries.
-
-We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
-This time, we save 100\% of the solution path found by the problem's corresponding control from Experiment 1.
-Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps, respectively, of random walk along the graph.
-Note that, due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
-
-Now, on each of the displaced problems, we run 2 searches: the first uses no E-Graph and acts as our new control, while the second uses the E-Graph created using the undisplaced original problem, consisting of the path found by the Experiment 1 control.
-Speedup and cost improvement ratios are taken with respect to Experiment 2 controls; this is to provide an apples-to-apples comparison, as the displaced problem is different from the original.
-
-Results are summarized in Table \ref{tab:walk}, with the full distributions plotted in Figures \ref{fig:s_100_5} to \ref{fig:s_100_50}.
-Again we observe encouraging speedups in some domains.
-As one would expect, the advantage provided by the E-Graph decreases as we walk farther distances from the original query.
-Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is typically not made much worse by using E-Graphs.
-Nonetheless, this time we do observe a slight cost degradation on average.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.5]{Cost_100_20.png}
-	\caption{Relative plan costs using 100\% of the control experience, displaced 20 steps from the control query.}
-	 \label{fig:c_100_20}
-\end{figure}
-
 \begin{table}
@@
 	    \hline
-	    Domain & Inst & 5 steps & 20 steps & 50 steps
+	    Domain & Count & 5 steps & 20 steps & 50 steps
 	    \\ \hline
@@
 
+\subsection{Experiment 2: Reusing Nearby Experiences}
+
+The previous experiment tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-Graph.
+Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
+In this manner, we test how well E-Graphs enable the planner to generalize to nearby but non-identical queries.
+
+We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
+This time, we save 100\% of the solution path found by the problem's corresponding control from Experiment 1.
+Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps, respectively, of random walk along the graph.
+Note that, due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
+
+Now, on each of the displaced problems, we run 2 searches: the first uses no E-Graph and acts as our new control, while the second uses the E-Graph created using the undisplaced original problem, consisting of the path found by the Experiment 1 control.
+Speedup and cost improvement ratios are taken with respect to Experiment 2 controls; this is to provide an apples-to-apples comparison, as the displaced problem is different from the original.
+
+Results are summarized in Table \ref{tab:walk}, with the full distributions plotted in Figures \ref{fig:s_100_5} to \ref{fig:s_100_50}.
+Again we observe encouraging speedups in some domains.
+As one would expect, the advantage provided by the E-Graph decreases as we walk farther distances from the original query.
+Figure \ref{fig:c_100_20} is a representative plot to show that, once again, path quality is typically not made much worse by using E-Graphs.
+Nonetheless, this time we do observe a slight cost degradation on average.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.5]{Cost_100_20.png}
+	\caption{Relative plan costs using 100\% of the control experience, displaced 20 steps from the control query.}
+	 \label{fig:c_100_20}
+\end{figure}
+
 \section{Discussion}
@@
 
+\section{Conclusions}
+
+We saw that, by reusing pieces from past plans, E-Graph-based planners can find solutions more quickly as they learn and acquire experiences.
+Many interesting directions remain for future investigation.
+It remains unclear how the bias parameters should be set.
+In addition, more advanced schemes will be needed to expand and prune E-Graphs if they grow large from collecting a lot of solutions.
+Keeping track of the most recently computed plans seems like a good idea intuitively, but other possibilities may be worth trying.
 \begin{figure}
@@
 \end{figure}
-
-\section{Conclusions}
-
-We saw that, by reusing pieces from past plans, E-Graph-based planners can find solutions more quickly as they learn and acquire experiences.
-Many interesting directions remain for future investigation.
-It remains unclear how the bias parameters should be set.
-In addition, more advanced schemes will be needed to expand and prune E-Graphs if they grow large from collecting a lot of solutions.
-Keeping track of the most recently computed plans seems like a good idea intuitively, but other possibilities may be worth trying.
-
 As mentioned in the discussion, generalization and parallelization certainly merit further investigation.
@@
 In addition to speeding up replanning, the E-Graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan.
-Minimizing disruption is important when resources must be allocated in advance according to the plan, or when cognitively-burdened humans are involved with its execution.
+Minimizing disruption is important when resources must be allocated in advance according to the plan, or when cognitively burdened humans are involved with its execution.
 
